---
title: "LagunaDeJuanacatlan.Jones.2015"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
    theme: bootstrap
    source_code: embed
    orientation: rows
---

```{r setup, include = FALSE}
library(flexdashboard)
library(maptools)
library(tidyverse)
library(purrr)
library(leaflet)
library(plotly)
library(lipdR)
library(dygraphs)
library(geoChronR)
library(lipdverseR)
#read functions
load("../../temp.Rdata")
load("../../chronTemp.Rdata")


#remove columns we don't want to plot
varNames <- sapply(TS, "[[","paleoData_variableName")

# good <- which(!(varNames %in% c("year","depth","age")))
# TS <- TS[good]


#All datasets
dsn <- sapply(TS,"[[","dataSetName")
ui <- which(!duplicated(dsn))
udsn <- dsn[ui]
lat <- as.numeric(sapply(TS,"[[","geo_latitude")[ui])
lon <- as.numeric(sapply(TS,"[[","geo_longitude")[ui])
#elev <- sapply(TS,"[[","geo_elevation")[ui]
archiveType <- sapply(TS,"[[","archiveType")[ui]
link <- paste0(udsn,".html") %>% 
  str_replace_all("'","_")

#Organize metadata for map
map.meta <- data.frame(dataSetName = udsn, #datasetname
                       lat = lat,#lat
                       lon = lon,#lon
                      # elev = elev,#elevation
                       archiveType = factor(archiveType),#archiveType
                       link = link)#Link


#set index number

i = 421
thisTS <- TS[which(udsn[i] == dsn)]
```
#LagunaDeJuanacatlan.Jones.2015

Metadata {.sidebar}
-------------------------------------
[Download LiPD file](LagunaDeJuanacatlan.Jones.2015.lpd)
            

[Edit LiPD file](http://lipd.net/playground?source=http://lipdverse.org/globalHolocene/0_25_5/LagunaDeJuanacatlan.Jones.2015.lpd)
            

[Download paleoData only (csv)](LagunaDeJuanacatlan.Jones.2015.csv)
            

[Download chronData only (csv)](LagunaDeJuanacatlan.Jones.2015-chron.csv)
            

[Report an issue (include dataset name)](https://github.com/nickmckay/LiPDverse/issues)

<details open style="margin-left: 0px">
<summary>root</summary>
<p style="margin-left: 0px"><strong>archiveType: </strong>LakeSediment
<p style="margin-left: 0px"><strong>originalDataURL: </strong>https://www.sciencedirect.com/science/article/pii/S0277379115300433
<p style="margin-left: 0px"><strong>lipdVersion: </strong>1.3
</details>
<details>
<summary>pub</summary>
<details style="margin-left: 10px">
<summary>pub1</summary>
<p style="margin-left: 10px"><strong>author: </strong>list(list(name = "Jones, Matthew D."), list(name = "Metcalfe, Sarah E."), list(name = "Davies, Sarah J."), list(name = "Noren, Anders"))
<p style="margin-left: 10px"><strong>journal: </strong>Quaternary Science Reviews
<p style="margin-left: 10px"><strong>volume: </strong>124
<p style="margin-left: 10px"><strong>pages: </strong>290-295
<p style="margin-left: 10px"><strong>title: </strong>Late Holocene climate reorganisation and the North American Monsoon
</details>
<details style="margin-left: 10px">
<summary>pub2</summary>
<p style="margin-left: 10px"><strong>author: </strong>list(list(name = "Metcalfe, S.E."), list(name = "Jones, M.D."), list(name = "Davies, S.J."), list(name = "Noren, A."), list(name = "MacKenzie, A."))
<p style="margin-left: 10px"><strong>journal: </strong>The Holocene
<p style="margin-left: 10px"><strong>volume: </strong>20
<p style="margin-left: 10px"><strong>pages: </strong>290-295
<p style="margin-left: 10px"><strong>title: </strong>Climate variability over the last two millennia in the North American Monsoon region, recorded in laminated lake sediments from Laguna de Juanacatlán, Mexico
</details>
</details>
<details>
<summary>funding</summary>
<details style="margin-left: 10px">
<summary>funding1</summary>
<p style="margin-left: 10px"><strong>agency: </strong>Funding Agency
<p style="margin-left: 10px"><strong>grant: </strong>Grant name or number
</details>
</details>
<details open style="margin-left: 0px">
<summary>geo</summary>
<p style="margin-left: 0px"><strong>latitude: </strong>20.6293
<p style="margin-left: 0px"><strong>longitude: </strong>-104.7364
<p style="margin-left: 0px"><strong>elevation: </strong>2000
<p style="margin-left: 0px"><strong>siteName: </strong>Laguna de Juanacatlan
</details>
<details open>
<summary>PaleoData columns</summary>
<details style="margin-left: 10px">
<summary>year (AD) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB988cf23d
<p style="margin-left: 10px"><strong>variableName: </strong>year
<p style="margin-left: 10px"><strong>units: </strong>AD
<p style="margin-left: 10px"><strong>description: </strong>Year AD
</details>
<details style="margin-left: 10px">
<summary>age (BP) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBce52080e
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>BP
<p style="margin-left: 10px"><strong>description: </strong>Years before present (1950) BP
</details>
<details style="margin-left: 10px">
<summary>Ti_peakArea (missing) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDe11c862a
<p style="margin-left: 10px"><strong>variableName: </strong>Ti_peakArea
<p style="margin-left: 10px"><strong>units: </strong>missing
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>TRUE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>basis: </strong>indicator or terriginous runnoff
<p style="margin-left: 20px"><strong>direction: </strong>positive
<p style="margin-left: 20px"><strong>interpDirection: </strong>positive
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>seasonality: </strong>1 2 3 4 5 6 7 8 9 10 11 12
<p style="margin-left: 20px"><strong>variable: </strong>M
<p style="margin-left: 20px"><strong>variableDetail: </strong>monsoon
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>CAL (missing) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD01441887
<p style="margin-left: 10px"><strong>variableName: </strong>CAL
<p style="margin-left: 10px"><strong>units: </strong>missing
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>year (AD) [2-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBddfe7278
<p style="margin-left: 10px"><strong>variableName: </strong>year
<p style="margin-left: 10px"><strong>units: </strong>AD
<p style="margin-left: 10px"><strong>description: </strong>Year AD
</details>
<details style="margin-left: 10px">
<summary>age (BP) [2-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBa25ed912
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>BP
<p style="margin-left: 10px"><strong>description: </strong>Years before present (1950) BP
</details>
<details style="margin-left: 10px">
<summary>Ti_norm (missing) [2-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD91196716
<p style="margin-left: 10px"><strong>variableName: </strong>Ti_norm
<p style="margin-left: 10px"><strong>units: </strong>missing
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>TRUE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>basis: </strong>indicator or terriginous runnoff
<p style="margin-left: 20px"><strong>direction: </strong>positive
<p style="margin-left: 20px"><strong>interpDirection: </strong>positive
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>seasonality: </strong>1 2 3 4 5 6 7 8 9 10 11 12
<p style="margin-left: 20px"><strong>variable: </strong>M
<p style="margin-left: 20px"><strong>variableDetail: </strong>monsoon
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>CAL (missing) [2-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDe9872299
<p style="margin-left: 10px"><strong>variableName: </strong>CAL
<p style="margin-left: 10px"><strong>units: </strong>missing
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details>
<summary>ChronData columns</summary>
<details style="margin-left: 10px">
<summary>depth (cm)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD5b7ccf1d
<p style="margin-left: 10px"><strong>variableName: </strong>depth
<p style="margin-left: 10px"><strong>units: </strong>cm
</details>
<details style="margin-left: 10px">
<summary>age (yr BP)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD77079478
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>yr BP
<p style="margin-left: 10px"><strong>description: </strong>14 C age
</details>
<details style="margin-left: 10px">
<summary>ref (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD70dfd68a
<p style="margin-left: 10px"><strong>variableName: </strong>ref
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>core (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDacd3cbf1
<p style="margin-left: 10px"><strong>variableName: </strong>core
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>type (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDba366732
<p style="margin-left: 10px"><strong>variableName: </strong>type
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>Core_depth (cm)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDe61386e4
<p style="margin-left: 10px"><strong>variableName: </strong>Core_depth
<p style="margin-left: 10px"><strong>units: </strong>cm
</details>
<details style="margin-left: 10px">
<summary>Depth of top of sample (cm)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD307ab71a
<p style="margin-left: 10px"><strong>variableName: </strong>Depth of top of sample
<p style="margin-left: 10px"><strong>units: </strong>cm
</details>
<details style="margin-left: 10px">
<summary>Depth of bottom of sample (cm) (cm)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD923a546d
<p style="margin-left: 10px"><strong>variableName: </strong>Depth of bottom of sample (cm)
<p style="margin-left: 10px"><strong>units: </strong>cm
</details>
<details style="margin-left: 10px">
<summary>14C enrichment (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDd5383e51
<p style="margin-left: 10px"><strong>variableName: </strong>14C enrichment
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>youngest_error (yr BP)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD9de8429d
<p style="margin-left: 10px"><strong>variableName: </strong>youngest_error
<p style="margin-left: 10px"><strong>units: </strong>yr BP
</details>
<details style="margin-left: 10px">
<summary>oldest_error (yr BP)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDe29dccd6
<p style="margin-left: 10px"><strong>variableName: </strong>oldest_error
<p style="margin-left: 10px"><strong>units: </strong>yr BP
</details>
<details style="margin-left: 10px">
<summary>calibrated age (yrs before 1950 AD) (yr BP)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDd936b049
<p style="margin-left: 10px"><strong>variableName: </strong>calibrated age (yrs before 1950 AD)
<p style="margin-left: 10px"><strong>units: </strong>yr BP
</details>
<details style="margin-left: 10px">
<summary>youngest calibrated age (yrs before 1950 AD) (yr BP)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD1685ea2f
<p style="margin-left: 10px"><strong>variableName: </strong>youngest calibrated age (yrs before 1950 AD)
<p style="margin-left: 10px"><strong>units: </strong>yr BP
</details>
<details style="margin-left: 10px">
<summary>oldest calibrated age (yrs before 1950 AD) (yr BP)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDfc9f1dca
<p style="margin-left: 10px"><strong>variableName: </strong>oldest calibrated age (yrs before 1950 AD)
<p style="margin-left: 10px"><strong>units: </strong>yr BP
</details>
<details style="margin-left: 10px">
<summary>1 sigma or 2 sigma? (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDb9275a55
<p style="margin-left: 10px"><strong>variableName: </strong>1 sigma or 2 sigma?
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>Reservoir Correction/R (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD36774e07
<p style="margin-left: 10px"><strong>variableName: </strong>Reservoir Correction/R
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>Calibration used (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDee277fcf
<p style="margin-left: 10px"><strong>variableName: </strong>Calibration used
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>Comments (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD413cf3ef
<p style="margin-left: 10px"><strong>variableName: </strong>Comments
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>probability (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD39d52b77
<p style="margin-left: 10px"><strong>variableName: </strong>probability
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>d13C (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD720e2d85
<p style="margin-left: 10px"><strong>variableName: </strong>d13C
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>

Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### Sitemap

```{r}
  map.meta.split <- split(map.meta, map.meta$archiveType)


factpal <- colorFactor("Paired",map.meta$archiveType)
buff <- 15
l <- leaflet() %>% 
  addTiles() %>% 
  fitBounds(map.meta$lon[i]-buff,map.meta$lat[i]-buff,map.meta$lon[i]+buff,map.meta$lat[i]+buff)
  

  
  
names(map.meta.split) %>%
  purrr::walk( function(df) {
    l <<- l %>%
      addMarkers(data=map.meta.split[[df]],
                 lng=~lon, lat=~lat,
                 label=~as.character(archiveType),
                 popup=~paste(str_c('Dataset: <a href="',link,'">',dataSetName,'</a>'),
                                 # str_c("Elevation: ",elev),
                                  str_c("Archive Type: ",archiveType),
                                  sep = "<br>"),
                 group = df,
                 clusterOptions = markerClusterOptions(removeOutsideVisibleBounds = F),
                 labelOptions = labelOptions(noHide = F,
                                             direction = 'auto'))
  })

l %>%
  addLayersControl(position = "bottomleft",
    overlayGroups = names(map.meta.split),
    options = layersControlOptions(collapsed = FALSE,
                                   opacity = 0.8)
  )
```

### Search the LiPDverse (Beta! doesn't work well yet)
```{r}
#Add google search bar
htmltools::includeHTML("../../googleSearchChunk.html")
```


Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### Ti_peakArea (missing) [1-1]
```{r}
plotCol(thisTS,ind = 4)
```

### CAL (missing) [1-1]
```{r}
plotCol(thisTS,ind = 1)
```

### Ti_norm (missing) [2-1]
```{r}
plotCol(thisTS,ind = 8)
```

### CAL (missing) [2-1]
```{r}
plotCol(thisTS,ind = 5)
```

Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### depth (cm)
```{r}
plotCol(chronTS,ind = 7)
```

### age (yr BP)
```{r}
plotCol(chronTS,ind = 9)
```

### ref (unitless)
```{r}
plotCol(chronTS,ind = 1)
```

### core (unitless)
```{r}
plotCol(chronTS,ind = 2)
```

### type (unitless)
```{r}
plotCol(chronTS,ind = 3)
```

### Core_depth (cm)
```{r}
plotCol(chronTS,ind = 4)
```

### Depth of top of sample (cm)
```{r}
plotCol(chronTS,ind = 5)
```

### Depth of bottom of sample (cm) (cm)
```{r}
plotCol(chronTS,ind = 6)
```

### 14C enrichment (unitless)
```{r}
plotCol(chronTS,ind = 8)
```

### youngest_error (yr BP)
```{r}
plotCol(chronTS,ind = 10)
```

### oldest_error (yr BP)
```{r}
plotCol(chronTS,ind = 11)
```

### calibrated age (yrs before 1950 AD) (yr BP)
```{r}
plotCol(chronTS,ind = 12)
```

### youngest calibrated age (yrs before 1950 AD) (yr BP)
```{r}
plotCol(chronTS,ind = 13)
```

### oldest calibrated age (yrs before 1950 AD) (yr BP)
```{r}
plotCol(chronTS,ind = 14)
```

### 1 sigma or 2 sigma? (unitless)
```{r}
plotCol(chronTS,ind = 15)
```

### Reservoir Correction/R (unitless)
```{r}
plotCol(chronTS,ind = 16)
```

### Calibration used (unitless)
```{r}
plotCol(chronTS,ind = 17)
```

### Comments (unitless)
```{r}
plotCol(chronTS,ind = 18)
```

### probability (unitless)
```{r}
plotCol(chronTS,ind = 19)
```

### d13C (unitless)
```{r}
plotCol(chronTS,ind = 20)
```
