---
title: "LehmanCaves.Steponaitis.2015"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
    theme: bootstrap
    source_code: embed
    orientation: rows
---

```{r setup, include = FALSE}
library(flexdashboard)
library(maptools)
library(tidyverse)
library(purrr)
library(leaflet)
library(plotly)
library(lipdR)
library(dygraphs)
library(geoChronR)
library(lipdverseR)
#read functions
load("../../temp.Rdata")
load("../../chronTemp.Rdata")


#remove columns we don't want to plot
varNames <- sapply(TS, "[[","paleoData_variableName")

# good <- which(!(varNames %in% c("year","depth","age")))
# TS <- TS[good]


#All datasets
dsn <- sapply(TS,"[[","dataSetName")
ui <- which(!duplicated(dsn))
udsn <- dsn[ui]
lat <- as.numeric(sapply(TS,"[[","geo_latitude")[ui])
lon <- as.numeric(sapply(TS,"[[","geo_longitude")[ui])
#elev <- sapply(TS,"[[","geo_elevation")[ui]
archiveType <- sapply(TS,"[[","archiveType")[ui]
link <- paste0(udsn,".html") %>% 
  str_replace_all("'","_")

#Organize metadata for map
map.meta <- data.frame(dataSetName = udsn, #datasetname
                       lat = lat,#lat
                       lon = lon,#lon
                      # elev = elev,#elevation
                       archiveType = factor(archiveType),#archiveType
                       link = link)#Link


#set index number

i = 459
thisTS <- TS[which(udsn[i] == dsn)]
```
#LehmanCaves.Steponaitis.2015

Metadata {.sidebar}
-------------------------------------
[Download LiPD file](LehmanCaves.Steponaitis.2015.lpd)
            

[Edit LiPD file](http://lipd.net/playground?source=http://lipdverse.org/globalHolocene/0_25_5/LehmanCaves.Steponaitis.2015.lpd)
            

[Download paleoData only (csv)](LehmanCaves.Steponaitis.2015.csv)
            

[Download chronData only (csv)](LehmanCaves.Steponaitis.2015-chron.csv)
            

[Report an issue (include dataset name)](https://github.com/nickmckay/LiPDverse/issues)

<details open style="margin-left: 0px">
<summary>root</summary>
<p style="margin-left: 0px"><strong>archiveType: </strong>Speleothem
<p style="margin-left: 0px"><strong>originalDataURL: </strong>https://www.ncdc.noaa.gov/paleo/study/19038
<p style="margin-left: 0px"><strong>lipdVersion: </strong>1.3
</details>
<details>
<summary>pub</summary>
<details style="margin-left: 10px">
<summary>pub1</summary>
<p style="margin-left: 10px"><strong>author: </strong>list(list(name = "Steponaitis, Elena"), list(name = "Andrews, Alexandra"), list(name = "McGee, David"), list(name = "Quade, Jay"), list(name = "Hsieh, Yu-Te"), list(name = "Broecker, Wallace S."), list(name = "Shuman, Bryan N."), list(name = "Burns, Stephen J."), list(name = "Cheng, Hai"))
<p style="margin-left: 10px"><strong>journal: </strong>Quaternary Science Reviews
<p style="margin-left: 10px"><strong>volume: </strong>127
<p style="margin-left: 10px"><strong>pages: </strong>174-185
<p style="margin-left: 10px"><strong>title: </strong>Mid-Holocene drying of the U.S. Great Basin recorded in Nevada speleothems
</details>
<details style="margin-left: 10px">
<summary>pub2</summary>
<p style="margin-left: 10px"><strong>author: </strong>list(list(name = NA))
</details>
</details>
<details open style="margin-left: 0px">
<summary>geo</summary>
<p style="margin-left: 0px"><strong>latitude: </strong>39.0006
<p style="margin-left: 0px"><strong>longitude: </strong>-114.2203
<p style="margin-left: 0px"><strong>elevation: </strong>2130
<p style="margin-left: 0px"><strong>siteName: </strong>Lehman Caves
</details>
<details open>
<summary>PaleoData columns</summary>
<details style="margin-left: 10px">
<summary>age (BP) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB36f7e999
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>BP
</details>
<details style="margin-left: 10px">
<summary>WR11_d13C (permil) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB5432df9c
<p style="margin-left: 10px"><strong>variableName: </strong>WR11_d13C
<p style="margin-left: 10px"><strong>units: </strong>permil
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>TRUE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>direction: </strong>negative
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>seasonality: </strong>winter
<p style="margin-left: 20px"><strong>variable: </strong>M
<p style="margin-left: 20px"><strong>variableDetail: </strong>infiltration
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>WR11_d18O (permil) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB6b9d77ce
<p style="margin-left: 10px"><strong>variableName: </strong>WR11_d18O
<p style="margin-left: 10px"><strong>units: </strong>permil
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>age (BP) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB84c0bfda
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>BP
</details>
<details style="margin-left: 10px">
<summary>CDR3_d18O (permil) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBc6e6732c
<p style="margin-left: 10px"><strong>variableName: </strong>CDR3_d18O
<p style="margin-left: 10px"><strong>units: </strong>permil
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>CDR3_d13C (permil) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBd1dae05b
<p style="margin-left: 10px"><strong>variableName: </strong>CDR3_d13C
<p style="margin-left: 10px"><strong>units: </strong>permil
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>age (BP) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB7abe9a6e
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>BP
</details>
<details style="margin-left: 10px">
<summary>WR11_MgCa (m) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB753b9479
<p style="margin-left: 10px"><strong>variableName: </strong>WR11_MgCa
<p style="margin-left: 10px"><strong>units: </strong>m
<p style="margin-left: 10px"><strong>description: </strong>We therefore interpret Mg/Ca and d13C as reflecting infiltration rates, with higher values corresponding to drier periods.
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>TRUE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>direction: </strong>negative
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>seasonality: </strong>winter
<p style="margin-left: 20px"><strong>variable: </strong>M
<p style="margin-left: 20px"><strong>variableDetail: </strong>infiltration
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>WR11_SrCa (m) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB59702d62
<p style="margin-left: 10px"><strong>variableName: </strong>WR11_SrCa
<p style="margin-left: 10px"><strong>units: </strong>m
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>age (BP) [1-4]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBdb7f2f80
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>BP
</details>
<details style="margin-left: 10px">
<summary>CDR3_MgCa (m) [1-4]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB2b10ce20
<p style="margin-left: 10px"><strong>variableName: </strong>CDR3_MgCa
<p style="margin-left: 10px"><strong>units: </strong>m
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>CDR3_SrCa (m) [1-4]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBeb20a1db
<p style="margin-left: 10px"><strong>variableName: </strong>CDR3_SrCa
<p style="margin-left: 10px"><strong>units: </strong>m
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details>
<summary>ChronData columns</summary>
<details style="margin-left: 10px">
<summary>depth (mm) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBed958827
<p style="margin-left: 10px"><strong>variableName: </strong>depth
<p style="margin-left: 10px"><strong>units: </strong>mm
<p style="margin-left: 10px"><strong>description: </strong>depth from base
</details>
<details style="margin-left: 10px">
<summary>age (yrBP) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBb3fa5614
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>yrBP
<p style="margin-left: 10px"><strong>description: </strong>230Th corrected. WR11 speleothem age model.
</details>
<details style="margin-left: 10px">
<summary>238U ((ng/g)) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBaddc5a66
<p style="margin-left: 10px"><strong>variableName: </strong>238U
<p style="margin-left: 10px"><strong>units: </strong>(ng/g)
</details>
<details style="margin-left: 10px">
<summary>238U_error (ng/g) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBaf98b55b
<p style="margin-left: 10px"><strong>variableName: </strong>238U_error
<p style="margin-left: 10px"><strong>units: </strong>ng/g
</details>
<details style="margin-left: 10px">
<summary>232Th ((pg/g)) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBb447d029
<p style="margin-left: 10px"><strong>variableName: </strong>232Th
<p style="margin-left: 10px"><strong>units: </strong>(pg/g)
</details>
<details style="margin-left: 10px">
<summary>232Th_error ((pg/g)) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB39e51f97
<p style="margin-left: 10px"><strong>variableName: </strong>232Th_error
<p style="margin-left: 10px"><strong>units: </strong>(pg/g)
</details>
<details style="margin-left: 10px">
<summary>230Th / 232Th ((atomic x10-6)) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBa7214a2c
<p style="margin-left: 10px"><strong>variableName: </strong>230Th / 232Th
<p style="margin-left: 10px"><strong>units: </strong>(atomic x10-6)
</details>
<details style="margin-left: 10px">
<summary>230Th / 232Th_error ((atomic x10-6)) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBb94a98a0
<p style="margin-left: 10px"><strong>variableName: </strong>230Th / 232Th_error
<p style="margin-left: 10px"><strong>units: </strong>(atomic x10-6)
</details>
<details style="margin-left: 10px">
<summary><ce><b4>234U (measured) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB75d63789
<p style="margin-left: 10px"><strong>variableName: </strong><ce><b4>234U
<p style="margin-left: 10px"><strong>units: </strong>measured
</details>
<details style="margin-left: 10px">
<summary><ce><b4>234U_error (measured) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBaf45f7ce
<p style="margin-left: 10px"><strong>variableName: </strong><ce><b4>234U_error
<p style="margin-left: 10px"><strong>units: </strong>measured
</details>
<details style="margin-left: 10px">
<summary>230Th / 238U (activity) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB26a61e35
<p style="margin-left: 10px"><strong>variableName: </strong>230Th / 238U
<p style="margin-left: 10px"><strong>units: </strong>activity
</details>
<details style="margin-left: 10px">
<summary>230Th / 238U_error (activity) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB017f3d48
<p style="margin-left: 10px"><strong>variableName: </strong>230Th / 238U_error
<p style="margin-left: 10px"><strong>units: </strong>activity
</details>
<details style="margin-left: 10px">
<summary>230Th_age_uncorrected (yr) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB43d04e55
<p style="margin-left: 10px"><strong>variableName: </strong>230Th_age_uncorrected
<p style="margin-left: 10px"><strong>units: </strong>yr
</details>
<details style="margin-left: 10px">
<summary>230Th_age_uncorrected_error (yr) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB2144a40f
<p style="margin-left: 10px"><strong>variableName: </strong>230Th_age_uncorrected_error
<p style="margin-left: 10px"><strong>units: </strong>yr
</details>
<details style="margin-left: 10px">
<summary>230ThAge_corrected (yr) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB46f45343
<p style="margin-left: 10px"><strong>variableName: </strong>230ThAge_corrected
<p style="margin-left: 10px"><strong>units: </strong>yr
<p style="margin-left: 10px"><strong>description: </strong>WR11 speleothem age model.
</details>
<details style="margin-left: 10px">
<summary>230ThAge_corrected_err (yr) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBdc77d90d
<p style="margin-left: 10px"><strong>variableName: </strong>230ThAge_corrected_err
<p style="margin-left: 10px"><strong>units: </strong>yr
</details>
<details style="margin-left: 10px">
<summary><ce><b4>234UInitial (corrected) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBc3776301
<p style="margin-left: 10px"><strong>variableName: </strong><ce><b4>234UInitial
<p style="margin-left: 10px"><strong>units: </strong>corrected
<p style="margin-left: 10px"><strong>description: </strong>WR11 speleothem age model.
</details>
<details style="margin-left: 10px">
<summary><ce><b4>234UInitial_error (corrected) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB7c36aa8b
<p style="margin-left: 10px"><strong>variableName: </strong><ce><b4>234UInitial_error
<p style="margin-left: 10px"><strong>units: </strong>corrected
<p style="margin-left: 10px"><strong>description: </strong>WR11 speleothem age model.
</details>
<details style="margin-left: 10px">
<summary>error (yr) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBacdd2f56
<p style="margin-left: 10px"><strong>variableName: </strong>error
<p style="margin-left: 10px"><strong>units: </strong>yr
<p style="margin-left: 10px"><strong>description: </strong>230Th age error corrected. WR11 speleothem age model.
</details>
<details style="margin-left: 10px">
<summary>Lab (NA) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB1549b247
<p style="margin-left: 10px"><strong>variableName: </strong>Lab
<p style="margin-left: 10px"><strong>units: </strong>NA
</details>
<details style="margin-left: 10px">
<summary>depth (mm) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBaf29117c
<p style="margin-left: 10px"><strong>variableName: </strong>depth
<p style="margin-left: 10px"><strong>units: </strong>mm
<p style="margin-left: 10px"><strong>description: </strong>depth from base
</details>
<details style="margin-left: 10px">
<summary>age (yrBP) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBf68746ef
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>yrBP
<p style="margin-left: 10px"><strong>description: </strong>230TH corrected age. Decay constants for 230Th and 234U are from Cheng et al. (2013); decay constant for 238U is 1.55125 x 10-10 yr-1 (Jaffey et al., 1971).
</details>
<details style="margin-left: 10px">
<summary>238U (ng/g) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB7af095ed
<p style="margin-left: 10px"><strong>variableName: </strong>238U
<p style="margin-left: 10px"><strong>units: </strong>ng/g
</details>
<details style="margin-left: 10px">
<summary>238U_error (ng/g) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBb914665c
<p style="margin-left: 10px"><strong>variableName: </strong>238U_error
<p style="margin-left: 10px"><strong>units: </strong>ng/g
</details>
<details style="margin-left: 10px">
<summary>232TH (pg/g) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB1ae54c8c
<p style="margin-left: 10px"><strong>variableName: </strong>232TH
<p style="margin-left: 10px"><strong>units: </strong>pg/g
</details>
<details style="margin-left: 10px">
<summary>232TH_error (pg/g) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBfb0d0b00
<p style="margin-left: 10px"><strong>variableName: </strong>232TH_error
<p style="margin-left: 10px"><strong>units: </strong>pg/g
</details>
<details style="margin-left: 10px">
<summary>230Th / 232Th ((atomic x10-6)) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB1c5efacf
<p style="margin-left: 10px"><strong>variableName: </strong>230Th / 232Th
<p style="margin-left: 10px"><strong>units: </strong>(atomic x10-6)
</details>
<details style="margin-left: 10px">
<summary>230Th / 232Th_error ((atomic x10-6)) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBc33041d8
<p style="margin-left: 10px"><strong>variableName: </strong>230Th / 232Th_error
<p style="margin-left: 10px"><strong>units: </strong>(atomic x10-6)
</details>
<details style="margin-left: 10px">
<summary><ce><b4>234U* (measured) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB0bd75aa2
<p style="margin-left: 10px"><strong>variableName: </strong><ce><b4>234U*
<p style="margin-left: 10px"><strong>units: </strong>measured
</details>
<details style="margin-left: 10px">
<summary><ce><b4>234U*_error (measured) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB3b0c7a4a
<p style="margin-left: 10px"><strong>variableName: </strong><ce><b4>234U*_error
<p style="margin-left: 10px"><strong>units: </strong>measured
</details>
<details style="margin-left: 10px">
<summary>230Th / 238U (activity) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBf5fe0bf6
<p style="margin-left: 10px"><strong>variableName: </strong>230Th / 238U
<p style="margin-left: 10px"><strong>units: </strong>activity
</details>
<details style="margin-left: 10px">
<summary>230Th / 238U_error (activity) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBbbb0bc8b
<p style="margin-left: 10px"><strong>variableName: </strong>230Th / 238U_error
<p style="margin-left: 10px"><strong>units: </strong>activity
</details>
<details style="margin-left: 10px">
<summary>230ThAge_uncorrected (yr) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB4f92da2f
<p style="margin-left: 10px"><strong>variableName: </strong>230ThAge_uncorrected
<p style="margin-left: 10px"><strong>units: </strong>yr
</details>
<details style="margin-left: 10px">
<summary>230ThAge_uncorrected_error (yr) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBd46677da
<p style="margin-left: 10px"><strong>variableName: </strong>230ThAge_uncorrected_error
<p style="margin-left: 10px"><strong>units: </strong>yr
</details>
<details style="margin-left: 10px">
<summary>230ThAge_corrected (yrBP) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB79d05b8f
<p style="margin-left: 10px"><strong>variableName: </strong>230ThAge_corrected
<p style="margin-left: 10px"><strong>units: </strong>yrBP
</details>
<details style="margin-left: 10px">
<summary>230ThAge_corrected_error (yr) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB3b551ae3
<p style="margin-left: 10px"><strong>variableName: </strong>230ThAge_corrected_error
<p style="margin-left: 10px"><strong>units: </strong>yr
</details>
<details style="margin-left: 10px">
<summary><ce><b4>234UInitial** (NA) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBf34a2d47
<p style="margin-left: 10px"><strong>variableName: </strong><ce><b4>234UInitial**
<p style="margin-left: 10px"><strong>units: </strong>NA
<p style="margin-left: 10px"><strong>description: </strong>d234Uinitial corrected was calculated based on 230Th age (T), i.e., d234Uinitial = d234Umeasured X el234*T, and T is corrected age.
</details>
<details style="margin-left: 10px">
<summary><ce><b4>234UInitial**_error (NA) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB036be7d3
<p style="margin-left: 10px"><strong>variableName: </strong><ce><b4>234UInitial**_error
<p style="margin-left: 10px"><strong>units: </strong>NA
<p style="margin-left: 10px"><strong>description: </strong>d234Uinitial corrected was calculated based on 230Th age (T), i.e., d234Uinitial = d234Umeasured X el234*T, and T is corrected age.
</details>
<details style="margin-left: 10px">
<summary>error (yr) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB2d973f0b
<p style="margin-left: 10px"><strong>variableName: </strong>error
<p style="margin-left: 10px"><strong>units: </strong>yr
<p style="margin-left: 10px"><strong>description: </strong>230TH corrected age error
</details>
<details style="margin-left: 10px">
<summary>Lab (NA) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB2b2c7fe6
<p style="margin-left: 10px"><strong>variableName: </strong>Lab
<p style="margin-left: 10px"><strong>units: </strong>NA
</details>

Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### Sitemap

```{r}
  map.meta.split <- split(map.meta, map.meta$archiveType)


factpal <- colorFactor("Paired",map.meta$archiveType)
buff <- 15
l <- leaflet() %>% 
  addTiles() %>% 
  fitBounds(map.meta$lon[i]-buff,map.meta$lat[i]-buff,map.meta$lon[i]+buff,map.meta$lat[i]+buff)
  

  
  
names(map.meta.split) %>%
  purrr::walk( function(df) {
    l <<- l %>%
      addMarkers(data=map.meta.split[[df]],
                 lng=~lon, lat=~lat,
                 label=~as.character(archiveType),
                 popup=~paste(str_c('Dataset: <a href="',link,'">',dataSetName,'</a>'),
                                 # str_c("Elevation: ",elev),
                                  str_c("Archive Type: ",archiveType),
                                  sep = "<br>"),
                 group = df,
                 clusterOptions = markerClusterOptions(removeOutsideVisibleBounds = F),
                 labelOptions = labelOptions(noHide = F,
                                             direction = 'auto'))
  })

l %>%
  addLayersControl(position = "bottomleft",
    overlayGroups = names(map.meta.split),
    options = layersControlOptions(collapsed = FALSE,
                                   opacity = 0.8)
  )
```

### Search the LiPDverse (Beta! doesn't work well yet)
```{r}
#Add google search bar
htmltools::includeHTML("../../googleSearchChunk.html")
```


Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### WR11_d13C (permil) [1-1]
```{r}
plotCol(thisTS,ind = 3)
```

### WR11_d18O (permil) [1-1]
```{r}
plotCol(thisTS,ind = 2)
```

### CDR3_d18O (permil) [1-2]
```{r}
plotCol(thisTS,ind = 5)
```

### CDR3_d13C (permil) [1-2]
```{r}
plotCol(thisTS,ind = 6)
```

### WR11_MgCa (m) [1-3]
```{r}
plotCol(thisTS,ind = 8)
```

### WR11_SrCa (m) [1-3]
```{r}
plotCol(thisTS,ind = 9)
```

### CDR3_MgCa (m) [1-4]
```{r}
plotCol(thisTS,ind = 11)
```

### CDR3_SrCa (m) [1-4]
```{r}
plotCol(thisTS,ind = 12)
```

Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### depth (mm) [1-1]
```{r}
plotCol(chronTS,ind = 1)
```

### age (yrBP) [1-1]
```{r}
plotCol(chronTS,ind = 18)
```

### 238U ((ng/g)) [1-1]
```{r}
plotCol(chronTS,ind = 2)
```

### 238U_error (ng/g) [1-1]
```{r}
plotCol(chronTS,ind = 3)
```

### 232Th ((pg/g)) [1-1]
```{r}
plotCol(chronTS,ind = 4)
```

### 232Th_error ((pg/g)) [1-1]
```{r}
plotCol(chronTS,ind = 5)
```

### 230Th / 232Th ((atomic x10-6)) [1-1]
```{r}
plotCol(chronTS,ind = 6)
```

### 230Th / 232Th_error ((atomic x10-6)) [1-1]
```{r}
plotCol(chronTS,ind = 7)
```

### <ce><b4>234U (measured) [1-1]
```{r}
plotCol(chronTS,ind = 8)
```

### <ce><b4>234U_error (measured) [1-1]
```{r}
plotCol(chronTS,ind = 9)
```

### 230Th / 238U (activity) [1-1]
```{r}
plotCol(chronTS,ind = 10)
```

### 230Th / 238U_error (activity) [1-1]
```{r}
plotCol(chronTS,ind = 11)
```

### 230Th_age_uncorrected (yr) [1-1]
```{r}
plotCol(chronTS,ind = 12)
```

### 230Th_age_uncorrected_error (yr) [1-1]
```{r}
plotCol(chronTS,ind = 13)
```

### 230ThAge_corrected (yr) [1-1]
```{r}
plotCol(chronTS,ind = 14)
```

### 230ThAge_corrected_err (yr) [1-1]
```{r}
plotCol(chronTS,ind = 15)
```

### <ce><b4>234UInitial (corrected) [1-1]
```{r}
plotCol(chronTS,ind = 16)
```

### <ce><b4>234UInitial_error (corrected) [1-1]
```{r}
plotCol(chronTS,ind = 17)
```

### error (yr) [1-1]
```{r}
plotCol(chronTS,ind = 19)
```

### Lab (NA) [1-1]
```{r}
plotCol(chronTS,ind = 20)
```

### depth (mm) [1-2]
```{r}
plotCol(chronTS,ind = 21)
```

### age (yrBP) [1-2]
```{r}
plotCol(chronTS,ind = 38)
```

### 238U (ng/g) [1-2]
```{r}
plotCol(chronTS,ind = 22)
```

### 238U_error (ng/g) [1-2]
```{r}
plotCol(chronTS,ind = 23)
```

### 232TH (pg/g) [1-2]
```{r}
plotCol(chronTS,ind = 24)
```

### 232TH_error (pg/g) [1-2]
```{r}
plotCol(chronTS,ind = 25)
```

### 230Th / 232Th ((atomic x10-6)) [1-2]
```{r}
plotCol(chronTS,ind = 26)
```

### 230Th / 232Th_error ((atomic x10-6)) [1-2]
```{r}
plotCol(chronTS,ind = 27)
```

### <ce><b4>234U* (measured) [1-2]
```{r}
plotCol(chronTS,ind = 28)
```

### <ce><b4>234U*_error (measured) [1-2]
```{r}
plotCol(chronTS,ind = 29)
```

### 230Th / 238U (activity) [1-2]
```{r}
plotCol(chronTS,ind = 30)
```

### 230Th / 238U_error (activity) [1-2]
```{r}
plotCol(chronTS,ind = 31)
```

### 230ThAge_uncorrected (yr) [1-2]
```{r}
plotCol(chronTS,ind = 32)
```

### 230ThAge_uncorrected_error (yr) [1-2]
```{r}
plotCol(chronTS,ind = 33)
```

### 230ThAge_corrected (yrBP) [1-2]
```{r}
plotCol(chronTS,ind = 34)
```

### 230ThAge_corrected_error (yr) [1-2]
```{r}
plotCol(chronTS,ind = 35)
```

### <ce><b4>234UInitial** (NA) [1-2]
```{r}
plotCol(chronTS,ind = 36)
```

### <ce><b4>234UInitial**_error (NA) [1-2]
```{r}
plotCol(chronTS,ind = 37)
```

### error (yr) [1-2]
```{r}
plotCol(chronTS,ind = 39)
```

### Lab (NA) [1-2]
```{r}
plotCol(chronTS,ind = 40)
```
