---
title: "MD01_2378"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
    theme: bootstrap
    source_code: embed
    orientation: rows
---

```{r setup, include = FALSE}
library(flexdashboard)
library(maptools)
library(tidyverse)
library(purrr)
library(leaflet)
library(plotly)
library(lipdR)
library(dygraphs)
library(geoChronR)
library(lipdverseR)
#read functions
load("../../temp.Rdata")
load("../../chronTemp.Rdata")


#remove columns we don't want to plot
varNames <- sapply(TS, "[[","paleoData_variableName")

# good <- which(!(varNames %in% c("year","depth","age")))
# TS <- TS[good]


#All datasets
dsn <- sapply(TS,"[[","dataSetName")
ui <- which(!duplicated(dsn))
udsn <- dsn[ui]
lat <- as.numeric(sapply(TS,"[[","geo_latitude")[ui])
lon <- as.numeric(sapply(TS,"[[","geo_longitude")[ui])
#elev <- sapply(TS,"[[","geo_elevation")[ui]
archiveType <- sapply(TS,"[[","archiveType")[ui]
link <- paste0(udsn,".html") %>% 
  str_replace_all("'","_")

#Organize metadata for map
map.meta <- data.frame(dataSetName = udsn, #datasetname
                       lat = lat,#lat
                       lon = lon,#lon
                      # elev = elev,#elevation
                       archiveType = factor(archiveType),#archiveType
                       link = link)#Link


#set index number

i = 514
thisTS <- TS[which(udsn[i] == dsn)]
```
#MD01_2378

Metadata {.sidebar}
-------------------------------------
[Download LiPD file](MD01_2378.lpd)
            

[Edit LiPD file](http://lipd.net/playground?source=http://lipdverse.org/globalHolocene/0_25_5/MD01_2378.lpd)
            

[Download paleoData only (csv)](MD01_2378.csv)
            

[Download chronData only (csv)](MD01_2378-chron.csv)
            

[Report an issue (include dataset name)](https://github.com/nickmckay/LiPDverse/issues)

<details open style="margin-left: 0px">
<summary>root</summary>
<p style="margin-left: 0px"><strong>archiveType: </strong>MarineSediment
<p style="margin-left: 0px"><strong>originalDataURL: </strong>c("https://doi.pangaea.de/10.1594/PANGAEA.263755", "https://doi.pangaea.de/10.1594/PANGAEA.472294", "https://doi.pangaea.de/10.1594/PANGAEA.712513", "https://doi.pangaea.de/10.1594/PANGAEA.831197", "https://doi.pangaea.de/10.1594/PANGAEA.263757", "https://doi.pangaea.de/10.1594/PANGAEA.263759", "https://doi.pangaea.de/10.1594/PANGAEA.263758", "https://doi.pangaea.de/10.1594/PANGAEA.666556", "https://doi.pangaea.de/10.1594/PANGAEA.666553")
<p style="margin-left: 0px"><strong>lipdVersion: </strong>1.3
</details>
<details>
<summary>pub</summary>
<details style="margin-left: 10px">
<summary>pub1</summary>
<p style="margin-left: 10px"><strong>author: </strong>list(list(name = "Holbourn, Ann"), list(name = "Kuhnt, Wolfgang"), list(name = "Kawamura, Hiroshi"), list(name = "Jian, Zhimin"), list(name = "Grootes, Piet"), list(name = "Erlenkeuser, Helmut"), list(name = "Xu, Jian"))
<p style="margin-left: 10px"><strong>journal: </strong>Paleoceanography
<p style="margin-left: 10px"><strong>volume: </strong>20
<p style="margin-left: 10px"><strong>title: </strong>Orbitally paced paleoproductivity variations in the Timor Sea and Indonesian Throughflow variability during the last 460 kyr
</details>
<details style="margin-left: 10px">
<summary>pub2</summary>
<p style="margin-left: 10px"><strong>author: </strong>list(list(name = "Xu, Jian"), list(name = "Kuhnt, Wolfgang"), list(name = "Holbourn, Ann"), list(name = "Andersen, Nils"), list(name = "Bartoli, Gretta"))
<p style="margin-left: 10px"><strong>journal: </strong>Paleoceanography
<p style="margin-left: 10px"><strong>volume: </strong>21
<p style="margin-left: 10px"><strong>title: </strong>Changes in the vertical profile of the Indonesian Throughflow during Termination II: Evidence from the Timor Sea
</details>
<details style="margin-left: 10px">
<summary>pub3</summary>
<p style="margin-left: 10px"><strong>author: </strong>list(list(name = "Zuraida, Rina"), list(name = "Holbourn, Ann"), list(name = "Nürnberg, Dirk"), list(name = "Kuhnt, Wolfgang"), list(name = "Dürkop, Anke"), list(name = "Erichsen, A."))
<p style="margin-left: 10px"><strong>journal: </strong>Paleoceanography
<p style="margin-left: 10px"><strong>volume: </strong>24
<p style="margin-left: 10px"><strong>title: </strong>Evidence for Indonesian Throughflow slowdown during Heinrich events 3-5
</details>
<details style="margin-left: 10px">
<summary>pub4</summary>
<p style="margin-left: 10px"><strong>author: </strong>list(list(name = "Xu, Jian"), list(name = "Holbourn, Ann"), list(name = "Kuhnt, Wolfgang"), list(name = "Jian, Zhimin"), list(name = "Kawamura, Hiroshi"))
<p style="margin-left: 10px"><strong>journal: </strong>Earth and Planetary Science Letters
<p style="margin-left: 10px"><strong>volume: </strong>273
<p style="margin-left: 10px"><strong>title: </strong>Changes in the thermocline structure of the Indonesian outflow during Terminations I and II
</details>
<details style="margin-left: 10px">
<summary>pub5</summary>
<p style="margin-left: 10px"><strong>author: </strong>list(list(name = "Kawamura, Hiroshi"), list(name = "Holbourn, Ann"), list(name = "Kuhnt, Wolfgang"))
<p style="margin-left: 10px"><strong>journal: </strong>Marine Micropaleontology
<p style="margin-left: 10px"><strong>volume: </strong>59
<p style="margin-left: 10px"><strong>title: </strong>Climate variability and land–ocean interactions in the Indo Pacific Warm Pool: A 460-ka palynological and organic geochemical record from the Timor Sea
</details>
<details style="margin-left: 10px">
<summary>pub6</summary>
<p style="margin-left: 10px"><strong>author: </strong>list(list(name = "Dürkop, Anke"), list(name = "Holbourn, Ann"), list(name = "Kuhnt, Wolfgang"), list(name = "Zuraida, Rina"), list(name = "Andersen, Nils"), list(name = "Grootes, Pieter M."))
<p style="margin-left: 10px"><strong>journal: </strong>Marine Micropaleontology
<p style="margin-left: 10px"><strong>volume: </strong>66
<p style="margin-left: 10px"><strong>title: </strong>Centennial-scale climate variability in the Timor Sea during Marine Isotope Stage 3
</details>
<details style="margin-left: 10px">
<summary>pub7</summary>
<p style="margin-left: 10px"><strong>author: </strong>list(list(name = "Dürkop, Anke"), list(name = "Holbourn, Ann"), list(name = "Kuhnt, Wolfgang"), list(name = "Zuraida, Rina"), list(name = "Andersen, Nils"), list(name = "Grootes, Pieter M."))
<p style="margin-left: 10px"><strong>journal: </strong>Marine Micropaleontology
<p style="margin-left: 10px"><strong>volume: </strong>66
<p style="margin-left: 10px"><strong>title: </strong>Centennial-scale climate variability in the Timor Sea during Marine Isotope Stage 3
</details>
<details style="margin-left: 10px">
<summary>pub8</summary>
<p style="margin-left: 10px"><strong>author: </strong>list(list(name = "Sarnthein, M."), list(name = "Grootes, P.M."), list(name = "Holbourn, A."), list(name = "Kuhnt, W."), list(name = "Kühn, H."))
<p style="margin-left: 10px"><strong>journal: </strong>Earth and Planetary Science Letters
<p style="margin-left: 10px"><strong>volume: </strong>302
<p style="margin-left: 10px"><strong>title: </strong>Tropical warming in the Timor Sea led deglacial Antarctic warming and atmospheric CO2 rise by more than 500yr
</details>
</details>
<details open style="margin-left: 0px">
<summary>geo</summary>
<p style="margin-left: 0px"><strong>latitude: </strong>-13.0825
<p style="margin-left: 0px"><strong>longitude: </strong>121.788
<p style="margin-left: 0px"><strong>elevation: </strong>-1783
<p style="margin-left: 0px"><strong>siteName: </strong>MD01_2378
</details>
<details open>
<summary>PaleoData columns</summary>
<details style="margin-left: 10px">
<summary>depth (m) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>ROWM7qHuBCo
<p style="margin-left: 10px"><strong>variableName: </strong>depth
<p style="margin-left: 10px"><strong>units: </strong>m
</details>
<details style="margin-left: 10px">
<summary>age (BP) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RaqJOkfsTYw
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>BP
<p style="margin-left: 10px"><strong>description: </strong>Age_ka_BP
</details>
<details style="margin-left: 10px">
<summary>depth (m) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RMjUks7cU05
<p style="margin-left: 10px"><strong>variableName: </strong>depth
<p style="margin-left: 10px"><strong>units: </strong>m
</details>
<details style="margin-left: 10px">
<summary>age (BP) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RSgSD1mJnnW
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>BP
<p style="margin-left: 10px"><strong>description: </strong>Age_ka_BP
</details>
<details style="margin-left: 10px">
<summary>planktic.d13C (permil) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RDk2rH43Os5
<p style="margin-left: 10px"><strong>variableName: </strong>planktic.d13C
<p style="margin-left: 10px"><strong>units: </strong>permil
<p style="margin-left: 10px"><strong>description: </strong>G_ruber_w_d13C_per_mil_PDB
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>depth (m) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>ROvmmXp7x40
<p style="margin-left: 10px"><strong>variableName: </strong>depth
<p style="margin-left: 10px"><strong>units: </strong>m
</details>
<details style="margin-left: 10px">
<summary>age (BP) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RSVZ1qOiDLt
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>BP
<p style="margin-left: 10px"><strong>description: </strong>Age_ka_BP
</details>
<details style="margin-left: 10px">
<summary>TOC (percent) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>R5tB2eSqeqf
<p style="margin-left: 10px"><strong>variableName: </strong>TOC
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>description: </strong>TOC_percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>depth (m) [1-4]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RlHmp9GEaaB
<p style="margin-left: 10px"><strong>variableName: </strong>depth
<p style="margin-left: 10px"><strong>units: </strong>m
</details>
<details style="margin-left: 10px">
<summary>age (BP) [1-4]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>R38keDgk6Np
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>BP
<p style="margin-left: 10px"><strong>description: </strong>Age_ka_BP
</details>
<details style="margin-left: 10px">
<summary>CaCO3 (percent) [1-4]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RRc0JRaqpDw
<p style="margin-left: 10px"><strong>variableName: </strong>CaCO3
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>description: </strong>CaCO3_percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>depth (m) [1-5]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RLnIkqaWuZL
<p style="margin-left: 10px"><strong>variableName: </strong>depth
<p style="margin-left: 10px"><strong>units: </strong>m
</details>
<details style="margin-left: 10px">
<summary>age (BP) [1-5]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>R0AL9YLkpIS
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>BP
<p style="margin-left: 10px"><strong>description: </strong>Age_ka_BP
</details>
<details style="margin-left: 10px">
<summary>temperature (degC) [1-5]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RsLnvWTKxH5
<p style="margin-left: 10px"><strong>variableName: </strong>temperature
<p style="margin-left: 10px"><strong>units: </strong>degC
<p style="margin-left: 10px"><strong>description: </strong>TT_degC
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>variable: </strong>T
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>temperature (degC) [1-5]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RaFQKq8j02P
<p style="margin-left: 10px"><strong>variableName: </strong>temperature
<p style="margin-left: 10px"><strong>units: </strong>degC
<p style="margin-left: 10px"><strong>description: </strong>SST_1_12_degC
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>depth (m) [1-6]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>Rm4ncp90lOc
<p style="margin-left: 10px"><strong>variableName: </strong>depth
<p style="margin-left: 10px"><strong>units: </strong>m
</details>
<details style="margin-left: 10px">
<summary>age (BP) [1-6]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RzWBK57mTjZ
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>BP
<p style="margin-left: 10px"><strong>description: </strong>Age_ka_BP
</details>
<details style="margin-left: 10px">
<summary>temperature (degC) [1-6]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RSlSF7IhEUX
<p style="margin-left: 10px"><strong>variableName: </strong>temperature
<p style="margin-left: 10px"><strong>units: </strong>degC
<p style="margin-left: 10px"><strong>description: </strong>TT_degC
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>variable: </strong>T
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>temperature (degC) [1-6]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RazJflUVEh7
<p style="margin-left: 10px"><strong>variableName: </strong>temperature
<p style="margin-left: 10px"><strong>units: </strong>degC
<p style="margin-left: 10px"><strong>description: </strong>SST_1_12_degC
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>TRUE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>seasonality: </strong>1 2 3 4 5 6 7 8 9 10 11 12
<p style="margin-left: 20px"><strong>variable: </strong>T
<p style="margin-left: 20px"><strong>variableDetail: </strong>surface.temp
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>planktic.MgCa (mmol_mol) [1-6]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RelARRdOCVN
<p style="margin-left: 10px"><strong>variableName: </strong>planktic.MgCa
<p style="margin-left: 10px"><strong>units: </strong>mmol_mol
<p style="margin-left: 10px"><strong>description: </strong>P_obliqu_Mg_Ca_mmol_mol
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>planktic.MgCa (mmol_mol) [1-6]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RB9odQrtVrH
<p style="margin-left: 10px"><strong>variableName: </strong>planktic.MgCa
<p style="margin-left: 10px"><strong>units: </strong>mmol_mol
<p style="margin-left: 10px"><strong>description: </strong>G_ruber_Mg_Ca_mmol_mol
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>depth (m) [1-7]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RHpxGt8wKHw
<p style="margin-left: 10px"><strong>variableName: </strong>depth
<p style="margin-left: 10px"><strong>units: </strong>m
</details>
<details style="margin-left: 10px">
<summary>age (BP) [1-7]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RkhkxqdcKUo
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>BP
<p style="margin-left: 10px"><strong>description: </strong>Age_ka_BP
</details>
<details style="margin-left: 10px">
<summary>temperature (degC) [1-7]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RGjzfXMedwV
<p style="margin-left: 10px"><strong>variableName: </strong>temperature
<p style="margin-left: 10px"><strong>units: </strong>degC
<p style="margin-left: 10px"><strong>description: </strong>SST_1_12_degC
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>TRUE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>seasonality: </strong>1 2 3 4 5 6 7 8 9 10 11 12
<p style="margin-left: 20px"><strong>variable: </strong>T
<p style="margin-left: 20px"><strong>variableDetail: </strong>surface.temp
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>temperature (degC) [1-7]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RngO0tVRof1
<p style="margin-left: 10px"><strong>variableName: </strong>temperature
<p style="margin-left: 10px"><strong>units: </strong>degC
<p style="margin-left: 10px"><strong>description: </strong>TT_degC
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>variable: </strong>T
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>depth (m) [1-8]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RjKVkjRSEkW
<p style="margin-left: 10px"><strong>variableName: </strong>depth
<p style="margin-left: 10px"><strong>units: </strong>m
</details>
<details style="margin-left: 10px">
<summary>d18O (permil) [1-8]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RTfm55oecMv
<p style="margin-left: 10px"><strong>variableName: </strong>d18O
<p style="margin-left: 10px"><strong>units: </strong>permil
<p style="margin-left: 10px"><strong>description: </strong>merged benthic d18O
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>d13C (permil) [1-8]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RuiPAhMsaKu
<p style="margin-left: 10px"><strong>variableName: </strong>d13C
<p style="margin-left: 10px"><strong>units: </strong>permil
<p style="margin-left: 10px"><strong>description: </strong>merged benthic d13C
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>depth (m) [1-9]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>R0Rb0GIyiqP
<p style="margin-left: 10px"><strong>variableName: </strong>depth
<p style="margin-left: 10px"><strong>units: </strong>m
</details>
<details style="margin-left: 10px">
<summary>planktic.d18O (permil) [1-9]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RD9xZJN6B8T
<p style="margin-left: 10px"><strong>variableName: </strong>planktic.d18O
<p style="margin-left: 10px"><strong>units: </strong>permil
<p style="margin-left: 10px"><strong>description: </strong>merged obl 18O
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>planktic.d13C (permil) [1-9]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RpBYYglPm4F
<p style="margin-left: 10px"><strong>variableName: </strong>planktic.d13C
<p style="margin-left: 10px"><strong>units: </strong>permil
<p style="margin-left: 10px"><strong>description: </strong>merged obl 13C
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>depth (m) [1-10]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RdRl95IoVbv
<p style="margin-left: 10px"><strong>variableName: </strong>depth
<p style="margin-left: 10px"><strong>units: </strong>m
</details>
<details style="margin-left: 10px">
<summary>planktic.d18O (permil) [1-10]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RjO8ZOIvEMX
<p style="margin-left: 10px"><strong>variableName: </strong>planktic.d18O
<p style="margin-left: 10px"><strong>units: </strong>permil
<p style="margin-left: 10px"><strong>description: </strong>merged ruber 18O (all)
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>planktic.d13C (permil) [1-10]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>R1JemqRcMtX
<p style="margin-left: 10px"><strong>variableName: </strong>planktic.d13C
<p style="margin-left: 10px"><strong>units: </strong>permil
<p style="margin-left: 10px"><strong>description: </strong>merged ruber 13C (8 and 9)
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>depth (m) [1-11]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RV51LAcbtoK
<p style="margin-left: 10px"><strong>variableName: </strong>depth
<p style="margin-left: 10px"><strong>units: </strong>m
</details>
<details style="margin-left: 10px">
<summary>planktic.MgCa (mmol_mol) [1-11]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>R2sStCJp6fT
<p style="margin-left: 10px"><strong>variableName: </strong>planktic.MgCa
<p style="margin-left: 10px"><strong>units: </strong>mmol_mol
<p style="margin-left: 10px"><strong>description: </strong>G_ruber_Mg_Ca_mmol_mol merged 8 and 25
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>depth (m) [1-12]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RcmzgS5yUQ5
<p style="margin-left: 10px"><strong>variableName: </strong>depth
<p style="margin-left: 10px"><strong>units: </strong>m
</details>
<details style="margin-left: 10px">
<summary>planktic.MgCa (mmol_mol) [1-12]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RG3Q0KPVl65
<p style="margin-left: 10px"><strong>variableName: </strong>planktic.MgCa
<p style="margin-left: 10px"><strong>units: </strong>mmol_mol
<p style="margin-left: 10px"><strong>description: </strong>P_obliqu_Mg_Ca_mmol_mol. Merged 8 and 25
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details>
<summary>ChronData columns</summary>
<details style="margin-left: 10px">
<summary>depth (cm)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RCurWEXcRkR
<p style="margin-left: 10px"><strong>variableName: </strong>depth
<p style="margin-left: 10px"><strong>units: </strong>cm
</details>
<details style="margin-left: 10px">
<summary>age (kyr)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>R5TVfmpmtY0
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>kyr
</details>
<details style="margin-left: 10px">
<summary>dateType ()</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RhMm5814LgL
<p style="margin-left: 10px"><strong>variableName: </strong>dateType
</details>
<details style="margin-left: 10px">
<summary>thickness (cm)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>Rav3RG845aV
<p style="margin-left: 10px"><strong>variableName: </strong>thickness
<p style="margin-left: 10px"><strong>units: </strong>cm
</details>
<details style="margin-left: 10px">
<summary>measurementMaterial ()</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>R6yu2nAPFZ6
<p style="margin-left: 10px"><strong>variableName: </strong>measurementMaterial
</details>
<details style="margin-left: 10px">
<summary>sensorSpecies ()</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RXzwTY5TZ89
<p style="margin-left: 10px"><strong>variableName: </strong>sensorSpecies
</details>
<details style="margin-left: 10px">
<summary>measurementN ()</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RRbXHHydunl
<p style="margin-left: 10px"><strong>variableName: </strong>measurementN
</details>
<details style="margin-left: 10px">
<summary>labID ()</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RTyNg5lbmTw
<p style="margin-left: 10px"><strong>variableName: </strong>labID
</details>
<details style="margin-left: 10px">
<summary>age14C (kyr)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>R9ehygIyfVS
<p style="margin-left: 10px"><strong>variableName: </strong>age14C
<p style="margin-left: 10px"><strong>units: </strong>kyr
</details>
<details style="margin-left: 10px">
<summary>age14CUncertainty (kyr)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RsVV6VH988a
<p style="margin-left: 10px"><strong>variableName: </strong>age14CUncertainty
<p style="margin-left: 10px"><strong>units: </strong>kyr
</details>
<details style="margin-left: 10px">
<summary>age14CHi (kyr)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RFW8JOATntN
<p style="margin-left: 10px"><strong>variableName: </strong>age14CHi
<p style="margin-left: 10px"><strong>units: </strong>kyr
</details>
<details style="margin-left: 10px">
<summary>age14CLow (kyr)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RZZtmR6kpsC
<p style="margin-left: 10px"><strong>variableName: </strong>age14CLow
<p style="margin-left: 10px"><strong>units: </strong>kyr
</details>
<details style="margin-left: 10px">
<summary>reservoirAge (kyr)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RjPNLexLwL6
<p style="margin-left: 10px"><strong>variableName: </strong>reservoirAge
<p style="margin-left: 10px"><strong>units: </strong>kyr
</details>
<details style="margin-left: 10px">
<summary>reservoirAgeUncertainty (kyr)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RIWbqrn4npB
<p style="margin-left: 10px"><strong>variableName: </strong>reservoirAgeUncertainty
<p style="margin-left: 10px"><strong>units: </strong>kyr
</details>
<details style="margin-left: 10px">
<summary>calibrationCurve ()</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>Rzhswv1ZoyV
<p style="margin-left: 10px"><strong>variableName: </strong>calibrationCurve
</details>
<details style="margin-left: 10px">
<summary>ageUncertainty2sigLo (kyr)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RlJ3tCtWKoT
<p style="margin-left: 10px"><strong>variableName: </strong>ageUncertainty2sigLo
<p style="margin-left: 10px"><strong>units: </strong>kyr
</details>
<details style="margin-left: 10px">
<summary>ageUncertainty2sigHi (kyr)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RS3scNcbDvO
<p style="margin-left: 10px"><strong>variableName: </strong>ageUncertainty2sigHi
<p style="margin-left: 10px"><strong>units: </strong>kyr
</details>
<details style="margin-left: 10px">
<summary>notes ()</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RCaNPoGHi3l
<p style="margin-left: 10px"><strong>variableName: </strong>notes
</details>

Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### Sitemap

```{r}
  map.meta.split <- split(map.meta, map.meta$archiveType)


factpal <- colorFactor("Paired",map.meta$archiveType)
buff <- 15
l <- leaflet() %>% 
  addTiles() %>% 
  fitBounds(map.meta$lon[i]-buff,map.meta$lat[i]-buff,map.meta$lon[i]+buff,map.meta$lat[i]+buff)
  

  
  
names(map.meta.split) %>%
  purrr::walk( function(df) {
    l <<- l %>%
      addMarkers(data=map.meta.split[[df]],
                 lng=~lon, lat=~lat,
                 label=~as.character(archiveType),
                 popup=~paste(str_c('Dataset: <a href="',link,'">',dataSetName,'</a>'),
                                 # str_c("Elevation: ",elev),
                                  str_c("Archive Type: ",archiveType),
                                  sep = "<br>"),
                 group = df,
                 clusterOptions = markerClusterOptions(removeOutsideVisibleBounds = F),
                 labelOptions = labelOptions(noHide = F,
                                             direction = 'auto'))
  })

l %>%
  addLayersControl(position = "bottomleft",
    overlayGroups = names(map.meta.split),
    options = layersControlOptions(collapsed = FALSE,
                                   opacity = 0.8)
  )
```

### Search the LiPDverse (Beta! doesn't work well yet)
```{r}
#Add google search bar
htmltools::includeHTML("../../googleSearchChunk.html")
```


Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### planktic.d13C (permil)
```{r}
plotCol(thisTS,ind = 5)
```

### TOC (percent)
```{r}
plotCol(thisTS,ind = 8)
```

### CaCO3 (percent)
```{r}
plotCol(thisTS,ind = 11)
```

### temperature (degC)
```{r}
plotCol(thisTS,ind = 14)
```

### temperature (degC)
```{r}
plotCol(thisTS,ind = 15)
```

### temperature (degC)
```{r}
plotCol(thisTS,ind = 19)
```

### temperature (degC)
```{r}
plotCol(thisTS,ind = 21)
```

### planktic.MgCa (mmol_mol)
```{r}
plotCol(thisTS,ind = 18)
```

### planktic.MgCa (mmol_mol)
```{r}
plotCol(thisTS,ind = 20)
```

### temperature (degC)
```{r}
plotCol(thisTS,ind = 24)
```

### temperature (degC)
```{r}
plotCol(thisTS,ind = 25)
```

### d18O (permil)
```{r}
plotCol(thisTS,ind = 27)
```

### d13C (permil)
```{r}
plotCol(thisTS,ind = 28)
```

### planktic.d18O (permil)
```{r}
plotCol(thisTS,ind = 30)
```

### planktic.d13C (permil)
```{r}
plotCol(thisTS,ind = 31)
```

### planktic.d18O (permil)
```{r}
plotCol(thisTS,ind = 33)
```

### planktic.d13C (permil)
```{r}
plotCol(thisTS,ind = 34)
```

### planktic.MgCa (mmol_mol)
```{r}
plotCol(thisTS,ind = 36)
```

### planktic.MgCa (mmol_mol)
```{r}
plotCol(thisTS,ind = 38)
```

Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### depth (cm)
```{r}
plotCol(chronTS,ind = 2)
```

### age (kyr)
```{r}
plotCol(chronTS,ind = 15)
```

### dateType ()
```{r}
plotCol(chronTS,ind = 1)
```

### thickness (cm)
```{r}
plotCol(chronTS,ind = 3)
```

### measurementMaterial ()
```{r}
plotCol(chronTS,ind = 4)
```

### sensorSpecies ()
```{r}
plotCol(chronTS,ind = 5)
```

### measurementN ()
```{r}
plotCol(chronTS,ind = 6)
```

### labID ()
```{r}
plotCol(chronTS,ind = 7)
```

### age14C (kyr)
```{r}
plotCol(chronTS,ind = 8)
```

### age14CUncertainty (kyr)
```{r}
plotCol(chronTS,ind = 9)
```

### age14CHi (kyr)
```{r}
plotCol(chronTS,ind = 10)
```

### age14CLow (kyr)
```{r}
plotCol(chronTS,ind = 11)
```

### reservoirAge (kyr)
```{r}
plotCol(chronTS,ind = 12)
```

### reservoirAgeUncertainty (kyr)
```{r}
plotCol(chronTS,ind = 13)
```

### calibrationCurve ()
```{r}
plotCol(chronTS,ind = 14)
```

### ageUncertainty2sigLo (kyr)
```{r}
plotCol(chronTS,ind = 16)
```

### ageUncertainty2sigHi (kyr)
```{r}
plotCol(chronTS,ind = 17)
```

### notes ()
```{r}
plotCol(chronTS,ind = 18)
```
