---
title: "PolevaCave.Constantin.2007"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
    theme: bootstrap
    source_code: embed
    orientation: rows
---

```{r setup, include = FALSE}
library(flexdashboard)
library(maptools)
library(tidyverse)
library(purrr)
library(leaflet)
library(plotly)
library(lipdR)
library(dygraphs)
library(geoChronR)
library(lipdverseR)
#read functions
load("../../temp.Rdata")
load("../../chronTemp.Rdata")


#remove columns we don't want to plot
varNames <- sapply(TS, "[[","paleoData_variableName")

# good <- which(!(varNames %in% c("year","depth","age")))
# TS <- TS[good]


#All datasets
dsn <- sapply(TS,"[[","dataSetName")
ui <- which(!duplicated(dsn))
udsn <- dsn[ui]
lat <- as.numeric(sapply(TS,"[[","geo_latitude")[ui])
lon <- as.numeric(sapply(TS,"[[","geo_longitude")[ui])
#elev <- sapply(TS,"[[","geo_elevation")[ui]
archiveType <- sapply(TS,"[[","archiveType")[ui]
link <- paste0(udsn,".html") %>% 
  str_replace_all("'","_")

#Organize metadata for map
map.meta <- data.frame(dataSetName = udsn, #datasetname
                       lat = lat,#lat
                       lon = lon,#lon
                      # elev = elev,#elevation
                       archiveType = factor(archiveType),#archiveType
                       link = link)#Link


#set index number

i = 691
thisTS <- TS[which(udsn[i] == dsn)]
```
#PolevaCave.Constantin.2007

Metadata {.sidebar}
-------------------------------------
[Download LiPD file](PolevaCave.Constantin.2007.lpd)
            

[Edit LiPD file](http://lipd.net/playground?source=http://lipdverse.org/globalHolocene/0_25_5/PolevaCave.Constantin.2007.lpd)
            

[Download paleoData only (csv)](PolevaCave.Constantin.2007.csv)
            

[Download chronData only (csv)](PolevaCave.Constantin.2007-chron.csv)
            

[Report an issue (include dataset name)](https://github.com/nickmckay/LiPDverse/issues)

<details open style="margin-left: 0px">
<summary>root</summary>
<p style="margin-left: 0px"><strong>archiveType: </strong>Speleothem
<p style="margin-left: 0px"><strong>lipdVersion: </strong>1.3
</details>
<details>
<summary>pub</summary>
<details style="margin-left: 10px">
<summary>pub1</summary>
<p style="margin-left: 10px"><strong>author: </strong>list(list(name = "Constantin, Silviu"), list(name = "Bojar, Ana-Voica"), list(name = "Lauritzen, Stein-Erik"), list(name = "Lundberg, Joyce"))
<p style="margin-left: 10px"><strong>journal: </strong>Palaeogeography, Palaeoclimatology, Palaeoecology
<p style="margin-left: 10px"><strong>volume: </strong>243
<p style="margin-left: 10px"><strong>pages: </strong>322-338
<p style="margin-left: 10px"><strong>title: </strong>Holocene and Late Pleistocene climate in the sub-Mediterranean continental environment: A speleothem record from Poleva Cave (Southern Carpathians, Romania)
</details>
<details style="margin-left: 10px">
<summary>pub2</summary>
<p style="margin-left: 10px"><strong>author: </strong>list(list(name = NA))
</details>
</details>
<details open style="margin-left: 0px">
<summary>geo</summary>
<p style="margin-left: 0px"><strong>latitude: </strong>44.7144
<p style="margin-left: 0px"><strong>longitude: </strong>21.747
<p style="margin-left: 0px"><strong>elevation: </strong>390
<p style="margin-left: 0px"><strong>siteName: </strong>Poleva Cave
</details>
<details open>
<summary>PaleoData columns</summary>
<details style="margin-left: 10px">
<summary>age (yr bo)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB00f8bf96
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>yr bo
</details>
<details style="margin-left: 10px">
<summary>d18O (permil)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB21765f70
<p style="margin-left: 10px"><strong>variableName: </strong>d18O
<p style="margin-left: 10px"><strong>units: </strong>permil
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>TRUE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>direction: </strong>positive
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>seasonality: </strong>1 2 3 4 5 6 7 8 9 10 11 12
<p style="margin-left: 20px"><strong>variable: </strong>T
<p style="margin-left: 20px"><strong>variableDetail: </strong>air@surface
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>d13C (permil)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB2fbf3af7
<p style="margin-left: 10px"><strong>variableName: </strong>d13C
<p style="margin-left: 10px"><strong>units: </strong>permil
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details>
<summary>ChronData columns</summary>
<details style="margin-left: 10px">
<summary>depth (cm)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB9e8b5067
<p style="margin-left: 10px"><strong>variableName: </strong>depth
<p style="margin-left: 10px"><strong>units: </strong>cm
</details>
<details style="margin-left: 10px">
<summary>Lab# (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB6059d811
<p style="margin-left: 10px"><strong>variableName: </strong>Lab#
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>depth_top (cm)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBfe64a33d
<p style="margin-left: 10px"><strong>variableName: </strong>depth_top
<p style="margin-left: 10px"><strong>units: </strong>cm
</details>
<details style="margin-left: 10px">
<summary>depth_bot (cm)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBccb01568
<p style="margin-left: 10px"><strong>variableName: </strong>depth_bot
<p style="margin-left: 10px"><strong>units: </strong>cm
</details>
<details style="margin-left: 10px">
<summary>U (ppm)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB43376eab
<p style="margin-left: 10px"><strong>variableName: </strong>U
<p style="margin-left: 10px"><strong>units: </strong>ppm
</details>
<details style="margin-left: 10px">
<summary>U_error (ppm)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB131a10b4
<p style="margin-left: 10px"><strong>variableName: </strong>U_error
<p style="margin-left: 10px"><strong>units: </strong>ppm
</details>
<details style="margin-left: 10px">
<summary>232Th (ppm)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBcdd11558
<p style="margin-left: 10px"><strong>variableName: </strong>232Th
<p style="margin-left: 10px"><strong>units: </strong>ppm
</details>
<details style="margin-left: 10px">
<summary>234U/238U (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB598a66f8
<p style="margin-left: 10px"><strong>variableName: </strong>234U/238U
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>234U/238U_error (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB84a2cde0
<p style="margin-left: 10px"><strong>variableName: </strong>234U/238U_error
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>230Th/234U (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB52e6682f
<p style="margin-left: 10px"><strong>variableName: </strong>230Th/234U
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>230Th/234U_error (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBcc8e22d1
<p style="margin-left: 10px"><strong>variableName: </strong>230Th/234U_error
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>230Th/232Th (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBe37410bc
<p style="margin-left: 10px"><strong>variableName: </strong>230Th/232Th
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>230Th/232Th_error (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBcdfbdd9a
<p style="margin-left: 10px"><strong>variableName: </strong>230Th/232Th_error
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>234U/232Th (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB9f2f5b25
<p style="margin-left: 10px"><strong>variableName: </strong>234U/232Th
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>234U/232Th_error (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBced4a624
<p style="margin-left: 10px"><strong>variableName: </strong>234U/232Th_error
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>calclulated_age (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB5bc91753
<p style="margin-left: 10px"><strong>variableName: </strong>calclulated_age
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>calculated_age_error (yr bp)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB28130e8a
<p style="margin-left: 10px"><strong>variableName: </strong>calculated_age_error
<p style="margin-left: 10px"><strong>units: </strong>yr bp
</details>
<details style="margin-left: 10px">
<summary>corrected_age (yr)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBfde05f99
<p style="margin-left: 10px"><strong>variableName: </strong>corrected_age
<p style="margin-left: 10px"><strong>units: </strong>yr
</details>
<details style="margin-left: 10px">
<summary>corrected_age_error (yr bp)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBb5c01448
<p style="margin-left: 10px"><strong>variableName: </strong>corrected_age_error
<p style="margin-left: 10px"><strong>units: </strong>yr bp
</details>

Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### Sitemap

```{r}
  map.meta.split <- split(map.meta, map.meta$archiveType)


factpal <- colorFactor("Paired",map.meta$archiveType)
buff <- 15
l <- leaflet() %>% 
  addTiles() %>% 
  fitBounds(map.meta$lon[i]-buff,map.meta$lat[i]-buff,map.meta$lon[i]+buff,map.meta$lat[i]+buff)
  

  
  
names(map.meta.split) %>%
  purrr::walk( function(df) {
    l <<- l %>%
      addMarkers(data=map.meta.split[[df]],
                 lng=~lon, lat=~lat,
                 label=~as.character(archiveType),
                 popup=~paste(str_c('Dataset: <a href="',link,'">',dataSetName,'</a>'),
                                 # str_c("Elevation: ",elev),
                                  str_c("Archive Type: ",archiveType),
                                  sep = "<br>"),
                 group = df,
                 clusterOptions = markerClusterOptions(removeOutsideVisibleBounds = F),
                 labelOptions = labelOptions(noHide = F,
                                             direction = 'auto'))
  })

l %>%
  addLayersControl(position = "bottomleft",
    overlayGroups = names(map.meta.split),
    options = layersControlOptions(collapsed = FALSE,
                                   opacity = 0.8)
  )
```

### Search the LiPDverse (Beta! doesn't work well yet)
```{r}
#Add google search bar
htmltools::includeHTML("../../googleSearchChunk.html")
```


Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### d18O (permil)
```{r}
plotCol(thisTS,ind = 2)
```

### d13C (permil)
```{r}
plotCol(thisTS,ind = 3)
```

Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### depth (cm)
```{r}
plotCol(chronTS,ind = 19)
```

### Lab# (unitless)
```{r}
plotCol(chronTS,ind = 1)
```

### depth_top (cm)
```{r}
plotCol(chronTS,ind = 2)
```

### depth_bot (cm)
```{r}
plotCol(chronTS,ind = 3)
```

### U (ppm)
```{r}
plotCol(chronTS,ind = 4)
```

### U_error (ppm)
```{r}
plotCol(chronTS,ind = 5)
```

### 232Th (ppm)
```{r}
plotCol(chronTS,ind = 6)
```

### 234U/238U (unitless)
```{r}
plotCol(chronTS,ind = 7)
```

### 234U/238U_error (unitless)
```{r}
plotCol(chronTS,ind = 8)
```

### 230Th/234U (unitless)
```{r}
plotCol(chronTS,ind = 9)
```

### 230Th/234U_error (unitless)
```{r}
plotCol(chronTS,ind = 10)
```

### 230Th/232Th (unitless)
```{r}
plotCol(chronTS,ind = 11)
```

### 230Th/232Th_error (unitless)
```{r}
plotCol(chronTS,ind = 12)
```

### 234U/232Th (unitless)
```{r}
plotCol(chronTS,ind = 13)
```

### 234U/232Th_error (unitless)
```{r}
plotCol(chronTS,ind = 14)
```

### calclulated_age (unitless)
```{r}
plotCol(chronTS,ind = 15)
```

### calculated_age_error (yr bp)
```{r}
plotCol(chronTS,ind = 16)
```

### corrected_age (yr)
```{r}
plotCol(chronTS,ind = 17)
```

### corrected_age_error (yr bp)
```{r}
plotCol(chronTS,ind = 18)
```
