---
title: "SanLuisLake.Yuan.2013"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
    theme: bootstrap
    source_code: embed
    orientation: rows
---

```{r setup, include = FALSE}
library(flexdashboard)
library(maptools)
library(tidyverse)
library(purrr)
library(leaflet)
library(plotly)
library(lipdR)
library(dygraphs)
library(geoChronR)
library(lipdverseR)
#read functions
load("../../temp.Rdata")
load("../../chronTemp.Rdata")


#remove columns we don't want to plot
varNames <- sapply(TS, "[[","paleoData_variableName")

# good <- which(!(varNames %in% c("year","depth","age")))
# TS <- TS[good]


#All datasets
dsn <- sapply(TS,"[[","dataSetName")
ui <- which(!duplicated(dsn))
udsn <- dsn[ui]
lat <- as.numeric(sapply(TS,"[[","geo_latitude")[ui])
lon <- as.numeric(sapply(TS,"[[","geo_longitude")[ui])
#elev <- sapply(TS,"[[","geo_elevation")[ui]
archiveType <- sapply(TS,"[[","archiveType")[ui]
link <- paste0(udsn,".html") %>% 
  str_replace_all("'","_")

#Organize metadata for map
map.meta <- data.frame(dataSetName = udsn, #datasetname
                       lat = lat,#lat
                       lon = lon,#lon
                      # elev = elev,#elevation
                       archiveType = factor(archiveType),#archiveType
                       link = link)#Link


#set index number

i = 741
thisTS <- TS[which(udsn[i] == dsn)]
```
#SanLuisLake.Yuan.2013

Metadata {.sidebar}
-------------------------------------
[Download LiPD file](SanLuisLake.Yuan.2013.lpd)
            

[Edit LiPD file](http://lipd.net/playground?source=http://lipdverse.org/globalHolocene/0_25_5/SanLuisLake.Yuan.2013.lpd)
            

[Download paleoData only (csv)](SanLuisLake.Yuan.2013.csv)
            

[Download chronData only (csv)](SanLuisLake.Yuan.2013-chron.csv)
            

[Report an issue (include dataset name)](https://github.com/nickmckay/LiPDverse/issues)

<details open style="margin-left: 0px">
<summary>root</summary>
<p style="margin-left: 0px"><strong>archiveType: </strong>LakeSediment
<p style="margin-left: 0px"><strong>originalDataURL: </strong>https://www.ncdc.noaa.gov/paleo/study/16114
<p style="margin-left: 0px"><strong>lipdVersion: </strong>1.3
</details>
<details>
<summary>pub</summary>
<details style="margin-left: 10px">
<summary>pub1</summary>
<p style="margin-left: 10px"><strong>author: </strong>list(list(name = "Yuan, Fasong"), list(name = "Koran, Max R."), list(name = "Valdez, Andrew"))
<p style="margin-left: 10px"><strong>citeKey: </strong>yuan2013lateglacialandholocenerec
<p style="margin-left: 10px"><strong>journal: </strong>Palaeogeography, Palaeoclimatology, Palaeoecology
<p style="margin-left: 10px"><strong>volume: </strong>392
<p style="margin-left: 10px"><strong>pages: </strong>146-160
<p style="margin-left: 10px"><strong>title: </strong>Late Glacial and Holocene record of climatic change in the southern Rocky Mountains from sediments in San Luis Lake, Colorado, USA
</details>
<details style="margin-left: 10px">
<summary>pub2</summary>
<p style="margin-left: 10px"><strong>author: </strong>list(list(name = NA))
</details>
</details>
<details open style="margin-left: 0px">
<summary>geo</summary>
<p style="margin-left: 0px"><strong>latitude: </strong>37.675
<p style="margin-left: 0px"><strong>longitude: </strong>-105.723
<p style="margin-left: 0px"><strong>elevation: </strong>2293
<p style="margin-left: 0px"><strong>siteName: </strong>San Luis Lake
</details>
<details open>
<summary>PaleoData columns</summary>
<details style="margin-left: 10px">
<summary>year (AD)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB982522b8
<p style="margin-left: 10px"><strong>variableName: </strong>year
<p style="margin-left: 10px"><strong>units: </strong>AD
<p style="margin-left: 10px"><strong>description: </strong>Year AD
</details>
<details style="margin-left: 10px">
<summary>age (BP)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBb1522500
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>BP
<p style="margin-left: 10px"><strong>description: </strong>Years before present (1950) yr BP
</details>
<details style="margin-left: 10px">
<summary>depth (cm)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBa24d9598
<p style="margin-left: 10px"><strong>variableName: </strong>depth
<p style="margin-left: 10px"><strong>units: </strong>cm
<p style="margin-left: 10px"><strong>description: </strong>depth
</details>
<details style="margin-left: 10px">
<summary>d13C (permil)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>GH2d3d5a0b
<p style="margin-left: 10px"><strong>variableName: </strong>d13C
<p style="margin-left: 10px"><strong>units: </strong>permil
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>direction: </strong>negative
<p style="margin-left: 20px"><strong>interpDirection: </strong>negative
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>seasonality: </strong>1 2 3 4 5 6 7 8 9 10 11 12
<p style="margin-left: 20px"><strong>variable: </strong>M
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>d18O (permil)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>GH8f461f71
<p style="margin-left: 10px"><strong>variableName: </strong>d18O
<p style="margin-left: 10px"><strong>units: </strong>permil
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>TRUE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>direction: </strong>negative
<p style="margin-left: 20px"><strong>interpDirection: </strong>negative
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>seasonality: </strong>1 2 3 4 5 6 7 8 9 10 11 12
<p style="margin-left: 20px"><strong>variable: </strong>M
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>CaCO3 (percent)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>GH0648d490
<p style="margin-left: 10px"><strong>variableName: </strong>CaCO3
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details>
<summary>ChronData columns</summary>
<details style="margin-left: 10px">
<summary>depth (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD775e8bad
<p style="margin-left: 10px"><strong>variableName: </strong>depth
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>age (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD4c60df18
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>TypeOfMaterialDated (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD5024de7f
<p style="margin-left: 10px"><strong>variableName: </strong>TypeOfMaterialDated
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>AverageSampleDepth_cm_ (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD0d8fd260
<p style="margin-left: 10px"><strong>variableName: </strong>AverageSampleDepth_cm_
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>ageMin (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDb1072fee
<p style="margin-left: 10px"><strong>variableName: </strong>ageMin
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>ageMax (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDfaa61777
<p style="margin-left: 10px"><strong>variableName: </strong>ageMax
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>calAge (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDc9f9d2cf
<p style="margin-left: 10px"><strong>variableName: </strong>calAge
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>calMin (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD3eabac7b
<p style="margin-left: 10px"><strong>variableName: </strong>calMin
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>calMax (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD8e2d2b79
<p style="margin-left: 10px"><strong>variableName: </strong>calMax
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>x1SigmaOr2Sigma_ (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD66bfd9f9
<p style="margin-left: 10px"><strong>variableName: </strong>x1SigmaOr2Sigma_
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>ReservoirCorrection__R (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDce31d7be
<p style="margin-left: 10px"><strong>variableName: </strong>ReservoirCorrection__R
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>rejected (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD55779927
<p style="margin-left: 10px"><strong>variableName: </strong>rejected
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>Comments (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD614fec27
<p style="margin-left: 10px"><strong>variableName: </strong>Comments
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>

Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### Sitemap

```{r}
  map.meta.split <- split(map.meta, map.meta$archiveType)


factpal <- colorFactor("Paired",map.meta$archiveType)
buff <- 15
l <- leaflet() %>% 
  addTiles() %>% 
  fitBounds(map.meta$lon[i]-buff,map.meta$lat[i]-buff,map.meta$lon[i]+buff,map.meta$lat[i]+buff)
  

  
  
names(map.meta.split) %>%
  purrr::walk( function(df) {
    l <<- l %>%
      addMarkers(data=map.meta.split[[df]],
                 lng=~lon, lat=~lat,
                 label=~as.character(archiveType),
                 popup=~paste(str_c('Dataset: <a href="',link,'">',dataSetName,'</a>'),
                                 # str_c("Elevation: ",elev),
                                  str_c("Archive Type: ",archiveType),
                                  sep = "<br>"),
                 group = df,
                 clusterOptions = markerClusterOptions(removeOutsideVisibleBounds = F),
                 labelOptions = labelOptions(noHide = F,
                                             direction = 'auto'))
  })

l %>%
  addLayersControl(position = "bottomleft",
    overlayGroups = names(map.meta.split),
    options = layersControlOptions(collapsed = FALSE,
                                   opacity = 0.8)
  )
```

### Search the LiPDverse (Beta! doesn't work well yet)
```{r}
#Add google search bar
htmltools::includeHTML("../../googleSearchChunk.html")
```


Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### d13C (permil)
```{r}
plotCol(thisTS,ind = 5)
```

### d18O (permil)
```{r}
plotCol(thisTS,ind = 6)
```

### CaCO3 (percent)
```{r}
plotCol(thisTS,ind = 1)
```

Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### depth (unitless)
```{r}
plotCol(chronTS,ind = 3)
```

### age (unitless)
```{r}
plotCol(chronTS,ind = 4)
```

### TypeOfMaterialDated (unitless)
```{r}
plotCol(chronTS,ind = 1)
```

### AverageSampleDepth_cm_ (unitless)
```{r}
plotCol(chronTS,ind = 2)
```

### ageMin (unitless)
```{r}
plotCol(chronTS,ind = 5)
```

### ageMax (unitless)
```{r}
plotCol(chronTS,ind = 6)
```

### calAge (unitless)
```{r}
plotCol(chronTS,ind = 7)
```

### calMin (unitless)
```{r}
plotCol(chronTS,ind = 8)
```

### calMax (unitless)
```{r}
plotCol(chronTS,ind = 9)
```

### x1SigmaOr2Sigma_ (unitless)
```{r}
plotCol(chronTS,ind = 10)
```

### ReservoirCorrection__R (unitless)
```{r}
plotCol(chronTS,ind = 11)
```

### rejected (unitless)
```{r}
plotCol(chronTS,ind = 12)
```

### Comments (unitless)
```{r}
plotCol(chronTS,ind = 13)
```
