---
title: "SilverLake.Kirby.2015"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
    theme: bootstrap
    source_code: embed
    orientation: rows
---

```{r setup, include = FALSE}
library(flexdashboard)
library(maptools)
library(tidyverse)
library(purrr)
library(leaflet)
library(plotly)
library(lipdR)
library(dygraphs)
library(geoChronR)
library(lipdverseR)
#read functions
load("../../temp.Rdata")
load("../../chronTemp.Rdata")


#remove columns we don't want to plot
varNames <- sapply(TS, "[[","paleoData_variableName")

# good <- which(!(varNames %in% c("year","depth","age")))
# TS <- TS[good]


#All datasets
dsn <- sapply(TS,"[[","dataSetName")
ui <- which(!duplicated(dsn))
udsn <- dsn[ui]
lat <- as.numeric(sapply(TS,"[[","geo_latitude")[ui])
lon <- as.numeric(sapply(TS,"[[","geo_longitude")[ui])
#elev <- sapply(TS,"[[","geo_elevation")[ui]
archiveType <- sapply(TS,"[[","archiveType")[ui]
link <- paste0(udsn,".html") %>% 
  str_replace_all("'","_")

#Organize metadata for map
map.meta <- data.frame(dataSetName = udsn, #datasetname
                       lat = lat,#lat
                       lon = lon,#lon
                      # elev = elev,#elevation
                       archiveType = factor(archiveType),#archiveType
                       link = link)#Link


#set index number

i = 753
thisTS <- TS[which(udsn[i] == dsn)]
```
#SilverLake.Kirby.2015

Metadata {.sidebar}
-------------------------------------
[Download LiPD file](SilverLake.Kirby.2015.lpd)
            

[Edit LiPD file](http://lipd.net/playground?source=http://lipdverse.org/globalHolocene/0_25_5/SilverLake.Kirby.2015.lpd)
            

[Download paleoData only (csv)](SilverLake.Kirby.2015.csv)
            

[Download chronData only (csv)](SilverLake.Kirby.2015-chron.csv)
            

[Report an issue (include dataset name)](https://github.com/nickmckay/LiPDverse/issues)

<details open style="margin-left: 0px">
<summary>root</summary>
<p style="margin-left: 0px"><strong>archiveType: </strong>LakeSediment
<p style="margin-left: 0px"><strong>lipdVersion: </strong>1.3
</details>
<details>
<summary>pub</summary>
<details style="margin-left: 10px">
<summary>pub1</summary>
<p style="margin-left: 10px"><strong>author: </strong>list(list(name = "Kirby, Matthew E."), list(name = "Knell, Edward J."), list(name = "Anderson, William T."), list(name = "Lachniet, Matthew S."), list(name = "Palermo, Jennifer"), list(name = "Eeg, Holly"), list(name = "Lucero, Ricardo"), list(name = "Murrieta, Rosa"), list(name = "Arevalo, Andrea"), list(name = "Silveira, Emily"), list(name = "Hiner, Christine A."))
<p style="margin-left: 10px"><strong>citeKey: </strong>kirby2015evidenceforinsolationandp
<p style="margin-left: 10px"><strong>journal: </strong>Quaternary Research
<p style="margin-left: 10px"><strong>volume: </strong>84
<p style="margin-left: 10px"><strong>pages: </strong>174-186
<p style="margin-left: 10px"><strong>title: </strong>Evidence for insolation and Pacific forcing of late glacial through Holocene climate in the Central Mojave Desert (Silver Lake, CA)
</details>
<details style="margin-left: 10px">
<summary>pub2</summary>
<p style="margin-left: 10px"><strong>author: </strong>list(list(name = NA))
</details>
</details>
<details open style="margin-left: 0px">
<summary>geo</summary>
<p style="margin-left: 0px"><strong>latitude: </strong>35.3669
<p style="margin-left: 0px"><strong>longitude: </strong>-116.135
<p style="margin-left: 0px"><strong>elevation: </strong>276.8
<p style="margin-left: 0px"><strong>siteName: </strong>SilverLake
</details>
<details open>
<summary>PaleoData columns</summary>
<details style="margin-left: 10px">
<summary>depth (cm)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>GH60d9d80e
<p style="margin-left: 10px"><strong>variableName: </strong>depth
<p style="margin-left: 10px"><strong>units: </strong>cm
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>year (AD)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBe990c2f9
<p style="margin-left: 10px"><strong>variableName: </strong>year
<p style="margin-left: 10px"><strong>units: </strong>AD
<p style="margin-left: 10px"><strong>description: </strong>Year AD
</details>
<details style="margin-left: 10px">
<summary>age (BP)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBd49459d4
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>BP
<p style="margin-left: 10px"><strong>description: </strong>Years before present (1950) BP
</details>
<details style="margin-left: 10px">
<summary>clay0x25strd (percent)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>GH5c7c9e12
<p style="margin-left: 10px"><strong>variableName: </strong>clay0x25strd
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>direction: </strong>positive
<p style="margin-left: 20px"><strong>interpDirection: </strong>positive
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>seasonality: </strong>1 2 3 4 5 6 7 8 9 10 11 12
<p style="margin-left: 20px"><strong>variable: </strong>M
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>susc (missing)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>GH6b2cecb6
<p style="margin-left: 10px"><strong>variableName: </strong>susc
<p style="margin-left: 10px"><strong>units: </strong>missing
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>LOI (missing)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD7156de28
<p style="margin-left: 10px"><strong>variableName: </strong>LOI
<p style="margin-left: 10px"><strong>units: </strong>missing
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>LOI (missing)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>GH4776cdb6
<p style="margin-left: 10px"><strong>variableName: </strong>LOI
<p style="margin-left: 10px"><strong>units: </strong>missing
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>gs500x25 (percent)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD9fb6bf7e
<p style="margin-left: 10px"><strong>variableName: </strong>gs500x25
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>gs0x2E020x2D30x2E89um (percent)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDa562774b
<p style="margin-left: 10px"><strong>variableName: </strong>gs0x2E020x2D30x2E89um
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>gs30x2E900x2D70x2E79um (percent)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD51cbe474
<p style="margin-left: 10px"><strong>variableName: </strong>gs30x2E900x2D70x2E79um
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>gs70x2E800x2D150x2E59um (percent)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD3ef4bfe7
<p style="margin-left: 10px"><strong>variableName: </strong>gs70x2E800x2D150x2E59um
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>gs150x2E60um0x2D300x2E99um (percent)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>GHa775a207
<p style="margin-left: 10px"><strong>variableName: </strong>gs150x2E60um0x2D300x2E99um
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>gs310x2E000x2D620x2E49um (percent)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>GH77aefe9e
<p style="margin-left: 10px"><strong>variableName: </strong>gs310x2E000x2D620x2E49um
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>gs620x2E500x2D1240x2E99um (percent)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>GH992857f7
<p style="margin-left: 10px"><strong>variableName: </strong>gs620x2E500x2D1240x2E99um
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>gs1250x2E000x2D2490x2E99um (percent)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>GH1507b371
<p style="margin-left: 10px"><strong>variableName: </strong>gs1250x2E000x2D2490x2E99um
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>gs2500x2E000x2D4990x2E99um (percent)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>GH0ee64c87
<p style="margin-left: 10px"><strong>variableName: </strong>gs2500x2E000x2D4990x2E99um
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>grainSize5000x2E00um0x2D10000x2E00um (percent)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>GHa1df1de0
<p style="margin-left: 10px"><strong>variableName: </strong>grainSize5000x2E00um0x2D10000x2E00um
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>gs10000x2E010x2D20000x2E00um (percent)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>GH8a6ab794
<p style="margin-left: 10px"><strong>variableName: </strong>gs10000x2E010x2D20000x2E00um
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>mode (missing)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>GHd79d4677
<p style="margin-left: 10px"><strong>variableName: </strong>mode
<p style="margin-left: 10px"><strong>units: </strong>missing
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>clay0x25 (percent)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>GH1b070f8e
<p style="margin-left: 10px"><strong>variableName: </strong>clay0x25
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>silt0x25 (percent)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>GH6e4ee697
<p style="margin-left: 10px"><strong>variableName: </strong>silt0x25
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>sand0x25 (percent)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>GHe30d3495
<p style="margin-left: 10px"><strong>variableName: </strong>sand0x25
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>ostracods (missing)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>GH7be027b8
<p style="margin-left: 10px"><strong>variableName: </strong>ostracods
<p style="margin-left: 10px"><strong>units: </strong>missing
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>C0x2FN (missing)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>GHb2a90bf2
<p style="margin-left: 10px"><strong>variableName: </strong>C0x2FN
<p style="margin-left: 10px"><strong>units: </strong>missing
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details>
<summary>ChronData columns</summary>
<details style="margin-left: 10px">
<summary>age (yr BP)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDaa786707
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>yr BP
</details>
<details style="margin-left: 10px">
<summary>x_LABAndID_ (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD32931661
<p style="margin-left: 10px"><strong>variableName: </strong>x_LABAndID_
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>UpperDepth_cm_ (cm)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDa7f3eab6
<p style="margin-left: 10px"><strong>variableName: </strong>UpperDepth_cm_
<p style="margin-left: 10px"><strong>units: </strong>cm
</details>
<details style="margin-left: 10px">
<summary>LowerDepth_cm_ (cm)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD81e7ab49
<p style="margin-left: 10px"><strong>variableName: </strong>LowerDepth_cm_
<p style="margin-left: 10px"><strong>units: </strong>cm
</details>
<details style="margin-left: 10px">
<summary>MaterialDated (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD6c1fc0ed
<p style="margin-left: 10px"><strong>variableName: </strong>MaterialDated
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>x13C_12C_permil_ (permil)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDae761fd0
<p style="margin-left: 10px"><strong>variableName: </strong>x13C_12C_permil_
<p style="margin-left: 10px"><strong>units: </strong>permil
</details>
<details style="margin-left: 10px">
<summary>error (yr)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD1079b4bb
<p style="margin-left: 10px"><strong>variableName: </strong>error
<p style="margin-left: 10px"><strong>units: </strong>yr
</details>
<details style="margin-left: 10px">
<summary>x2SigmaCalibrationLower (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD8ec8baf1
<p style="margin-left: 10px"><strong>variableName: </strong>x2SigmaCalibrationLower
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>x2SigmaCalibrationUpper (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDd72fd146
<p style="margin-left: 10px"><strong>variableName: </strong>x2SigmaCalibrationUpper
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>Rel_AreaUnderProb_Distribution (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD9e7bf79e
<p style="margin-left: 10px"><strong>variableName: </strong>Rel_AreaUnderProb_Distribution
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>x_meanCalYr_ka_BP (yr)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDd239c465
<p style="margin-left: 10px"><strong>variableName: </strong>x_meanCalYr_ka_BP
<p style="margin-left: 10px"><strong>units: </strong>yr
</details>

Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### Sitemap

```{r}
  map.meta.split <- split(map.meta, map.meta$archiveType)


factpal <- colorFactor("Paired",map.meta$archiveType)
buff <- 15
l <- leaflet() %>% 
  addTiles() %>% 
  fitBounds(map.meta$lon[i]-buff,map.meta$lat[i]-buff,map.meta$lon[i]+buff,map.meta$lat[i]+buff)
  

  
  
names(map.meta.split) %>%
  purrr::walk( function(df) {
    l <<- l %>%
      addMarkers(data=map.meta.split[[df]],
                 lng=~lon, lat=~lat,
                 label=~as.character(archiveType),
                 popup=~paste(str_c('Dataset: <a href="',link,'">',dataSetName,'</a>'),
                                 # str_c("Elevation: ",elev),
                                  str_c("Archive Type: ",archiveType),
                                  sep = "<br>"),
                 group = df,
                 clusterOptions = markerClusterOptions(removeOutsideVisibleBounds = F),
                 labelOptions = labelOptions(noHide = F,
                                             direction = 'auto'))
  })

l %>%
  addLayersControl(position = "bottomleft",
    overlayGroups = names(map.meta.split),
    options = layersControlOptions(collapsed = FALSE,
                                   opacity = 0.8)
  )
```

### Search the LiPDverse (Beta! doesn't work well yet)
```{r}
#Add google search bar
htmltools::includeHTML("../../googleSearchChunk.html")
```


Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### clay0x25strd (percent)
```{r}
plotCol(thisTS,ind = 22)
```

### susc (missing)
```{r}
plotCol(thisTS,ind = 4)
```

### LOI (missing)
```{r}
plotCol(thisTS,ind = 5)
```

### LOI (missing)
```{r}
plotCol(thisTS,ind = 6)
```

### gs500x25 (percent)
```{r}
plotCol(thisTS,ind = 7)
```

### gs0x2E020x2D30x2E89um (percent)
```{r}
plotCol(thisTS,ind = 8)
```

### gs30x2E900x2D70x2E79um (percent)
```{r}
plotCol(thisTS,ind = 9)
```

### gs70x2E800x2D150x2E59um (percent)
```{r}
plotCol(thisTS,ind = 10)
```

### gs150x2E60um0x2D300x2E99um (percent)
```{r}
plotCol(thisTS,ind = 11)
```

### gs310x2E000x2D620x2E49um (percent)
```{r}
plotCol(thisTS,ind = 12)
```

### gs620x2E500x2D1240x2E99um (percent)
```{r}
plotCol(thisTS,ind = 13)
```

### gs1250x2E000x2D2490x2E99um (percent)
```{r}
plotCol(thisTS,ind = 14)
```

### gs2500x2E000x2D4990x2E99um (percent)
```{r}
plotCol(thisTS,ind = 15)
```

### grainSize5000x2E00um0x2D10000x2E00um (percent)
```{r}
plotCol(thisTS,ind = 16)
```

### gs10000x2E010x2D20000x2E00um (percent)
```{r}
plotCol(thisTS,ind = 17)
```

### mode (missing)
```{r}
plotCol(thisTS,ind = 18)
```

### clay0x25 (percent)
```{r}
plotCol(thisTS,ind = 19)
```

### silt0x25 (percent)
```{r}
plotCol(thisTS,ind = 20)
```

### sand0x25 (percent)
```{r}
plotCol(thisTS,ind = 21)
```

### ostracods (missing)
```{r}
plotCol(thisTS,ind = 23)
```

### C0x2FN (missing)
```{r}
plotCol(thisTS,ind = 24)
```

Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### age (yr BP)
```{r}
plotCol(chronTS,ind = 6)
```

### x_LABAndID_ (unitless)
```{r}
plotCol(chronTS,ind = 1)
```

### UpperDepth_cm_ (cm)
```{r}
plotCol(chronTS,ind = 2)
```

### LowerDepth_cm_ (cm)
```{r}
plotCol(chronTS,ind = 3)
```

### MaterialDated (unitless)
```{r}
plotCol(chronTS,ind = 4)
```

### x13C_12C_permil_ (permil)
```{r}
plotCol(chronTS,ind = 5)
```

### error (yr)
```{r}
plotCol(chronTS,ind = 7)
```

### x2SigmaCalibrationLower (unitless)
```{r}
plotCol(chronTS,ind = 8)
```

### x2SigmaCalibrationUpper (unitless)
```{r}
plotCol(chronTS,ind = 9)
```

### Rel_AreaUnderProb_Distribution (unitless)
```{r}
plotCol(chronTS,ind = 10)
```

### x_meanCalYr_ka_BP (yr)
```{r}
plotCol(chronTS,ind = 11)
```
