---
title: "Elsinore.Kirby.2010"
output: 
  flexdashboard::flex_dashboard:
    theme: bootstrap
    source_code: embed
    orientation: rows
---

```{r setup, include = FALSE}
library(flexdashboard)
library(maptools)
library(tidyverse)
library(purrr)
library(leaflet)
library(plotly)
library(lipdR)
library(dygraphs)
library(geoChronR)

#read functions
source("../../functions.R")


load("../../temp.Rdata")

#remove columns we don't want to plot
varNames <- sapply(TS, "[[","paleoData_variableName")

# good <- which(!(varNames %in% c("year","depth","age")))
# TS <- TS[good]


#All datasets
dsn <- sapply(TS,"[[","dataSetName")
ui <- which(!duplicated(dsn))
udsn <- dsn[ui]
lat <- as.numeric(sapply(TS,"[[","geo_latitude")[ui])
lon <- as.numeric(sapply(TS,"[[","geo_longitude")[ui])
#elev <- sapply(TS,"[[","geo_elevation")[ui]
archiveType <- sapply(TS,"[[","archiveType")[ui]
link <- paste0(udsn,".html") %>% 
  str_replace_all("'","_")

#Organize metadata for map
map.meta <- data.frame(dataSetName = udsn, #datasetname
                       lat = lat,#lat
                       lon = lon,#lon
                      # elev = elev,#elevation
                       archiveType = factor(archiveType),#archiveType
                       link = link)#Link


#set index number

i = 27
thisTS <- TS[which(udsn[i] == dsn)]
```
#Elsinore.Kirby.2010

Metadata {.sidebar}
-------------------------------------
[Download LiPD file](Elsinore.Kirby.2010.lpd)
            

[Edit LiPD file](http://lipd.net/playground?source=http://lipdverse.org/wNAm0_1_0/Elsinore.Kirby.2010.lpd)
            

[Download data only (csv)](Elsinore.Kirby.2010.csv)
            

[Report an issue (include dataset name)](https://github.com/nickmckay/LiPDverse/issues)

<details open style="margin-left: 0px">
<summary>root</summary>
<p style="margin-left: 0px"><strong>archiveType: </strong>lake sediment
<p style="margin-left: 0px"><strong>originalDataURL: </strong>https://www.ncdc.noaa.gov/paleo/study/12200
<p style="margin-left: 0px"><strong>lipdVersion: </strong>1.3
</details>
<details>
<summary>pub</summary>
<details style="margin-left: 10px">
<summary>pub1</summary>
<p style="margin-left: 10px"><strong>citeKey: </strong>kirby2010aholocenerecordofpacificd
<p style="margin-left: 10px"><strong>journal: </strong>Journal of Paleolimnology
<p style="margin-left: 10px"><strong>volume: </strong>44
<p style="margin-left: 10px"><strong>pages: </strong>819-839
<p style="margin-left: 10px"><strong>pubYear: </strong>2010
<p style="margin-left: 10px"><strong>title: </strong>A Holocene record of Pacific Decadal Oscillation (PDO)-related hydrologic variability in Southern California (Lake Elsinore, CA)
</details>
</details>
<details open style="margin-left: 0px">
<summary>geo</summary>
<p style="margin-left: 0px"><strong>latitude: </strong>33.6733
<p style="margin-left: 0px"><strong>longitude: </strong>-117.3542
<p style="margin-left: 0px"><strong>elevation: </strong>379
<p style="margin-left: 0px"><strong>siteName: </strong>Elsinore
</details>
<details open>
<summary>PaleoData columns</summary>
<details style="margin-left: 10px">
<summary>year (AD)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB61e0247e
<p style="margin-left: 10px"><strong>variableName: </strong>year
<p style="margin-left: 10px"><strong>units: </strong>AD
<p style="margin-left: 10px"><strong>description: </strong>Year AD
</details>
<details style="margin-left: 10px">
<summary>age (yr BP)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBb6fe494a
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>yr BP
<p style="margin-left: 10px"><strong>description: </strong>Years before present (1950) yr BP
</details>
<details style="margin-left: 10px">
<summary>depth (cm)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB3b82999e
<p style="margin-left: 10px"><strong>variableName: </strong>depth
<p style="margin-left: 10px"><strong>units: </strong>cm
<p style="margin-left: 10px"><strong>description: </strong>depth
</details>
<details style="margin-left: 10px">
<summary>Sand (percent)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>GHe74bbbb1
<p style="margin-left: 10px"><strong>variableName: </strong>Sand
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>TRUE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>direction: </strong>positive
<p style="margin-left: 20px"><strong>interpDirection: </strong>positive
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>seasonality: </strong>annual
<p style="margin-left: 20px"><strong>variable: </strong>M
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>d0x2800x2E10x29 (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD757c20b9dp
<p style="margin-left: 10px"><strong>variableName: </strong>d0x2800x2E10x29
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>d0x2800x2E50x29 (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD1fa4d0bedp
<p style="margin-left: 10px"><strong>variableName: </strong>d0x2800x2E50x29
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>d0x2800x2E90x29 (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD9b7b0312dp
<p style="margin-left: 10px"><strong>variableName: </strong>d0x2800x2E90x29
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>x00x2E020xB5m0x2D30x2E890xB5m (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDfd2a0239dp
<p style="margin-left: 10px"><strong>variableName: </strong>x00x2E020xB5m0x2D30x2E890xB5m
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>x30x2E900xB5m0x2D70x2E790xB5m (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDdd8c4ff1dp
<p style="margin-left: 10px"><strong>variableName: </strong>x30x2E900xB5m0x2D70x2E790xB5m
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>x70x2E800xB5m0x2D150x2E590xB5m (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD543c622edp
<p style="margin-left: 10px"><strong>variableName: </strong>x70x2E800xB5m0x2D150x2E590xB5m
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>x150x2E600xB5m0x2D300x2E990xB5m (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDf8072f4edp
<p style="margin-left: 10px"><strong>variableName: </strong>x150x2E600xB5m0x2D300x2E990xB5m
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>x310x2E000xB5m0x2D620x2E490xB5m (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDece0f148dp
<p style="margin-left: 10px"><strong>variableName: </strong>x310x2E000xB5m0x2D620x2E490xB5m
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>x620x2E500xB5m0x2D1240x2E990xB5m (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>NAm2kHydro224
<p style="margin-left: 10px"><strong>variableName: </strong>x620x2E500xB5m0x2D1240x2E990xB5m
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>x1250x2E000xB5m0x2D2490x2E990xB5m (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>NAm2kHydro225
<p style="margin-left: 10px"><strong>variableName: </strong>x1250x2E000xB5m0x2D2490x2E990xB5m
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>x2500x2E000xB5m0x2D4990x2E990xB5m (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>NAm2kHydro226
<p style="margin-left: 10px"><strong>variableName: </strong>x2500x2E000xB5m0x2D4990x2E990xB5m
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>x5000x2E000xB5m0x2D10000x2E000xB5m (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>GH15ca2210
<p style="margin-left: 10px"><strong>variableName: </strong>x5000x2E000xB5m0x2D10000x2E000xB5m
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>x10000x2E010xB5m0x2D20000x2E000xB5m (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>GH7ab71922
<p style="margin-left: 10px"><strong>variableName: </strong>x10000x2E010xB5m0x2D20000x2E000xB5m
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Mode (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>GH2bd5a57d
<p style="margin-left: 10px"><strong>variableName: </strong>Mode
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Clay (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>GH9557767b
<p style="margin-left: 10px"><strong>variableName: </strong>Clay
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Silt (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>GH772045af
<p style="margin-left: 10px"><strong>variableName: </strong>Silt
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>

Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### Sitemap

```{r}
  map.meta.split <- split(map.meta, map.meta$archiveType)


factpal <- colorFactor("Paired",map.meta$archiveType)
buff <- 15
l <- leaflet() %>% 
  addTiles() %>% 
  fitBounds(map.meta$lon[i]-buff,map.meta$lat[i]-buff,map.meta$lon[i]+buff,map.meta$lat[i]+buff)
  

  
  
names(map.meta.split) %>%
  purrr::walk( function(df) {
    l <<- l %>%
      addMarkers(data=map.meta.split[[df]],
                 lng=~lon, lat=~lat,
                 label=~as.character(archiveType),
                 popup=~paste(str_c('Dataset: <a href="',link,'">',dataSetName,'</a>'),
                                 # str_c("Elevation: ",elev),
                                  str_c("Archive Type: ",archiveType),
                                  sep = "<br>"),
                 group = df,
                 clusterOptions = markerClusterOptions(removeOutsideVisibleBounds = F),
                 labelOptions = labelOptions(noHide = F,
                                             direction = 'auto'))
  })

l %>%
  addLayersControl(position = "bottomleft",
    overlayGroups = names(map.meta.split),
    options = layersControlOptions(collapsed = FALSE,
                                   opacity = 0.8)
  )
```

### Search the LiPDverse (Beta! doesn't work well yet)
```{r}
#Add google search bar
htmltools::includeHTML("../../googleSearchChunk.html")
```


Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### Sand (percent)
```{r}
plotCol(thisTS,ind = 20)
```

### d0x2800x2E10x29 (unitless)
```{r}
plotCol(thisTS,ind = 1)
```

### d0x2800x2E50x29 (unitless)
```{r}
plotCol(thisTS,ind = 5)
```

### d0x2800x2E90x29 (unitless)
```{r}
plotCol(thisTS,ind = 6)
```

### x00x2E020xB5m0x2D30x2E890xB5m (unitless)
```{r}
plotCol(thisTS,ind = 7)
```

### x30x2E900xB5m0x2D70x2E790xB5m (unitless)
```{r}
plotCol(thisTS,ind = 8)
```

### x70x2E800xB5m0x2D150x2E590xB5m (unitless)
```{r}
plotCol(thisTS,ind = 9)
```

### x150x2E600xB5m0x2D300x2E990xB5m (unitless)
```{r}
plotCol(thisTS,ind = 10)
```

### x310x2E000xB5m0x2D620x2E490xB5m (unitless)
```{r}
plotCol(thisTS,ind = 11)
```

### x620x2E500xB5m0x2D1240x2E990xB5m (unitless)
```{r}
plotCol(thisTS,ind = 12)
```

### x1250x2E000xB5m0x2D2490x2E990xB5m (unitless)
```{r}
plotCol(thisTS,ind = 13)
```

### x2500x2E000xB5m0x2D4990x2E990xB5m (unitless)
```{r}
plotCol(thisTS,ind = 14)
```

### x5000x2E000xB5m0x2D10000x2E000xB5m (unitless)
```{r}
plotCol(thisTS,ind = 15)
```

### x10000x2E010xB5m0x2D20000x2E000xB5m (unitless)
```{r}
plotCol(thisTS,ind = 16)
```

### Mode (unitless)
```{r}
plotCol(thisTS,ind = 17)
```

### Clay (unitless)
```{r}
plotCol(thisTS,ind = 18)
```

### Silt (unitless)
```{r}
plotCol(thisTS,ind = 19)
```
