---
title: "Ew0408-85JC.Praetorius.2015"
output: 
  flexdashboard::flex_dashboard:
    theme: bootstrap
    source_code: embed
    orientation: rows
---

```{r setup, include = FALSE}
library(flexdashboard)
library(maptools)
library(tidyverse)
library(purrr)
library(leaflet)
library(plotly)
library(lipdR)
library(dygraphs)
library(geoChronR)

#read functions
source("../../functions.R")


load("../../temp.Rdata")

#remove columns we don't want to plot
varNames <- sapply(TS, "[[","paleoData_variableName")

# good <- which(!(varNames %in% c("year","depth","age")))
# TS <- TS[good]


#All datasets
dsn <- sapply(TS,"[[","dataSetName")
ui <- which(!duplicated(dsn))
udsn <- dsn[ui]
lat <- as.numeric(sapply(TS,"[[","geo_latitude")[ui])
lon <- as.numeric(sapply(TS,"[[","geo_longitude")[ui])
#elev <- sapply(TS,"[[","geo_elevation")[ui]
archiveType <- sapply(TS,"[[","archiveType")[ui]
link <- paste0(udsn,".html") %>% 
  str_replace_all("'","_")

#Organize metadata for map
map.meta <- data.frame(dataSetName = udsn, #datasetname
                       lat = lat,#lat
                       lon = lon,#lon
                      # elev = elev,#elevation
                       archiveType = factor(archiveType),#archiveType
                       link = link)#Link


#set index number

i = 30
thisTS <- TS[which(udsn[i] == dsn)]
```
#Ew0408-85JC.Praetorius.2015

Metadata {.sidebar}
-------------------------------------
[Download LiPD file](Ew0408-85JC.Praetorius.2015.lpd)
            

[Edit LiPD file](http://lipd.net/playground?source=http://lipdverse.org/wNAm0_1_0/Ew0408-85JC.Praetorius.2015.lpd)
            

[Download data only (csv)](Ew0408-85JC.Praetorius.2015.csv)
            

[Report an issue (include dataset name)](https://github.com/nickmckay/LiPDverse/issues)

<details open style="margin-left: 0px">
<summary>root</summary>
<p style="margin-left: 0px"><strong>archiveType: </strong>marine sediment
<p style="margin-left: 0px"><strong>lipdVersion: </strong>1.3
</details>
<details>
<summary>pub</summary>
<details style="margin-left: 10px">
<summary>pub1</summary>
<p style="margin-left: 10px"><strong>journal: </strong>Nature
<p style="margin-left: 10px"><strong>volume: </strong>527
<p style="margin-left: 10px"><strong>pages: </strong>362-366
<p style="margin-left: 10px"><strong>pubYear: </strong>NA
<p style="margin-left: 10px"><strong>title: </strong>North Pacific deglacial hypoxic events linked to abrupt ocean warming
</details>
</details>
<details open style="margin-left: 0px">
<summary>geo</summary>
<p style="margin-left: 0px"><strong>latitude: </strong>59.55
<p style="margin-left: 0px"><strong>longitude: </strong>-144.15
<p style="margin-left: 0px"><strong>elevation: </strong>-682
<p style="margin-left: 0px"><strong>siteName: </strong>Ew0408-85JC
</details>
<details open>
<summary>PaleoData columns</summary>
<details style="margin-left: 10px">
<summary>depth (m) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB205e60ed
<p style="margin-left: 10px"><strong>variableName: </strong>depth
<p style="margin-left: 10px"><strong>units: </strong>m
</details>
<details style="margin-left: 10px">
<summary>age (yr BP) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBd5ae5e07
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>yr BP
</details>
<details style="margin-left: 10px">
<summary>Temperature (degC) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB7f30ec1a
<p style="margin-left: 10px"><strong>variableName: </strong>Temperature
<p style="margin-left: 10px"><strong>units: </strong>degC
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>TRUE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>direction: </strong>positive
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>variable: </strong>T
<p style="margin-left: 20px"><strong>variableDetail: </strong>SST
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>Core (unitless) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB2909d5c0
<p style="margin-left: 10px"><strong>variableName: </strong>Core
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>Sample interval (cm) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBc95efe9f
<p style="margin-left: 10px"><strong>variableName: </strong>Sample interval
<p style="margin-left: 10px"><strong>units: </strong>cm
</details>
<details style="margin-left: 10px">
<summary>UK37 (unitless) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBe3f532bd
<p style="margin-left: 10px"><strong>variableName: </strong>UK37
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>UK37_error (1sigma) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB1bab37e5
<p style="margin-left: 10px"><strong>variableName: </strong>UK37_error
<p style="margin-left: 10px"><strong>units: </strong>1sigma
</details>
<details style="margin-left: 10px">
<summary>U371sigmaUncertainty- (unitless) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB3e867964
<p style="margin-left: 10px"><strong>variableName: </strong>U371sigmaUncertainty-
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>K37s (µg/g) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB5cd68ff7
<p style="margin-left: 10px"><strong>variableName: </strong>K37s
<p style="margin-left: 10px"><strong>units: </strong>µg/g
</details>
<details style="margin-left: 10px">
<summary>Temperature_uncertainty_plus (degC) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB42a6c0cf
<p style="margin-left: 10px"><strong>variableName: </strong>Temperature_uncertainty_plus
<p style="margin-left: 10px"><strong>units: </strong>degC
</details>
<details style="margin-left: 10px">
<summary>Temperature_uncertainty_minus (degC) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBc13e4c20
<p style="margin-left: 10px"><strong>variableName: </strong>Temperature_uncertainty_minus
<p style="margin-left: 10px"><strong>units: </strong>degC
</details>
<details style="margin-left: 10px">
<summary>depth (m) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB1d190b4f
<p style="margin-left: 10px"><strong>variableName: </strong>depth
<p style="margin-left: 10px"><strong>units: </strong>m
</details>
<details style="margin-left: 10px">
<summary>age (yr BP) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB96b73de1
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>yr BP
</details>
<details style="margin-left: 10px">
<summary>BSI (percentByWeight) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB7834c192
<p style="margin-left: 10px"><strong>variableName: </strong>BSI
<p style="margin-left: 10px"><strong>units: </strong>percentByWeight
</details>
<details style="margin-left: 10px">
<summary>depth (m) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB2d20e857
<p style="margin-left: 10px"><strong>variableName: </strong>depth
<p style="margin-left: 10px"><strong>units: </strong>m
</details>
<details style="margin-left: 10px">
<summary>age (yr BP) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB5a8e3c39
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>yr BP
</details>
<details style="margin-left: 10px">
<summary>Al (percent) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB71fc9c51
<p style="margin-left: 10px"><strong>variableName: </strong>Al
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>description: </strong>Units in percent by weight
</details>
<details style="margin-left: 10px">
<summary>Mn (ppm) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBf6dadb2e
<p style="margin-left: 10px"><strong>variableName: </strong>Mn
<p style="margin-left: 10px"><strong>units: </strong>ppm
</details>
<details style="margin-left: 10px">
<summary>Co (ppm) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBf460632d
<p style="margin-left: 10px"><strong>variableName: </strong>Co
<p style="margin-left: 10px"><strong>units: </strong>ppm
</details>
<details style="margin-left: 10px">
<summary>Cr (ppm) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBf779f0eb
<p style="margin-left: 10px"><strong>variableName: </strong>Cr
<p style="margin-left: 10px"><strong>units: </strong>ppm
</details>
<details style="margin-left: 10px">
<summary>U (ppm) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBb594b51a
<p style="margin-left: 10px"><strong>variableName: </strong>U
<p style="margin-left: 10px"><strong>units: </strong>ppm
</details>
<details style="margin-left: 10px">
<summary>Mo (ppm) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB9ee28e24
<p style="margin-left: 10px"><strong>variableName: </strong>Mo
<p style="margin-left: 10px"><strong>units: </strong>ppm
</details>
<details style="margin-left: 10px">
<summary>Cd (ppm) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB9b890d33
<p style="margin-left: 10px"><strong>variableName: </strong>Cd
<p style="margin-left: 10px"><strong>units: </strong>ppm
</details>
<details style="margin-left: 10px">
<summary>Mo_xs (ppm) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBe33b40a0
<p style="margin-left: 10px"><strong>variableName: </strong>Mo_xs
<p style="margin-left: 10px"><strong>units: </strong>ppm
</details>
<details style="margin-left: 10px">
<summary>U_xs (ppm) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBe6712311
<p style="margin-left: 10px"><strong>variableName: </strong>U_xs
<p style="margin-left: 10px"><strong>units: </strong>ppm
</details>
<details style="margin-left: 10px">
<summary>depth (m) [1-4]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB8649545b
<p style="margin-left: 10px"><strong>variableName: </strong>depth
<p style="margin-left: 10px"><strong>units: </strong>m
<p style="margin-left: 10px"><strong>description: </strong>depth in core
</details>
<details style="margin-left: 10px">
<summary>age (yr BP) [1-4]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBbb16b78b
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>yr BP
</details>
<details style="margin-left: 10px">
<summary>TOC (percent) [1-4]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB28cb3718
<p style="margin-left: 10px"><strong>variableName: </strong>TOC
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>description: </strong>Percent by weight
</details>
<details style="margin-left: 10px">
<summary>TN (percent) [1-4]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB102b2159
<p style="margin-left: 10px"><strong>variableName: </strong>TN
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>description: </strong>percent by weight
</details>
<details style="margin-left: 10px">
<summary>d13C (permil) [1-4]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB927c120e
<p style="margin-left: 10px"><strong>variableName: </strong>d13C
<p style="margin-left: 10px"><strong>units: </strong>permil
<p style="margin-left: 10px"><strong>description: </strong>Organic matter d13C
</details>
<details style="margin-left: 10px">
<summary>dN15 (permil) [1-4]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB16a076cb
<p style="margin-left: 10px"><strong>variableName: </strong>dN15
<p style="margin-left: 10px"><strong>units: </strong>permil
<p style="margin-left: 10px"><strong>description: </strong>Sedimentary d15N
</details>
<details style="margin-left: 10px">
<summary>dN15_corrected (permil) [1-4]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBd8fee875
<p style="margin-left: 10px"><strong>variableName: </strong>dN15_corrected
<p style="margin-left: 10px"><strong>units: </strong>permil
<p style="margin-left: 10px"><strong>description: </strong>Corrected dN15
</details>
<details style="margin-left: 10px">
<summary>depth (m) [1-5]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB4c5a6f2d
<p style="margin-left: 10px"><strong>variableName: </strong>depth
<p style="margin-left: 10px"><strong>units: </strong>m
<p style="margin-left: 10px"><strong>description: </strong>depth in core
</details>
<details style="margin-left: 10px">
<summary>age (yr BP) [1-5]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBc512582f
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>yr BP
</details>
<details style="margin-left: 10px">
<summary>d13C_benthic (permil) [1-5]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB3c8f95e9
<p style="margin-left: 10px"><strong>variableName: </strong>d13C_benthic
<p style="margin-left: 10px"><strong>units: </strong>permil
<p style="margin-left: 10px"><strong>description: </strong>Uvigerina peregrina d13C
</details>
<details style="margin-left: 10px">
<summary>d18O_benthic (permil) [1-5]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB66ce1b6b
<p style="margin-left: 10px"><strong>variableName: </strong>d18O_benthic
<p style="margin-left: 10px"><strong>units: </strong>permil
<p style="margin-left: 10px"><strong>description: </strong>Uvigerina peregrina d18O
</details>
<details style="margin-left: 10px">
<summary>depth (m) [1-6]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBf4c2c8b7
<p style="margin-left: 10px"><strong>variableName: </strong>depth
<p style="margin-left: 10px"><strong>units: </strong>m
<p style="margin-left: 10px"><strong>description: </strong>NPS depth. Data originally published in Davies et al., 2011.
</details>
<details style="margin-left: 10px">
<summary>age (yr BP) [1-6]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBc4516003
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>yr BP
</details>
<details style="margin-left: 10px">
<summary>d18O_plank (permil) [1-6]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB704d56ad
<p style="margin-left: 10px"><strong>variableName: </strong>d18O_plank
<p style="margin-left: 10px"><strong>units: </strong>permil
<p style="margin-left: 10px"><strong>description: </strong>NPS Planktonic d18O permil. Data from planktonic foraminifera species N.pachyderma sinistral (Nps)
</details>
<details style="margin-left: 10px">
<summary>d13C_plank (permil) [1-6]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBd5901305
<p style="margin-left: 10px"><strong>variableName: </strong>d13C_plank
<p style="margin-left: 10px"><strong>units: </strong>permil
<p style="margin-left: 10px"><strong>description: </strong>NPS Planktonic d13C permil. Data from planktonic foraminifera species N.pachyderma sinistral (Nps)
</details>
<details style="margin-left: 10px">
<summary>depth (m) [1-7]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBe5f54dba
<p style="margin-left: 10px"><strong>variableName: </strong>depth
<p style="margin-left: 10px"><strong>units: </strong>m
</details>
<details style="margin-left: 10px">
<summary>age (yr BP) [1-7]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB294b1334
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>yr BP
</details>
<details style="margin-left: 10px">
<summary>d18O_Gb (permil) [1-7]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBdc5425d8
<p style="margin-left: 10px"><strong>variableName: </strong>d18O_Gb
<p style="margin-left: 10px"><strong>units: </strong>permil
<p style="margin-left: 10px"><strong>description: </strong>Data from planktonic foraminifera species G.bulloides (Gb)
</details>
<details style="margin-left: 10px">
<summary>d13C_Gb (permil) [1-7]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBb0b64bea
<p style="margin-left: 10px"><strong>variableName: </strong>d13C_Gb
<p style="margin-left: 10px"><strong>units: </strong>permil
<p style="margin-left: 10px"><strong>description: </strong>Data from planktonic foraminifera species G.bulloides (Gb)
</details>

Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### Sitemap

```{r}
  map.meta.split <- split(map.meta, map.meta$archiveType)


factpal <- colorFactor("Paired",map.meta$archiveType)
buff <- 15
l <- leaflet() %>% 
  addTiles() %>% 
  fitBounds(map.meta$lon[i]-buff,map.meta$lat[i]-buff,map.meta$lon[i]+buff,map.meta$lat[i]+buff)
  

  
  
names(map.meta.split) %>%
  purrr::walk( function(df) {
    l <<- l %>%
      addMarkers(data=map.meta.split[[df]],
                 lng=~lon, lat=~lat,
                 label=~as.character(archiveType),
                 popup=~paste(str_c('Dataset: <a href="',link,'">',dataSetName,'</a>'),
                                 # str_c("Elevation: ",elev),
                                  str_c("Archive Type: ",archiveType),
                                  sep = "<br>"),
                 group = df,
                 clusterOptions = markerClusterOptions(removeOutsideVisibleBounds = F),
                 labelOptions = labelOptions(noHide = F,
                                             direction = 'auto'))
  })

l %>%
  addLayersControl(position = "bottomleft",
    overlayGroups = names(map.meta.split),
    options = layersControlOptions(collapsed = FALSE,
                                   opacity = 0.8)
  )
```

### Search the LiPDverse (Beta! doesn't work well yet)
```{r}
#Add google search bar
htmltools::includeHTML("../../googleSearchChunk.html")
```


Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### Temperature (degC) [1-1]
```{r}
plotCol(thisTS,ind = 9)
```

### Core (unitless) [1-1]
```{r}
plotCol(thisTS,ind = 1)
```

### Sample interval (cm) [1-1]
```{r}
plotCol(thisTS,ind = 2)
```

### UK37 (unitless) [1-1]
```{r}
plotCol(thisTS,ind = 5)
```

### UK37_error (1sigma) [1-1]
```{r}
plotCol(thisTS,ind = 6)
```

### U371sigmaUncertainty- (unitless) [1-1]
```{r}
plotCol(thisTS,ind = 7)
```

### K37s (µg/g) [1-1]
```{r}
plotCol(thisTS,ind = 8)
```

### Temperature_uncertainty_plus (degC) [1-1]
```{r}
plotCol(thisTS,ind = 10)
```

### Temperature_uncertainty_minus (degC) [1-1]
```{r}
plotCol(thisTS,ind = 11)
```

### BSI (percentByWeight) [1-2]
```{r}
plotCol(thisTS,ind = 14)
```

### Al (percent) [1-3]
```{r}
plotCol(thisTS,ind = 17)
```

### Mn (ppm) [1-3]
```{r}
plotCol(thisTS,ind = 18)
```

### Co (ppm) [1-3]
```{r}
plotCol(thisTS,ind = 19)
```

### Cr (ppm) [1-3]
```{r}
plotCol(thisTS,ind = 20)
```

### U (ppm) [1-3]
```{r}
plotCol(thisTS,ind = 21)
```

### Mo (ppm) [1-3]
```{r}
plotCol(thisTS,ind = 22)
```

### Cd (ppm) [1-3]
```{r}
plotCol(thisTS,ind = 23)
```

### Mo_xs (ppm) [1-3]
```{r}
plotCol(thisTS,ind = 24)
```

### U_xs (ppm) [1-3]
```{r}
plotCol(thisTS,ind = 25)
```

### TOC (percent) [1-4]
```{r}
plotCol(thisTS,ind = 28)
```

### TN (percent) [1-4]
```{r}
plotCol(thisTS,ind = 29)
```

### d13C (permil) [1-4]
```{r}
plotCol(thisTS,ind = 30)
```

### dN15 (permil) [1-4]
```{r}
plotCol(thisTS,ind = 31)
```

### dN15_corrected (permil) [1-4]
```{r}
plotCol(thisTS,ind = 32)
```

### d13C_benthic (permil) [1-5]
```{r}
plotCol(thisTS,ind = 35)
```

### d18O_benthic (permil) [1-5]
```{r}
plotCol(thisTS,ind = 36)
```

### d18O_plank (permil) [1-6]
```{r}
plotCol(thisTS,ind = 39)
```

### d13C_plank (permil) [1-6]
```{r}
plotCol(thisTS,ind = 40)
```

### d18O_Gb (permil) [1-7]
```{r}
plotCol(thisTS,ind = 43)
```

### d13C_Gb (permil) [1-7]
```{r}
plotCol(thisTS,ind = 44)
```
