---
title: "MV99-GC31.Barron.2012"
output: 
  flexdashboard::flex_dashboard:
    theme: bootstrap
    source_code: embed
    orientation: rows
---

```{r setup, include = FALSE}
library(flexdashboard)
library(maptools)
library(tidyverse)
library(purrr)
library(leaflet)
library(plotly)
library(lipdR)
library(dygraphs)
library(geoChronR)

#read functions
source("../../functions.R")


load("../../temp.Rdata")

#remove columns we don't want to plot
varNames <- sapply(TS, "[[","paleoData_variableName")

# good <- which(!(varNames %in% c("year","depth","age")))
# TS <- TS[good]


#All datasets
dsn <- sapply(TS,"[[","dataSetName")
ui <- which(!duplicated(dsn))
udsn <- dsn[ui]
lat <- as.numeric(sapply(TS,"[[","geo_latitude")[ui])
lon <- as.numeric(sapply(TS,"[[","geo_longitude")[ui])
#elev <- sapply(TS,"[[","geo_elevation")[ui]
archiveType <- sapply(TS,"[[","archiveType")[ui]
link <- paste0(udsn,".html") %>% 
  str_replace_all("'","_")

#Organize metadata for map
map.meta <- data.frame(dataSetName = udsn, #datasetname
                       lat = lat,#lat
                       lon = lon,#lon
                      # elev = elev,#elevation
                       archiveType = factor(archiveType),#archiveType
                       link = link)#Link


#set index number

i = 84
thisTS <- TS[which(udsn[i] == dsn)]
```
#MV99-GC31.Barron.2012

Metadata {.sidebar}
-------------------------------------
[Download LiPD file](MV99-GC31.Barron.2012.lpd)
            

[Edit LiPD file](http://lipd.net/playground?source=http://lipdverse.org/wNAm0_1_0/MV99-GC31.Barron.2012.lpd)
            

[Download data only (csv)](MV99-GC31.Barron.2012.csv)
            

[Report an issue (include dataset name)](https://github.com/nickmckay/LiPDverse/issues)

<details open style="margin-left: 0px">
<summary>root</summary>
<p style="margin-left: 0px"><strong>archiveType: </strong>marine sediment
<p style="margin-left: 0px"><strong>originalDataURL: </strong>https://doi.pangaea.de/10.1594/PANGAEA.824830?format=html#download
<p style="margin-left: 0px"><strong>lipdVersion: </strong>1.3
</details>
<details>
<summary>pub</summary>
<details style="margin-left: 10px">
<summary>pub1</summary>
<p style="margin-left: 10px"><strong>journal: </strong>Paleoceanography
<p style="margin-left: 10px"><strong>volume: </strong>27
<p style="margin-left: 10px"><strong>pages: </strong>n/a-n/a
<p style="margin-left: 10px"><strong>pubYear: </strong>NA
<p style="margin-left: 10px"><strong>title: </strong>Response of the North American monsoon to regional changes in ocean surface temperature
</details>
</details>
<details>
<summary>funding</summary>
<details style="margin-left: 10px">
<summary>funding1</summary>
<p style="margin-left: 10px"><strong>agency: </strong>Funding Agency
<p style="margin-left: 10px"><strong>grant: </strong>Grant name or number
</details>
</details>
<details open style="margin-left: 0px">
<summary>geo</summary>
<p style="margin-left: 0px"><strong>latitude: </strong>23.4672
<p style="margin-left: 0px"><strong>longitude: </strong>-111.5985
<p style="margin-left: 0px"><strong>elevation: </strong>-705
<p style="margin-left: 0px"><strong>siteName: </strong>MV99-GC31
</details>
<details open>
<summary>PaleoData columns</summary>
<details style="margin-left: 10px">
<summary>year (AD) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB1f20b950
<p style="margin-left: 10px"><strong>variableName: </strong>year
<p style="margin-left: 10px"><strong>units: </strong>AD
<p style="margin-left: 10px"><strong>description: </strong>Year AD
</details>
<details style="margin-left: 10px">
<summary>age (BP) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBb12a627e
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>BP
<p style="margin-left: 10px"><strong>description: </strong>Years before present (1950) BP
</details>
<details style="margin-left: 10px">
<summary>depth (cm) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBa8270941
<p style="margin-left: 10px"><strong>variableName: </strong>depth
<p style="margin-left: 10px"><strong>units: </strong>cm
<p style="margin-left: 10px"><strong>description: </strong>depth
</details>
<details style="margin-left: 10px">
<summary>SumDiatoms (number/cm2) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDbc86d401
<p style="margin-left: 10px"><strong>variableName: </strong>SumDiatoms
<p style="margin-left: 10px"><strong>units: </strong>number/cm2
<p style="margin-left: 10px"><strong>description: </strong>Percent opal and number of diatoms/gram interpreted as inversly related to SST. Infering relative SST from upwelling. Chronology is well constrained. Passes length and resolution criteria.
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>TRUE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>direction: </strong>negative
<p style="margin-left: 20px"><strong>interpDirection: </strong>negative
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>seasonality: </strong>not specified
<p style="margin-left: 20px"><strong>variable: </strong>T
<p style="margin-left: 20px"><strong>variableDetail: </strong>upwelling
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>CAL (unitless) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD071ba777
<p style="margin-left: 10px"><strong>variableName: </strong>CAL
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Acinocyclus. curvatulus (unitless) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD60dfeb45
<p style="margin-left: 10px"><strong>variableName: </strong>Acinocyclus. curvatulus
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>A. octonarius (unitless) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD8794764f
<p style="margin-left: 10px"><strong>variableName: </strong>A. octonarius
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Actinoptychus spp. (unitless) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDa61506bc
<p style="margin-left: 10px"><strong>variableName: </strong>Actinoptychus spp.
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Azpeitia nodulifer (unitless) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD1ea1bbc9
<p style="margin-left: 10px"><strong>variableName: </strong>Azpeitia nodulifer
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>description: </strong>tropcial, oligotrophic
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Az. tabularis (unitless) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD7df02d0a
<p style="margin-left: 10px"><strong>variableName: </strong>Az. tabularis
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Coscinodiscus spp. (unitless) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDd6b6e880
<p style="margin-left: 10px"><strong>variableName: </strong>Coscinodiscus spp.
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Cyclotella spp. (unitless) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD3c17a70a
<p style="margin-left: 10px"><strong>variableName: </strong>Cyclotella spp.
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>description: </strong>warm, stratified waters
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Hemidiscus cuneiformis (unitless) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD33179137
<p style="margin-left: 10px"><strong>variableName: </strong>Hemidiscus cuneiformis
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Paralia sulcata (unitless) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD2ee728c9
<p style="margin-left: 10px"><strong>variableName: </strong>Paralia sulcata
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>description: </strong>transported
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Roperia tesselata (unitless) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDa7b4083f
<p style="margin-left: 10px"><strong>variableName: </strong>Roperia tesselata
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Stephanopyxis spp. (unitless) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDb96e7b65
<p style="margin-left: 10px"><strong>variableName: </strong>Stephanopyxis spp.
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Thalassiosira spp. (unitless) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDbc6c866e
<p style="margin-left: 10px"><strong>variableName: </strong>Thalassiosira spp.
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Chaetoceros spores (unitless) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDcf87a317
<p style="margin-left: 10px"><strong>variableName: </strong>Chaetoceros spores
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>description: </strong>upwelling record -implies cool spring SSTs
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>year (AD) [2-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBafb3732b
<p style="margin-left: 10px"><strong>variableName: </strong>year
<p style="margin-left: 10px"><strong>units: </strong>AD
<p style="margin-left: 10px"><strong>description: </strong>Year AD
</details>
<details style="margin-left: 10px">
<summary>age (BP) [2-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB4df0bf9e
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>BP
<p style="margin-left: 10px"><strong>description: </strong>Years before present (1950) BP
</details>
<details style="margin-left: 10px">
<summary>depth (cm) [2-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBa43d9d15
<p style="margin-left: 10px"><strong>variableName: </strong>depth
<p style="margin-left: 10px"><strong>units: </strong>cm
<p style="margin-left: 10px"><strong>description: </strong>depth
</details>
<details style="margin-left: 10px">
<summary>percentOpal (percent) [2-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD4d80bd37
<p style="margin-left: 10px"><strong>variableName: </strong>percentOpal
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>description: </strong>Percent opal and number of diatoms/gram interpreted as inversly related to SST. Infering relative SST from upwelling. Chronology is well constrained. Passes length and resolution criteria.
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>TRUE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>direction: </strong>negative
<p style="margin-left: 20px"><strong>interpDirection: </strong>negative
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>seasonality: </strong>not specified
<p style="margin-left: 20px"><strong>variable: </strong>T
<p style="margin-left: 20px"><strong>variableDetail: </strong>upwelling
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>CAL (unitless) [2-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD85779bfd
<p style="margin-left: 10px"><strong>variableName: </strong>CAL
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>year (AD) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBb36ffb42
<p style="margin-left: 10px"><strong>variableName: </strong>year
<p style="margin-left: 10px"><strong>units: </strong>AD
<p style="margin-left: 10px"><strong>description: </strong>Year AD
</details>
<details style="margin-left: 10px">
<summary>age (BP) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBb0a96e1c
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>BP
<p style="margin-left: 10px"><strong>description: </strong>Years before present (1950) BP
</details>
<details style="margin-left: 10px">
<summary>depth (cm) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBe3464f3c
<p style="margin-left: 10px"><strong>variableName: </strong>depth
<p style="margin-left: 10px"><strong>units: </strong>cm
<p style="margin-left: 10px"><strong>description: </strong>depth
</details>
<details style="margin-left: 10px">
<summary>CAL (unitless) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD90380814
<p style="margin-left: 10px"><strong>variableName: </strong>CAL
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>LSR (cm/ky) (unitless) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD726ed772
<p style="margin-left: 10px"><strong>variableName: </strong>LSR (cm/ky)
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Bulk MAR (unitless) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD87573da3
<p style="margin-left: 10px"><strong>variableName: </strong>Bulk MAR
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>% Al (unitless) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD9a0848fc
<p style="margin-left: 10px"><strong>variableName: </strong>% Al
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>% Fe (unitless) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDde5d433d
<p style="margin-left: 10px"><strong>variableName: </strong>% Fe
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>% Mg (unitless) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD76d3e724
<p style="margin-left: 10px"><strong>variableName: </strong>% Mg
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>% Ca (unitless) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD8c60f8de
<p style="margin-left: 10px"><strong>variableName: </strong>% Ca
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>% Ca-detr (unitless) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDa876031c
<p style="margin-left: 10px"><strong>variableName: </strong>% Ca-detr
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>% Ca-ex (unitless) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD605de7d8
<p style="margin-left: 10px"><strong>variableName: </strong>% Ca-ex
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>% CaCO3-ex (unitless) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDe484d854
<p style="margin-left: 10px"><strong>variableName: </strong>% CaCO3-ex
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>% Na (unitless) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD29cdd38a
<p style="margin-left: 10px"><strong>variableName: </strong>% Na
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>% K (unitless) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD17567730
<p style="margin-left: 10px"><strong>variableName: </strong>% K
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>% P (unitless) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD04a5bc00
<p style="margin-left: 10px"><strong>variableName: </strong>% P
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>% Ti (unitless) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDba7e2f30
<p style="margin-left: 10px"><strong>variableName: </strong>% Ti
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>% Mn (unitless) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD3b5b919b
<p style="margin-left: 10px"><strong>variableName: </strong>% Mn
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>ppm Mn (unitless) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDd0283d75
<p style="margin-left: 10px"><strong>variableName: </strong>ppm Mn
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>ppm As (unitless) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD75d47c64
<p style="margin-left: 10px"><strong>variableName: </strong>ppm As
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>ppm Ba (unitless) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD63793db5
<p style="margin-left: 10px"><strong>variableName: </strong>ppm Ba
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>ppm Be (unitless) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDc7a4bbb3
<p style="margin-left: 10px"><strong>variableName: </strong>ppm Be
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>ppm Cd (unitless) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD27b03bf3
<p style="margin-left: 10px"><strong>variableName: </strong>ppm Cd
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>ppm Co (unitless) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD352577e1
<p style="margin-left: 10px"><strong>variableName: </strong>ppm Co
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>ppm Cr (unitless) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD16ae04fb
<p style="margin-left: 10px"><strong>variableName: </strong>ppm Cr
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>ppm Cu (unitless) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD00e608fe
<p style="margin-left: 10px"><strong>variableName: </strong>ppm Cu
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>ppm La (unitless) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD0e839d7e
<p style="margin-left: 10px"><strong>variableName: </strong>ppm La
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>ppm Mo (unitless) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD7dbaea3a
<p style="margin-left: 10px"><strong>variableName: </strong>ppm Mo
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>ppm Ni (unitless) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD4769fcbd
<p style="margin-left: 10px"><strong>variableName: </strong>ppm Ni
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>ppm Pb (unitless) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD476959ce
<p style="margin-left: 10px"><strong>variableName: </strong>ppm Pb
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>ppm Sc (unitless) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDa336cc92
<p style="margin-left: 10px"><strong>variableName: </strong>ppm Sc
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>ppm Sr (unitless) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD3d870b87
<p style="margin-left: 10px"><strong>variableName: </strong>ppm Sr
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>ppm V (unitless) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDf538e744
<p style="margin-left: 10px"><strong>variableName: </strong>ppm V
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>ppm Y (unitless) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD7c0b6b9a
<p style="margin-left: 10px"><strong>variableName: </strong>ppm Y
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>ppm Zr (unitless) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDf80d99b7
<p style="margin-left: 10px"><strong>variableName: </strong>ppm Zr
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>ppm Zn (unitless) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD171b0f6f
<p style="margin-left: 10px"><strong>variableName: </strong>ppm Zn
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>% TC (unitless) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDb18da1e0
<p style="margin-left: 10px"><strong>variableName: </strong>% TC
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>% IC (unitless) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDfad2ad32
<p style="margin-left: 10px"><strong>variableName: </strong>% IC
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>CaCO3-IC (unitless) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD091c71b7
<p style="margin-left: 10px"><strong>variableName: </strong>CaCO3-IC
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>% OC (unitless) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDaceadfb7
<p style="margin-left: 10px"><strong>variableName: </strong>% OC
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>ppm Cd/% Mn (unitless) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDf33f8463
<p style="margin-left: 10px"><strong>variableName: </strong>ppm Cd/% Mn
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>ppmBa/%Al (unitless) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD5a9149dc
<p style="margin-left: 10px"><strong>variableName: </strong>ppmBa/%Al
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>OC-MAR (g) (unitless) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD68c324f7
<p style="margin-left: 10px"><strong>variableName: </strong>OC-MAR (g)
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>OC-MAR (mg) (unitless) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDaa917599
<p style="margin-left: 10px"><strong>variableName: </strong>OC-MAR (mg)
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Cd MAR (ug/cm2/ky) (unitless) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD5d203752
<p style="margin-left: 10px"><strong>variableName: </strong>Cd MAR (ug/cm2/ky)
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>description: </strong>coastal upwelling
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Mo MAR (ug/cm2/ky) (unitless) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD94588022
<p style="margin-left: 10px"><strong>variableName: </strong>Mo MAR (ug/cm2/ky)
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Mn/Mo (unitless) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDb383a9dd
<p style="margin-left: 10px"><strong>variableName: </strong>Mn/Mo
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>

Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### Sitemap

```{r}
  map.meta.split <- split(map.meta, map.meta$archiveType)


factpal <- colorFactor("Paired",map.meta$archiveType)
buff <- 15
l <- leaflet() %>% 
  addTiles() %>% 
  fitBounds(map.meta$lon[i]-buff,map.meta$lat[i]-buff,map.meta$lon[i]+buff,map.meta$lat[i]+buff)
  

  
  
names(map.meta.split) %>%
  purrr::walk( function(df) {
    l <<- l %>%
      addMarkers(data=map.meta.split[[df]],
                 lng=~lon, lat=~lat,
                 label=~as.character(archiveType),
                 popup=~paste(str_c('Dataset: <a href="',link,'">',dataSetName,'</a>'),
                                 # str_c("Elevation: ",elev),
                                  str_c("Archive Type: ",archiveType),
                                  sep = "<br>"),
                 group = df,
                 clusterOptions = markerClusterOptions(removeOutsideVisibleBounds = F),
                 labelOptions = labelOptions(noHide = F,
                                             direction = 'auto'))
  })

l %>%
  addLayersControl(position = "bottomleft",
    overlayGroups = names(map.meta.split),
    options = layersControlOptions(collapsed = FALSE,
                                   opacity = 0.8)
  )
```

### Search the LiPDverse (Beta! doesn't work well yet)
```{r}
#Add google search bar
htmltools::includeHTML("../../googleSearchChunk.html")
```


Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### SumDiatoms (number/cm2) [1-1]
```{r}
plotCol(thisTS,ind = 17)
```

### CAL (unitless) [1-1]
```{r}
plotCol(thisTS,ind = 1)
```

### Acinocyclus. curvatulus (unitless) [1-1]
```{r}
plotCol(thisTS,ind = 5)
```

### A. octonarius (unitless) [1-1]
```{r}
plotCol(thisTS,ind = 6)
```

### Actinoptychus spp. (unitless) [1-1]
```{r}
plotCol(thisTS,ind = 7)
```

### Azpeitia nodulifer (unitless) [1-1]
```{r}
plotCol(thisTS,ind = 8)
```

### Az. tabularis (unitless) [1-1]
```{r}
plotCol(thisTS,ind = 9)
```

### Coscinodiscus spp. (unitless) [1-1]
```{r}
plotCol(thisTS,ind = 10)
```

### Cyclotella spp. (unitless) [1-1]
```{r}
plotCol(thisTS,ind = 11)
```

### Hemidiscus cuneiformis (unitless) [1-1]
```{r}
plotCol(thisTS,ind = 12)
```

### Paralia sulcata (unitless) [1-1]
```{r}
plotCol(thisTS,ind = 13)
```

### Roperia tesselata (unitless) [1-1]
```{r}
plotCol(thisTS,ind = 14)
```

### Stephanopyxis spp. (unitless) [1-1]
```{r}
plotCol(thisTS,ind = 15)
```

### Thalassiosira spp. (unitless) [1-1]
```{r}
plotCol(thisTS,ind = 16)
```

### Chaetoceros spores (unitless) [1-1]
```{r}
plotCol(thisTS,ind = 18)
```

### percentOpal (percent) [2-1]
```{r}
plotCol(thisTS,ind = 23)
```

### CAL (unitless) [2-1]
```{r}
plotCol(thisTS,ind = 19)
```

### CAL (unitless) [3-1]
```{r}
plotCol(thisTS,ind = 24)
```

### LSR (cm/ky) (unitless) [3-1]
```{r}
plotCol(thisTS,ind = 28)
```

### Bulk MAR (unitless) [3-1]
```{r}
plotCol(thisTS,ind = 29)
```

### % Al (unitless) [3-1]
```{r}
plotCol(thisTS,ind = 30)
```

### % Fe (unitless) [3-1]
```{r}
plotCol(thisTS,ind = 31)
```

### % Mg (unitless) [3-1]
```{r}
plotCol(thisTS,ind = 32)
```

### % Ca (unitless) [3-1]
```{r}
plotCol(thisTS,ind = 33)
```

### % Ca-detr (unitless) [3-1]
```{r}
plotCol(thisTS,ind = 34)
```

### % Ca-ex (unitless) [3-1]
```{r}
plotCol(thisTS,ind = 35)
```

### % CaCO3-ex (unitless) [3-1]
```{r}
plotCol(thisTS,ind = 36)
```

### % Na (unitless) [3-1]
```{r}
plotCol(thisTS,ind = 37)
```

### % K (unitless) [3-1]
```{r}
plotCol(thisTS,ind = 38)
```

### % P (unitless) [3-1]
```{r}
plotCol(thisTS,ind = 39)
```

### % Ti (unitless) [3-1]
```{r}
plotCol(thisTS,ind = 40)
```

### % Mn (unitless) [3-1]
```{r}
plotCol(thisTS,ind = 41)
```

### ppm Mn (unitless) [3-1]
```{r}
plotCol(thisTS,ind = 42)
```

### ppm As (unitless) [3-1]
```{r}
plotCol(thisTS,ind = 43)
```

### ppm Ba (unitless) [3-1]
```{r}
plotCol(thisTS,ind = 44)
```

### ppm Be (unitless) [3-1]
```{r}
plotCol(thisTS,ind = 45)
```

### ppm Cd (unitless) [3-1]
```{r}
plotCol(thisTS,ind = 46)
```

### ppm Co (unitless) [3-1]
```{r}
plotCol(thisTS,ind = 47)
```

### ppm Cr (unitless) [3-1]
```{r}
plotCol(thisTS,ind = 48)
```

### ppm Cu (unitless) [3-1]
```{r}
plotCol(thisTS,ind = 49)
```

### ppm La (unitless) [3-1]
```{r}
plotCol(thisTS,ind = 50)
```

### ppm Mo (unitless) [3-1]
```{r}
plotCol(thisTS,ind = 51)
```

### ppm Ni (unitless) [3-1]
```{r}
plotCol(thisTS,ind = 52)
```

### ppm Pb (unitless) [3-1]
```{r}
plotCol(thisTS,ind = 53)
```

### ppm Sc (unitless) [3-1]
```{r}
plotCol(thisTS,ind = 54)
```

### ppm Sr (unitless) [3-1]
```{r}
plotCol(thisTS,ind = 55)
```

### ppm V (unitless) [3-1]
```{r}
plotCol(thisTS,ind = 56)
```

### ppm Y (unitless) [3-1]
```{r}
plotCol(thisTS,ind = 57)
```

### ppm Zr (unitless) [3-1]
```{r}
plotCol(thisTS,ind = 58)
```

### ppm Zn (unitless) [3-1]
```{r}
plotCol(thisTS,ind = 59)
```

### % TC (unitless) [3-1]
```{r}
plotCol(thisTS,ind = 60)
```

### % IC (unitless) [3-1]
```{r}
plotCol(thisTS,ind = 61)
```

### CaCO3-IC (unitless) [3-1]
```{r}
plotCol(thisTS,ind = 62)
```

### % OC (unitless) [3-1]
```{r}
plotCol(thisTS,ind = 63)
```

### ppm Cd/% Mn (unitless) [3-1]
```{r}
plotCol(thisTS,ind = 64)
```

### ppmBa/%Al (unitless) [3-1]
```{r}
plotCol(thisTS,ind = 65)
```

### OC-MAR (g) (unitless) [3-1]
```{r}
plotCol(thisTS,ind = 66)
```

### OC-MAR (mg) (unitless) [3-1]
```{r}
plotCol(thisTS,ind = 67)
```

### Cd MAR (ug/cm2/ky) (unitless) [3-1]
```{r}
plotCol(thisTS,ind = 68)
```

### Mo MAR (ug/cm2/ky) (unitless) [3-1]
```{r}
plotCol(thisTS,ind = 69)
```

### Mn/Mo (unitless) [3-1]
```{r}
plotCol(thisTS,ind = 70)
```
