---
title: "ODP1019.Barron.2003"
output: 
  flexdashboard::flex_dashboard:
    theme: bootstrap
    source_code: embed
    orientation: rows
---

```{r setup, include = FALSE}
library(flexdashboard)
library(maptools)
library(tidyverse)
library(purrr)
library(leaflet)
library(plotly)
library(lipdR)
library(dygraphs)
library(geoChronR)

#read functions
source("../../functions.R")


load("../../temp.Rdata")

#remove columns we don't want to plot
varNames <- sapply(TS, "[[","paleoData_variableName")

# good <- which(!(varNames %in% c("year","depth","age")))
# TS <- TS[good]


#All datasets
dsn <- sapply(TS,"[[","dataSetName")
ui <- which(!duplicated(dsn))
udsn <- dsn[ui]
lat <- as.numeric(sapply(TS,"[[","geo_latitude")[ui])
lon <- as.numeric(sapply(TS,"[[","geo_longitude")[ui])
#elev <- sapply(TS,"[[","geo_elevation")[ui]
archiveType <- sapply(TS,"[[","archiveType")[ui]
link <- paste0(udsn,".html") %>% 
  str_replace_all("'","_")

#Organize metadata for map
map.meta <- data.frame(dataSetName = udsn, #datasetname
                       lat = lat,#lat
                       lon = lon,#lon
                      # elev = elev,#elevation
                       archiveType = factor(archiveType),#archiveType
                       link = link)#Link


#set index number

i = 92
thisTS <- TS[which(udsn[i] == dsn)]
```
#ODP1019.Barron.2003

Metadata {.sidebar}
-------------------------------------
[Download LiPD file](ODP1019.Barron.2003.lpd)
            

[Edit LiPD file](http://lipd.net/playground?source=http://lipdverse.org/wNAm0_1_0/ODP1019.Barron.2003.lpd)
            

[Download data only (csv)](ODP1019.Barron.2003.csv)
            

[Report an issue (include dataset name)](https://github.com/nickmckay/LiPDverse/issues)

<details open style="margin-left: 0px">
<summary>root</summary>
<p style="margin-left: 0px"><strong>archiveType: </strong>marine sediment
<p style="margin-left: 0px"><strong>originalDataURL: </strong>https://www.ncdc.noaa.gov/paleo-search/study/5867
<p style="margin-left: 0px"><strong>lipdVersion: </strong>1.3
</details>
<details>
<summary>pub</summary>
<details style="margin-left: 10px">
<summary>pub1</summary>
<p style="margin-left: 10px"><strong>journal: </strong>Paleoceanography
<p style="margin-left: 10px"><strong>volume: </strong>18
<p style="margin-left: 10px"><strong>pages: </strong>n/a-n/a
<p style="margin-left: 10px"><strong>pubYear: </strong>NA
<p style="margin-left: 10px"><strong>title: </strong>High-resolution climatic evolution of coastal northern California during the past 16,000 years
</details>
</details>
<details>
<summary>funding</summary>
<details style="margin-left: 10px">
<summary>funding1</summary>
<p style="margin-left: 10px"><strong>agency: </strong>Funding Agency
<p style="margin-left: 10px"><strong>grant: </strong>Grant name or number
</details>
</details>
<details open style="margin-left: 0px">
<summary>geo</summary>
<p style="margin-left: 0px"><strong>latitude: </strong>41.682
<p style="margin-left: 0px"><strong>longitude: </strong>-124.93
<p style="margin-left: 0px"><strong>elevation: </strong>-980
<p style="margin-left: 0px"><strong>siteName: </strong>ODP1019
</details>
<details open>
<summary>PaleoData columns</summary>
<details style="margin-left: 10px">
<summary>year (AD) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBa8219461
<p style="margin-left: 10px"><strong>variableName: </strong>year
<p style="margin-left: 10px"><strong>units: </strong>AD
<p style="margin-left: 10px"><strong>description: </strong>Year AD
</details>
<details style="margin-left: 10px">
<summary>age (yr BP) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBc0d223e7
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>yr BP
<p style="margin-left: 10px"><strong>description: </strong>Years before present (1950) yr BP
</details>
<details style="margin-left: 10px">
<summary>depth (cm) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB66529ad4
<p style="margin-left: 10px"><strong>variableName: </strong>depth
<p style="margin-left: 10px"><strong>units: </strong>cm
<p style="margin-left: 10px"><strong>description: </strong>depth
</details>
<details style="margin-left: 10px">
<summary>SST (degC) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD2d2ae711
<p style="margin-left: 10px"><strong>variableName: </strong>SST
<p style="margin-left: 10px"><strong>units: </strong>degC
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>TRUE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>direction: </strong>positive
<p style="margin-left: 20px"><strong>interpDirection: </strong>positive
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>seasonality: </strong>annual
<p style="margin-left: 20px"><strong>variable: </strong>T
<p style="margin-left: 20px"><strong>variableDetail: </strong>SST
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>CoreSect1H (unitless) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDc8474697
<p style="margin-left: 10px"><strong>variableName: </strong>CoreSect1H
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Top (unitless) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDe5b354a2
<p style="margin-left: 10px"><strong>variableName: </strong>Top
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Bot (unitless) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD732be32c
<p style="margin-left: 10px"><strong>variableName: </strong>Bot
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>sumUK37 (unitless) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDc096667d
<p style="margin-left: 10px"><strong>variableName: </strong>sumUK37
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>year (AD) [2-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBfbc1e156
<p style="margin-left: 10px"><strong>variableName: </strong>year
<p style="margin-left: 10px"><strong>units: </strong>AD
<p style="margin-left: 10px"><strong>description: </strong>Year AD
</details>
<details style="margin-left: 10px">
<summary>age (yr BP) [2-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB45c2b40f
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>yr BP
<p style="margin-left: 10px"><strong>description: </strong>Years before present (1950) yr BP
</details>
<details style="margin-left: 10px">
<summary>depth (cm) [2-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB32f921fc
<p style="margin-left: 10px"><strong>variableName: </strong>depth
<p style="margin-left: 10px"><strong>units: </strong>cm
<p style="margin-left: 10px"><strong>description: </strong>depth
</details>
<details style="margin-left: 10px">
<summary>CaCO3MAR (g/cm2/yr) [2-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDc8d8f169
<p style="margin-left: 10px"><strong>variableName: </strong>CaCO3MAR
<p style="margin-left: 10px"><strong>units: </strong>g/cm2/yr
<p style="margin-left: 10px"><strong>description: </strong>Lyle et al. [2000] present evidence that CaCO3 events are controlled by-production, not dissolution, and they postulate that higher CaCO3 values occur when coastal upwelling is weakened, causing increased blooms of coccolithophorids.
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>TRUE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>direction: </strong>negative
<p style="margin-left: 20px"><strong>interpDirection: </strong>negative
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>seasonality: </strong>annual
<p style="margin-left: 20px"><strong>variable: </strong>upwelling
<p style="margin-left: 20px"><strong>variableDetail: </strong>upwelling
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>core (unitless) [2-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDdbd85317
<p style="margin-left: 10px"><strong>variableName: </strong>core
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>section (unitless) [2-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD19d067a1
<p style="margin-left: 10px"><strong>variableName: </strong>section
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>top (unitless) [2-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDb60107b1
<p style="margin-left: 10px"><strong>variableName: </strong>top
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>bot (unitless) [2-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD19e6c846
<p style="margin-left: 10px"><strong>variableName: </strong>bot
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>sedRate (unitless) [2-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDec4fb49b
<p style="margin-left: 10px"><strong>variableName: </strong>sedRate
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Corg (unitless) [2-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD70f81095
<p style="margin-left: 10px"><strong>variableName: </strong>Corg
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>CaCO3 (unitless) [2-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDb7b957ca
<p style="margin-left: 10px"><strong>variableName: </strong>CaCO3
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>WetBD (unitless) [2-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDfa474b81
<p style="margin-left: 10px"><strong>variableName: </strong>WetBD
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>EstDryBD (unitless) [2-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDaae87ae5
<p style="margin-left: 10px"><strong>variableName: </strong>EstDryBD
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>bulkMAR (unitless) [2-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD0c17c7c5
<p style="margin-left: 10px"><strong>variableName: </strong>bulkMAR
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>CordMAR (unitless) [2-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD684c898d
<p style="margin-left: 10px"><strong>variableName: </strong>CordMAR
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>year (AD) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBb1b53383
<p style="margin-left: 10px"><strong>variableName: </strong>year
<p style="margin-left: 10px"><strong>units: </strong>AD
<p style="margin-left: 10px"><strong>description: </strong>Year AD
</details>
<details style="margin-left: 10px">
<summary>age (yr BP) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBdf68c9a8
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>yr BP
<p style="margin-left: 10px"><strong>description: </strong>Years before present (1950) yr BP
</details>
<details style="margin-left: 10px">
<summary>depth (cm) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB435012de
<p style="margin-left: 10px"><strong>variableName: </strong>depth
<p style="margin-left: 10px"><strong>units: </strong>cm
<p style="margin-left: 10px"><strong>description: </strong>depth
</details>
<details style="margin-left: 10px">
<summary>BSI (percent) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD067f4aa0
<p style="margin-left: 10px"><strong>variableName: </strong>BSI
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>year (AD) [4-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB0a8a163e
<p style="margin-left: 10px"><strong>variableName: </strong>year
<p style="margin-left: 10px"><strong>units: </strong>AD
<p style="margin-left: 10px"><strong>description: </strong>Year AD
</details>
<details style="margin-left: 10px">
<summary>age (yr BP) [4-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB205b7506
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>yr BP
<p style="margin-left: 10px"><strong>description: </strong>Years before present (1950) yr BP
</details>
<details style="margin-left: 10px">
<summary>depth (cm) [4-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB47ab9765
<p style="margin-left: 10px"><strong>variableName: </strong>depth
<p style="margin-left: 10px"><strong>units: </strong>cm
<p style="margin-left: 10px"><strong>description: </strong>depth
</details>
<details style="margin-left: 10px">
<summary>Thalassionema_nitzschioides (percent) [4-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD87397223
<p style="margin-left: 10px"><strong>variableName: </strong>Thalassionema_nitzschioides
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>TRUE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>direction: </strong>positive
<p style="margin-left: 20px"><strong>interpDirection: </strong>positive
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>seasonality: </strong>annual
<p style="margin-left: 20px"><strong>variable: </strong>upwelling
<p style="margin-left: 20px"><strong>variableDetail: </strong>upwelling
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>core_section (unitless) [4-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD79cfdfa2
<p style="margin-left: 10px"><strong>variableName: </strong>core_section
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>range (unitless) [4-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD0f17c78b
<p style="margin-left: 10px"><strong>variableName: </strong>range
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Actinocyclus_curvatulus (percent) [4-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD370773ec
<p style="margin-left: 10px"><strong>variableName: </strong>Actinocyclus_curvatulus
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Azpeitia_nodulifer (percent) [4-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDa501a787
<p style="margin-left: 10px"><strong>variableName: </strong>Azpeitia_nodulifer
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>A_tabularis (percent) [4-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDcc181dde
<p style="margin-left: 10px"><strong>variableName: </strong>A_tabularis
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Coscinodiscus_radiatus (percent) [4-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD9a6c42df
<p style="margin-left: 10px"><strong>variableName: </strong>Coscinodiscus_radiatus
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Delphineis (percent) [4-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDa0de1ee4
<p style="margin-left: 10px"><strong>variableName: </strong>Delphineis
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Hemidiscus_cuneiformis (percent) [4-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD61f28797
<p style="margin-left: 10px"><strong>variableName: </strong>Hemidiscus_cuneiformis
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Neodenticula_seminae (percent) [4-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD28879136
<p style="margin-left: 10px"><strong>variableName: </strong>Neodenticula_seminae
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Nitzschia_interruptestriata (percent) [4-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD32b471f6
<p style="margin-left: 10px"><strong>variableName: </strong>Nitzschia_interruptestriata
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>N_sicula (percent) [4-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD9f7051c6
<p style="margin-left: 10px"><strong>variableName: </strong>N_sicula
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Pseudoeunotia_doliolus (percent) [4-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD2ba48b7e
<p style="margin-left: 10px"><strong>variableName: </strong>Pseudoeunotia_doliolus
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Rhizosolenia (percent) [4-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD6b107d7f
<p style="margin-left: 10px"><strong>variableName: </strong>Rhizosolenia
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Roperia_tesselata (percent) [4-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD55b2f42b
<p style="margin-left: 10px"><strong>variableName: </strong>Roperia_tesselata
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Stephanopyxis (percent) [4-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD2cb1fa44
<p style="margin-left: 10px"><strong>variableName: </strong>Stephanopyxis
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Thalassiosira_excentrica (percent) [4-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD4c5795fb
<p style="margin-left: 10px"><strong>variableName: </strong>Thalassiosira_excentrica
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>T_oestrupii (percent) [4-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD96331c23
<p style="margin-left: 10px"><strong>variableName: </strong>T_oestrupii
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>T_pacifica (percent) [4-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD1c33bb36
<p style="margin-left: 10px"><strong>variableName: </strong>T_pacifica
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>T_spp (percent) [4-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD78feb153
<p style="margin-left: 10px"><strong>variableName: </strong>T_spp
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Thalassiothrix_longissima (percent) [4-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD14f73bf8
<p style="margin-left: 10px"><strong>variableName: </strong>Thalassiothrix_longissima
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Other_planktic (percent) [4-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDfe85945c
<p style="margin-left: 10px"><strong>variableName: </strong>Other_planktic
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Actinoptychus (percent) [4-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD43d0c767
<p style="margin-left: 10px"><strong>variableName: </strong>Actinoptychus
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Paralia_sucata (percent) [4-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD5855d89a
<p style="margin-left: 10px"><strong>variableName: </strong>Paralia_sucata
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Minidiscus? (percent) [4-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD37969087
<p style="margin-left: 10px"><strong>variableName: </strong>Minidiscus?
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Benthic (percent) [4-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDee740581
<p style="margin-left: 10px"><strong>variableName: </strong>Benthic
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Freshwater_planktic (percent) [4-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD39ed5039
<p style="margin-left: 10px"><strong>variableName: </strong>Freshwater_planktic
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Reworked (percent) [4-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD7469db23
<p style="margin-left: 10px"><strong>variableName: </strong>Reworked
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>total_non_Chaetoceros_counted (unitless) [4-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD34eb8707
<p style="margin-left: 10px"><strong>variableName: </strong>total_non_Chaetoceros_counted
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Chaetoceros_spores (unitless) [4-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD462b5aa8
<p style="margin-left: 10px"><strong>variableName: </strong>Chaetoceros_spores
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Diatoms_per_traverse (unitless) [4-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD7cef00f6
<p style="margin-left: 10px"><strong>variableName: </strong>Diatoms_per_traverse
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>year (AD) [5-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB06d41fcd
<p style="margin-left: 10px"><strong>variableName: </strong>year
<p style="margin-left: 10px"><strong>units: </strong>AD
<p style="margin-left: 10px"><strong>description: </strong>Year AD
</details>
<details style="margin-left: 10px">
<summary>age (yr BP) [5-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBfc5c318c
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>yr BP
<p style="margin-left: 10px"><strong>description: </strong>Years before present (1950) yr BP
</details>
<details style="margin-left: 10px">
<summary>depth (cm) [5-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBb05b8107
<p style="margin-left: 10px"><strong>variableName: </strong>depth
<p style="margin-left: 10px"><strong>units: </strong>cm
<p style="margin-left: 10px"><strong>description: </strong>depth
</details>
<details style="margin-left: 10px">
<summary>Sequoia (percent) [5-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDe7442731
<p style="margin-left: 10px"><strong>variableName: </strong>Sequoia
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>description: </strong>Interpreted in original paper as a indicator of moisture, but subsequently as related to coastal fog and upwelling
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>TRUE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>direction: </strong>positive
<p style="margin-left: 20px"><strong>interpDirection: </strong>positive
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>seasonality: </strong>annual
<p style="margin-left: 20px"><strong>variable: </strong>M
<p style="margin-left: 20px"><strong>variableDetail: </strong>upwelling
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>core_section (unitless) [5-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD77776d72
<p style="margin-left: 10px"><strong>variableName: </strong>core_section
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>interval (cm) [5-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDb1416af4
<p style="margin-left: 10px"><strong>variableName: </strong>interval
<p style="margin-left: 10px"><strong>units: </strong>cm
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Abies (percent) [5-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD01dc5bd1
<p style="margin-left: 10px"><strong>variableName: </strong>Abies
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Alnus (percent) [5-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDac11991f
<p style="margin-left: 10px"><strong>variableName: </strong>Alnus
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Artemisia (percent) [5-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD109d7dc3
<p style="margin-left: 10px"><strong>variableName: </strong>Artemisia
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Chenopodiacaeae (percent) [5-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD17ea0f7c
<p style="margin-left: 10px"><strong>variableName: </strong>Chenopodiacaeae
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Compositae (percent) [5-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD510d1821
<p style="margin-left: 10px"><strong>variableName: </strong>Compositae
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Cyperaceae (percent) [5-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD1494335e
<p style="margin-left: 10px"><strong>variableName: </strong>Cyperaceae
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Gramineae (percent) [5-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD604d883e
<p style="margin-left: 10px"><strong>variableName: </strong>Gramineae
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Picea (percent) [5-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD24076f43
<p style="margin-left: 10px"><strong>variableName: </strong>Picea
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Pinus (percent) [5-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD12ecdd3a
<p style="margin-left: 10px"><strong>variableName: </strong>Pinus
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Pseudtsuga (percent) [5-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD5cdc92e7
<p style="margin-left: 10px"><strong>variableName: </strong>Pseudtsuga
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Quercus (percent) [5-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD217226f5
<p style="margin-left: 10px"><strong>variableName: </strong>Quercus
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>RRA (unitless) [5-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD5398e791
<p style="margin-left: 10px"><strong>variableName: </strong>RRA
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Tsuga_heterophylla (unitless) [5-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD02286c93
<p style="margin-left: 10px"><strong>variableName: </strong>Tsuga_heterophylla
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>T_mertensianna (unitless) [5-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDee96f9d3
<p style="margin-left: 10px"><strong>variableName: </strong>T_mertensianna
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>TCT (unitless) [5-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDe2245135
<p style="margin-left: 10px"><strong>variableName: </strong>TCT
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Total_grains_counted (unitless) [5-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDce562d30
<p style="margin-left: 10px"><strong>variableName: </strong>Total_grains_counted
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>pollen_grains/gram (unitless) [5-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDffc3249f
<p style="margin-left: 10px"><strong>variableName: </strong>pollen_grains/gram
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>

Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### Sitemap

```{r}
  map.meta.split <- split(map.meta, map.meta$archiveType)


factpal <- colorFactor("Paired",map.meta$archiveType)
buff <- 15
l <- leaflet() %>% 
  addTiles() %>% 
  fitBounds(map.meta$lon[i]-buff,map.meta$lat[i]-buff,map.meta$lon[i]+buff,map.meta$lat[i]+buff)
  

  
  
names(map.meta.split) %>%
  purrr::walk( function(df) {
    l <<- l %>%
      addMarkers(data=map.meta.split[[df]],
                 lng=~lon, lat=~lat,
                 label=~as.character(archiveType),
                 popup=~paste(str_c('Dataset: <a href="',link,'">',dataSetName,'</a>'),
                                 # str_c("Elevation: ",elev),
                                  str_c("Archive Type: ",archiveType),
                                  sep = "<br>"),
                 group = df,
                 clusterOptions = markerClusterOptions(removeOutsideVisibleBounds = F),
                 labelOptions = labelOptions(noHide = F,
                                             direction = 'auto'))
  })

l %>%
  addLayersControl(position = "bottomleft",
    overlayGroups = names(map.meta.split),
    options = layersControlOptions(collapsed = FALSE,
                                   opacity = 0.8)
  )
```

### Search the LiPDverse (Beta! doesn't work well yet)
```{r}
#Add google search bar
htmltools::includeHTML("../../googleSearchChunk.html")
```


Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### SST (degC) [1-1]
```{r}
plotCol(thisTS,ind = 7)
```

### CoreSect1H (unitless) [1-1]
```{r}
plotCol(thisTS,ind = 1)
```

### Top (unitless) [1-1]
```{r}
plotCol(thisTS,ind = 5)
```

### Bot (unitless) [1-1]
```{r}
plotCol(thisTS,ind = 6)
```

### sumUK37 (unitless) [1-1]
```{r}
plotCol(thisTS,ind = 8)
```

### CaCO3MAR (g/cm2/yr) [2-1]
```{r}
plotCol(thisTS,ind = 23)
```

### core (unitless) [2-1]
```{r}
plotCol(thisTS,ind = 9)
```

### section (unitless) [2-1]
```{r}
plotCol(thisTS,ind = 13)
```

### top (unitless) [2-1]
```{r}
plotCol(thisTS,ind = 14)
```

### bot (unitless) [2-1]
```{r}
plotCol(thisTS,ind = 15)
```

### sedRate (unitless) [2-1]
```{r}
plotCol(thisTS,ind = 16)
```

### Corg (unitless) [2-1]
```{r}
plotCol(thisTS,ind = 17)
```

### CaCO3 (unitless) [2-1]
```{r}
plotCol(thisTS,ind = 18)
```

### WetBD (unitless) [2-1]
```{r}
plotCol(thisTS,ind = 19)
```

### EstDryBD (unitless) [2-1]
```{r}
plotCol(thisTS,ind = 20)
```

### bulkMAR (unitless) [2-1]
```{r}
plotCol(thisTS,ind = 21)
```

### CordMAR (unitless) [2-1]
```{r}
plotCol(thisTS,ind = 22)
```

### BSI (percent) [3-1]
```{r}
plotCol(thisTS,ind = 24)
```

### Thalassionema_nitzschioides (percent) [4-1]
```{r}
plotCol(thisTS,ind = 46)
```

### core_section (unitless) [4-1]
```{r}
plotCol(thisTS,ind = 28)
```

### range (unitless) [4-1]
```{r}
plotCol(thisTS,ind = 32)
```

### Actinocyclus_curvatulus (percent) [4-1]
```{r}
plotCol(thisTS,ind = 33)
```

### Azpeitia_nodulifer (percent) [4-1]
```{r}
plotCol(thisTS,ind = 34)
```

### A_tabularis (percent) [4-1]
```{r}
plotCol(thisTS,ind = 35)
```

### Coscinodiscus_radiatus (percent) [4-1]
```{r}
plotCol(thisTS,ind = 36)
```

### Delphineis (percent) [4-1]
```{r}
plotCol(thisTS,ind = 37)
```

### Hemidiscus_cuneiformis (percent) [4-1]
```{r}
plotCol(thisTS,ind = 38)
```

### Neodenticula_seminae (percent) [4-1]
```{r}
plotCol(thisTS,ind = 39)
```

### Nitzschia_interruptestriata (percent) [4-1]
```{r}
plotCol(thisTS,ind = 40)
```

### N_sicula (percent) [4-1]
```{r}
plotCol(thisTS,ind = 41)
```

### Pseudoeunotia_doliolus (percent) [4-1]
```{r}
plotCol(thisTS,ind = 42)
```

### Rhizosolenia (percent) [4-1]
```{r}
plotCol(thisTS,ind = 43)
```

### Roperia_tesselata (percent) [4-1]
```{r}
plotCol(thisTS,ind = 44)
```

### Stephanopyxis (percent) [4-1]
```{r}
plotCol(thisTS,ind = 45)
```

### Thalassiosira_excentrica (percent) [4-1]
```{r}
plotCol(thisTS,ind = 47)
```

### T_oestrupii (percent) [4-1]
```{r}
plotCol(thisTS,ind = 48)
```

### T_pacifica (percent) [4-1]
```{r}
plotCol(thisTS,ind = 49)
```

### T_spp (percent) [4-1]
```{r}
plotCol(thisTS,ind = 50)
```

### Thalassiothrix_longissima (percent) [4-1]
```{r}
plotCol(thisTS,ind = 51)
```

### Other_planktic (percent) [4-1]
```{r}
plotCol(thisTS,ind = 52)
```

### Actinoptychus (percent) [4-1]
```{r}
plotCol(thisTS,ind = 53)
```

### Paralia_sucata (percent) [4-1]
```{r}
plotCol(thisTS,ind = 54)
```

### Minidiscus? (percent) [4-1]
```{r}
plotCol(thisTS,ind = 55)
```

### Benthic (percent) [4-1]
```{r}
plotCol(thisTS,ind = 56)
```

### Freshwater_planktic (percent) [4-1]
```{r}
plotCol(thisTS,ind = 57)
```

### Reworked (percent) [4-1]
```{r}
plotCol(thisTS,ind = 58)
```

### total_non_Chaetoceros_counted (unitless) [4-1]
```{r}
plotCol(thisTS,ind = 59)
```

### Chaetoceros_spores (unitless) [4-1]
```{r}
plotCol(thisTS,ind = 60)
```

### Diatoms_per_traverse (unitless) [4-1]
```{r}
plotCol(thisTS,ind = 61)
```

### Sequoia (percent) [5-1]
```{r}
plotCol(thisTS,ind = 78)
```

### core_section (unitless) [5-1]
```{r}
plotCol(thisTS,ind = 62)
```

### interval (cm) [5-1]
```{r}
plotCol(thisTS,ind = 66)
```

### Abies (percent) [5-1]
```{r}
plotCol(thisTS,ind = 67)
```

### Alnus (percent) [5-1]
```{r}
plotCol(thisTS,ind = 68)
```

### Artemisia (percent) [5-1]
```{r}
plotCol(thisTS,ind = 69)
```

### Chenopodiacaeae (percent) [5-1]
```{r}
plotCol(thisTS,ind = 70)
```

### Compositae (percent) [5-1]
```{r}
plotCol(thisTS,ind = 71)
```

### Cyperaceae (percent) [5-1]
```{r}
plotCol(thisTS,ind = 72)
```

### Gramineae (percent) [5-1]
```{r}
plotCol(thisTS,ind = 73)
```

### Picea (percent) [5-1]
```{r}
plotCol(thisTS,ind = 74)
```

### Pinus (percent) [5-1]
```{r}
plotCol(thisTS,ind = 75)
```

### Pseudtsuga (percent) [5-1]
```{r}
plotCol(thisTS,ind = 76)
```

### Quercus (percent) [5-1]
```{r}
plotCol(thisTS,ind = 77)
```

### RRA (unitless) [5-1]
```{r}
plotCol(thisTS,ind = 79)
```

### Tsuga_heterophylla (unitless) [5-1]
```{r}
plotCol(thisTS,ind = 80)
```

### T_mertensianna (unitless) [5-1]
```{r}
plotCol(thisTS,ind = 81)
```

### TCT (unitless) [5-1]
```{r}
plotCol(thisTS,ind = 82)
```

### Total_grains_counted (unitless) [5-1]
```{r}
plotCol(thisTS,ind = 83)
```

### pollen_grains/gram (unitless) [5-1]
```{r}
plotCol(thisTS,ind = 84)
```
