---
title: "station803.Bringue.2012"
output: 
  flexdashboard::flex_dashboard:
    theme: bootstrap
    source_code: embed
    orientation: rows
---

```{r setup, include = FALSE}
library(flexdashboard)
library(maptools)
library(tidyverse)
library(purrr)
library(leaflet)
library(plotly)
library(lipdR)
library(dygraphs)
library(geoChronR)

#read functions
source("../../functions.R")


load("../../temp.Rdata")

#remove columns we don't want to plot
varNames <- sapply(TS, "[[","paleoData_variableName")

# good <- which(!(varNames %in% c("year","depth","age")))
# TS <- TS[good]


#All datasets
dsn <- sapply(TS,"[[","dataSetName")
ui <- which(!duplicated(dsn))
udsn <- dsn[ui]
lat <- as.numeric(sapply(TS,"[[","geo_latitude")[ui])
lon <- as.numeric(sapply(TS,"[[","geo_longitude")[ui])
#elev <- sapply(TS,"[[","geo_elevation")[ui]
archiveType <- sapply(TS,"[[","archiveType")[ui]
link <- paste0(udsn,".html") %>% 
  str_replace_all("'","_")

#Organize metadata for map
map.meta <- data.frame(dataSetName = udsn, #datasetname
                       lat = lat,#lat
                       lon = lon,#lon
                      # elev = elev,#elevation
                       archiveType = factor(archiveType),#archiveType
                       link = link)#Link


#set index number

i = 118
thisTS <- TS[which(udsn[i] == dsn)]
```
#station803.Bringue.2012

Metadata {.sidebar}
-------------------------------------
[Download LiPD file](station803.Bringue.2012.lpd)
            

[Edit LiPD file](http://lipd.net/playground?source=http://lipdverse.org/wNAm0_1_0/station803.Bringue.2012.lpd)
            

[Download data only (csv)](station803.Bringue.2012.csv)
            

[Report an issue (include dataset name)](https://github.com/nickmckay/LiPDverse/issues)

<details open style="margin-left: 0px">
<summary>root</summary>
<p style="margin-left: 0px"><strong>archiveType: </strong>marine sediment
<p style="margin-left: 0px"><strong>lipdVersion: </strong>1.3
</details>
<details>
<summary>pub</summary>
<details style="margin-left: 10px">
<summary>pub1</summary>
<p style="margin-left: 10px"><strong>journal: </strong>Marine Geology
<p style="margin-left: 10px"><strong>volume: </strong>291-294
<p style="margin-left: 10px"><strong>pages: </strong>83-96
<p style="margin-left: 10px"><strong>pubYear: </strong>NA
<p style="margin-left: 10px"><strong>title: </strong>Late Holocene paleoceanography and climate variability over the Mackenzie Slope (Beaufort Sea, Canadian Arctic)
</details>
</details>
<details open style="margin-left: 0px">
<summary>geo</summary>
<p style="margin-left: 0px"><strong>latitude: </strong>70.6328
<p style="margin-left: 0px"><strong>longitude: </strong>-135.8803
<p style="margin-left: 0px"><strong>elevation: </strong>-218
<p style="margin-left: 0px"><strong>siteName: </strong>Station 803
</details>
<details open>
<summary>PaleoData columns</summary>
<details style="margin-left: 10px">
<summary>depth (cm) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB5fb8e5a4
<p style="margin-left: 10px"><strong>variableName: </strong>depth
<p style="margin-left: 10px"><strong>units: </strong>cm
</details>
<details style="margin-left: 10px">
<summary>age (yr BP) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB0856a3ae
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>yr BP
</details>
<details style="margin-left: 10px">
<summary>TAUG (degC) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB1da17ab5
<p style="margin-left: 10px"><strong>variableName: </strong>TAUG
<p style="margin-left: 10px"><strong>units: </strong>degC
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>TRUE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>direction: </strong>positive
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>seasonality: </strong>august
<p style="margin-left: 20px"><strong>variable: </strong>T
<p style="margin-left: 20px"><strong>variableDetail: </strong>SST
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>IMON1953 (months/yr) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBd68d542b
<p style="margin-left: 10px"><strong>variableName: </strong>IMON1953
<p style="margin-left: 10px"><strong>units: </strong>months/yr
<p style="margin-left: 10px"><strong>description: </strong>sea ice cover in months/year
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>TRUE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>direction: </strong>positive
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>seasonality: </strong>annual
<p style="margin-left: 20px"><strong>variable: </strong>ICE
<p style="margin-left: 20px"><strong>variableDetail: </strong>sea ice
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>depth-range (cm) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB53e68761
<p style="margin-left: 10px"><strong>variableName: </strong>depth-range
<p style="margin-left: 10px"><strong>units: </strong>cm
</details>
<details style="margin-left: 10px">
<summary>TFEV_i (unitless) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBe86c3850
<p style="margin-left: 10px"><strong>variableName: </strong>TFEV_i
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>TFEV (unitless) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB219bb723
<p style="margin-left: 10px"><strong>variableName: </strong>TFEV
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>TFEV_s (unitless) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB9b9fe4ce
<p style="margin-left: 10px"><strong>variableName: </strong>TFEV_s
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>TFEV/3 (unitless) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB55a8955e
<p style="margin-left: 10px"><strong>variableName: </strong>TFEV/3
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>SFEV_i (unitless) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB630281bf
<p style="margin-left: 10px"><strong>variableName: </strong>SFEV_i
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>SFEV (unitless) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBf35ccd49
<p style="margin-left: 10px"><strong>variableName: </strong>SFEV
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>SFEV_s (unitless) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB530c34d4
<p style="margin-left: 10px"><strong>variableName: </strong>SFEV_s
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>SFEV/3 (unitless) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBdfe80620
<p style="margin-left: 10px"><strong>variableName: </strong>SFEV/3
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>THIV_i (unitless) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBbffe27a8
<p style="margin-left: 10px"><strong>variableName: </strong>THIV_i
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>THIV (unitless) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBb2b90adc
<p style="margin-left: 10px"><strong>variableName: </strong>THIV
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>THIV_s (unitless) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB979f32af
<p style="margin-left: 10px"><strong>variableName: </strong>THIV_s
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>THIV/3 (unitless) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB79168f92
<p style="margin-left: 10px"><strong>variableName: </strong>THIV/3
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>SHIV_i (unitless) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB7981e0bb
<p style="margin-left: 10px"><strong>variableName: </strong>SHIV_i
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>SHIV (unitless) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB668c53ad
<p style="margin-left: 10px"><strong>variableName: </strong>SHIV
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>SHIV_s (unitless) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB8b54567d
<p style="margin-left: 10px"><strong>variableName: </strong>SHIV_s
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>SHIV/3 (unitless) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBf735a0d6
<p style="margin-left: 10px"><strong>variableName: </strong>SHIV/3
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>TAUG_i (unitless) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBf7e97d2c
<p style="margin-left: 10px"><strong>variableName: </strong>TAUG_i
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>TAUG_s (unitless) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBe5d5c17a
<p style="margin-left: 10px"><strong>variableName: </strong>TAUG_s
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>TAUG/3 (unitless) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB0911d108
<p style="margin-left: 10px"><strong>variableName: </strong>TAUG/3
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>SAUG_i (unitless) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBef149c50
<p style="margin-left: 10px"><strong>variableName: </strong>SAUG_i
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>SAUG (unitless) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB18d3e2dc
<p style="margin-left: 10px"><strong>variableName: </strong>SAUG
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>SAUG_s (unitless) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBc6ba74c8
<p style="margin-left: 10px"><strong>variableName: </strong>SAUG_s
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>SAUG/3 (unitless) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB6259e3cf
<p style="margin-left: 10px"><strong>variableName: </strong>SAUG/3
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>TETE_i (unitless) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBfd4ee3a0
<p style="margin-left: 10px"><strong>variableName: </strong>TETE_i
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>TETE (unitless) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB6179b3f9
<p style="margin-left: 10px"><strong>variableName: </strong>TETE
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>TETE_s (unitless) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB6e01a776
<p style="margin-left: 10px"><strong>variableName: </strong>TETE_s
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>TETE/3 (unitless) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB29bdb01b
<p style="margin-left: 10px"><strong>variableName: </strong>TETE/3
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>SETE_i (unitless) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB6d36256c
<p style="margin-left: 10px"><strong>variableName: </strong>SETE_i
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>SETE (unitless) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB946f8057
<p style="margin-left: 10px"><strong>variableName: </strong>SETE
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>SETE_s (unitless) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB733a1585
<p style="margin-left: 10px"><strong>variableName: </strong>SETE_s
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>SETE/3 (unitless) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB6e0c6b5d
<p style="margin-left: 10px"><strong>variableName: </strong>SETE/3
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>IMON1953_i (unitless) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBa187f463
<p style="margin-left: 10px"><strong>variableName: </strong>IMON1953_i
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>IMON1953_s (unitless) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBe0dc24f9
<p style="margin-left: 10px"><strong>variableName: </strong>IMON1953_s
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>IMON1953/3 (unitless) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBb59bbe54
<p style="margin-left: 10px"><strong>variableName: </strong>IMON1953/3
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>depth (cm) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB7717a7f7
<p style="margin-left: 10px"><strong>variableName: </strong>depth
<p style="margin-left: 10px"><strong>units: </strong>cm
</details>
<details style="margin-left: 10px">
<summary>year (year ce) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB96cd89ae
<p style="margin-left: 10px"><strong>variableName: </strong>year
<p style="margin-left: 10px"><strong>units: </strong>year ce
</details>
<details style="margin-left: 10px">
<summary>age (yr BP) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBeef661d0
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>yr BP
</details>
<details style="margin-left: 10px">
<summary>TAUG (degC) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBb68390ad
<p style="margin-left: 10px"><strong>variableName: </strong>TAUG
<p style="margin-left: 10px"><strong>units: </strong>degC
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>seasonality: </strong>august
<p style="margin-left: 20px"><strong>variable: </strong>T
<p style="margin-left: 20px"><strong>variableDetail: </strong>SST
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>depth-range (cm) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBa5ca5bf6
<p style="margin-left: 10px"><strong>variableName: </strong>depth-range
<p style="margin-left: 10px"><strong>units: </strong>cm
</details>
<details style="margin-left: 10px">
<summary>TFEV_i (unitless) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB11eee4ca
<p style="margin-left: 10px"><strong>variableName: </strong>TFEV_i
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>TFEV (unitless) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBb19d797a
<p style="margin-left: 10px"><strong>variableName: </strong>TFEV
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>TFEV_s (unitless) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBc032af98
<p style="margin-left: 10px"><strong>variableName: </strong>TFEV_s
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>TFEV/3 (unitless) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB53f348f1
<p style="margin-left: 10px"><strong>variableName: </strong>TFEV/3
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>SFEV_i (unitless) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBedc87e21
<p style="margin-left: 10px"><strong>variableName: </strong>SFEV_i
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>SFEV (unitless) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBb0f9a263
<p style="margin-left: 10px"><strong>variableName: </strong>SFEV
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>SFEV_s (unitless) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB93255a9c
<p style="margin-left: 10px"><strong>variableName: </strong>SFEV_s
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>SFEV/3 (unitless) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBe95c56a7
<p style="margin-left: 10px"><strong>variableName: </strong>SFEV/3
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>THIV_i (unitless) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB5489a6ec
<p style="margin-left: 10px"><strong>variableName: </strong>THIV_i
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>THIV (unitless) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB5972b76c
<p style="margin-left: 10px"><strong>variableName: </strong>THIV
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>THIV_s (unitless) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBf34cf890
<p style="margin-left: 10px"><strong>variableName: </strong>THIV_s
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>THIV/3 (unitless) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB118d2170
<p style="margin-left: 10px"><strong>variableName: </strong>THIV/3
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>SHIV_i (unitless) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB06675ffd
<p style="margin-left: 10px"><strong>variableName: </strong>SHIV_i
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>SHIV (unitless) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBb45782c6
<p style="margin-left: 10px"><strong>variableName: </strong>SHIV
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>SHIV_s (unitless) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBa216e079
<p style="margin-left: 10px"><strong>variableName: </strong>SHIV_s
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>SHIV/3 (unitless) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBcf3dfd5f
<p style="margin-left: 10px"><strong>variableName: </strong>SHIV/3
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>TAUG_i (unitless) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB2350250e
<p style="margin-left: 10px"><strong>variableName: </strong>TAUG_i
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>TAUG_s (unitless) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBa88ad0e3
<p style="margin-left: 10px"><strong>variableName: </strong>TAUG_s
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>TAUG/3 (degC) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB1baf7f84
<p style="margin-left: 10px"><strong>variableName: </strong>TAUG/3
<p style="margin-left: 10px"><strong>units: </strong>degC
</details>
<details style="margin-left: 10px">
<summary>SAUG_i (unitless) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBe639c566
<p style="margin-left: 10px"><strong>variableName: </strong>SAUG_i
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>SAUG (unitless) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBfcbba369
<p style="margin-left: 10px"><strong>variableName: </strong>SAUG
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>SAUG_s (unitless) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBf013315a
<p style="margin-left: 10px"><strong>variableName: </strong>SAUG_s
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>SAUG/3 (unitless) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB67f1ec10
<p style="margin-left: 10px"><strong>variableName: </strong>SAUG/3
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>TETE_i (unitless) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB9bf1ebb7
<p style="margin-left: 10px"><strong>variableName: </strong>TETE_i
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>TETE (unitless) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBfc497fa0
<p style="margin-left: 10px"><strong>variableName: </strong>TETE
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>TETE_s (unitless) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBf924906e
<p style="margin-left: 10px"><strong>variableName: </strong>TETE_s
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>TETE/3 (unitless) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB3351f7c4
<p style="margin-left: 10px"><strong>variableName: </strong>TETE/3
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>SETE_i (unitless) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB81987935
<p style="margin-left: 10px"><strong>variableName: </strong>SETE_i
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>SETE (unitless) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBfd4751af
<p style="margin-left: 10px"><strong>variableName: </strong>SETE
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>SETE_s (unitless) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBc87e721e
<p style="margin-left: 10px"><strong>variableName: </strong>SETE_s
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>SETE/3 (unitless) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBe2fd65d8
<p style="margin-left: 10px"><strong>variableName: </strong>SETE/3
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>IMON1953_i (unitless) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB03f35735
<p style="margin-left: 10px"><strong>variableName: </strong>IMON1953_i
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>IMON1953 (unitless) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB397a390f
<p style="margin-left: 10px"><strong>variableName: </strong>IMON1953
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>IMON1953_s (unitless) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB1fa55bc1
<p style="margin-left: 10px"><strong>variableName: </strong>IMON1953_s
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>IMON1953/3 (unitless) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBa7652ecd
<p style="margin-left: 10px"><strong>variableName: </strong>IMON1953/3
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>depth (cm) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB1064eba4
<p style="margin-left: 10px"><strong>variableName: </strong>depth
<p style="margin-left: 10px"><strong>units: </strong>cm
</details>
<details style="margin-left: 10px">
<summary>year (year ce) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB147188d8
<p style="margin-left: 10px"><strong>variableName: </strong>year
<p style="margin-left: 10px"><strong>units: </strong>year ce
</details>
<details style="margin-left: 10px">
<summary>age (yr BP) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB17f15760
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>yr BP
</details>
<details style="margin-left: 10px">
<summary>TAUG (degC) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB460ab94e
<p style="margin-left: 10px"><strong>variableName: </strong>TAUG
<p style="margin-left: 10px"><strong>units: </strong>degC
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>seasonality: </strong>august
<p style="margin-left: 20px"><strong>variable: </strong>T
<p style="margin-left: 20px"><strong>variableDetail: </strong>SST
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>depth-range (cm) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB6cb0885b
<p style="margin-left: 10px"><strong>variableName: </strong>depth-range
<p style="margin-left: 10px"><strong>units: </strong>cm
</details>
<details style="margin-left: 10px">
<summary>TFEV_i (unitless) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB8a9c366c
<p style="margin-left: 10px"><strong>variableName: </strong>TFEV_i
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>TFEV (unitless) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBe8525a2b
<p style="margin-left: 10px"><strong>variableName: </strong>TFEV
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>TFEV_s (unitless) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBc9b2e67d
<p style="margin-left: 10px"><strong>variableName: </strong>TFEV_s
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>TFEV/3 (unitless) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBe5d7fe4b
<p style="margin-left: 10px"><strong>variableName: </strong>TFEV/3
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>SFEV_i (unitless) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBd60b353b
<p style="margin-left: 10px"><strong>variableName: </strong>SFEV_i
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>SFEV (unitless) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB40593100
<p style="margin-left: 10px"><strong>variableName: </strong>SFEV
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>SFEV_s (unitless) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB0cb86668
<p style="margin-left: 10px"><strong>variableName: </strong>SFEV_s
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>SFEV/3 (unitless) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBe7c3d5a0
<p style="margin-left: 10px"><strong>variableName: </strong>SFEV/3
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>THIV_i (unitless) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBd15eeee2
<p style="margin-left: 10px"><strong>variableName: </strong>THIV_i
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>THIV (unitless) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB677f5039
<p style="margin-left: 10px"><strong>variableName: </strong>THIV
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>THIV_s (unitless) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB605a3f9e
<p style="margin-left: 10px"><strong>variableName: </strong>THIV_s
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>THIV/3 (unitless) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBeb176066
<p style="margin-left: 10px"><strong>variableName: </strong>THIV/3
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>SHIV_i (unitless) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB93876c18
<p style="margin-left: 10px"><strong>variableName: </strong>SHIV_i
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>SHIV (unitless) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB07ec7d58
<p style="margin-left: 10px"><strong>variableName: </strong>SHIV
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>SHIV_s (unitless) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBdc9424f3
<p style="margin-left: 10px"><strong>variableName: </strong>SHIV_s
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>SHIV/3 (unitless) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBf956da65
<p style="margin-left: 10px"><strong>variableName: </strong>SHIV/3
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>TAUG_i (unitless) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBa2d03151
<p style="margin-left: 10px"><strong>variableName: </strong>TAUG_i
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>TAUG_s (unitless) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB069fbb10
<p style="margin-left: 10px"><strong>variableName: </strong>TAUG_s
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>TAUG/3 (unitless) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB2ba2caf1
<p style="margin-left: 10px"><strong>variableName: </strong>TAUG/3
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>SAUG_i (unitless) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBbedc283c
<p style="margin-left: 10px"><strong>variableName: </strong>SAUG_i
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>SAUG (unitless) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB7a58a27d
<p style="margin-left: 10px"><strong>variableName: </strong>SAUG
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>SAUG_s (unitless) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB6b06825b
<p style="margin-left: 10px"><strong>variableName: </strong>SAUG_s
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>SAUG/3 (unitless) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB3912b99a
<p style="margin-left: 10px"><strong>variableName: </strong>SAUG/3
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>TETE_i (unitless) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB2e5e2e3b
<p style="margin-left: 10px"><strong>variableName: </strong>TETE_i
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>TETE (unitless) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB72c68913
<p style="margin-left: 10px"><strong>variableName: </strong>TETE
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>TETE_s (unitless) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBb24c1947
<p style="margin-left: 10px"><strong>variableName: </strong>TETE_s
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>TETE/3 (unitless) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB0e8c4176
<p style="margin-left: 10px"><strong>variableName: </strong>TETE/3
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>SETE_i (unitless) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB2e782f9f
<p style="margin-left: 10px"><strong>variableName: </strong>SETE_i
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>SETE (unitless) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBe192e50f
<p style="margin-left: 10px"><strong>variableName: </strong>SETE
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>SETE_s (unitless) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBbc0c6c65
<p style="margin-left: 10px"><strong>variableName: </strong>SETE_s
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>SETE/3 (unitless) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBb06c31dd
<p style="margin-left: 10px"><strong>variableName: </strong>SETE/3
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>IMON1953_i (unitless) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB8d658c89
<p style="margin-left: 10px"><strong>variableName: </strong>IMON1953_i
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>IMON1953 (unitless) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB4cfaa231
<p style="margin-left: 10px"><strong>variableName: </strong>IMON1953
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>IMON1953_s (unitless) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBe2ea913c
<p style="margin-left: 10px"><strong>variableName: </strong>IMON1953_s
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>IMON1953/3 (unitless) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBd8acfbdb
<p style="margin-left: 10px"><strong>variableName: </strong>IMON1953/3
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>

Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### Sitemap

```{r}
  map.meta.split <- split(map.meta, map.meta$archiveType)


factpal <- colorFactor("Paired",map.meta$archiveType)
buff <- 15
l <- leaflet() %>% 
  addTiles() %>% 
  fitBounds(map.meta$lon[i]-buff,map.meta$lat[i]-buff,map.meta$lon[i]+buff,map.meta$lat[i]+buff)
  

  
  
names(map.meta.split) %>%
  purrr::walk( function(df) {
    l <<- l %>%
      addMarkers(data=map.meta.split[[df]],
                 lng=~lon, lat=~lat,
                 label=~as.character(archiveType),
                 popup=~paste(str_c('Dataset: <a href="',link,'">',dataSetName,'</a>'),
                                 # str_c("Elevation: ",elev),
                                  str_c("Archive Type: ",archiveType),
                                  sep = "<br>"),
                 group = df,
                 clusterOptions = markerClusterOptions(removeOutsideVisibleBounds = F),
                 labelOptions = labelOptions(noHide = F,
                                             direction = 'auto'))
  })

l %>%
  addLayersControl(position = "bottomleft",
    overlayGroups = names(map.meta.split),
    options = layersControlOptions(collapsed = FALSE,
                                   opacity = 0.8)
  )
```

### Search the LiPDverse (Beta! doesn't work well yet)
```{r}
#Add google search bar
htmltools::includeHTML("../../googleSearchChunk.html")
```


Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### TAUG (degC) [1-1]
```{r}
plotCol(thisTS,ind = 21)
```

### IMON1953 (months/yr) [1-1]
```{r}
plotCol(thisTS,ind = 37)
```

### depth-range (cm) [1-1]
```{r}
plotCol(thisTS,ind = 1)
```

### TFEV_i (unitless) [1-1]
```{r}
plotCol(thisTS,ind = 4)
```

### TFEV (unitless) [1-1]
```{r}
plotCol(thisTS,ind = 5)
```

### TFEV_s (unitless) [1-1]
```{r}
plotCol(thisTS,ind = 6)
```

### TFEV/3 (unitless) [1-1]
```{r}
plotCol(thisTS,ind = 7)
```

### SFEV_i (unitless) [1-1]
```{r}
plotCol(thisTS,ind = 8)
```

### SFEV (unitless) [1-1]
```{r}
plotCol(thisTS,ind = 9)
```

### SFEV_s (unitless) [1-1]
```{r}
plotCol(thisTS,ind = 10)
```

### SFEV/3 (unitless) [1-1]
```{r}
plotCol(thisTS,ind = 11)
```

### THIV_i (unitless) [1-1]
```{r}
plotCol(thisTS,ind = 12)
```

### THIV (unitless) [1-1]
```{r}
plotCol(thisTS,ind = 13)
```

### THIV_s (unitless) [1-1]
```{r}
plotCol(thisTS,ind = 14)
```

### THIV/3 (unitless) [1-1]
```{r}
plotCol(thisTS,ind = 15)
```

### SHIV_i (unitless) [1-1]
```{r}
plotCol(thisTS,ind = 16)
```

### SHIV (unitless) [1-1]
```{r}
plotCol(thisTS,ind = 17)
```

### SHIV_s (unitless) [1-1]
```{r}
plotCol(thisTS,ind = 18)
```

### SHIV/3 (unitless) [1-1]
```{r}
plotCol(thisTS,ind = 19)
```

### TAUG_i (unitless) [1-1]
```{r}
plotCol(thisTS,ind = 20)
```

### TAUG_s (unitless) [1-1]
```{r}
plotCol(thisTS,ind = 22)
```

### TAUG/3 (unitless) [1-1]
```{r}
plotCol(thisTS,ind = 23)
```

### SAUG_i (unitless) [1-1]
```{r}
plotCol(thisTS,ind = 24)
```

### SAUG (unitless) [1-1]
```{r}
plotCol(thisTS,ind = 25)
```

### SAUG_s (unitless) [1-1]
```{r}
plotCol(thisTS,ind = 26)
```

### SAUG/3 (unitless) [1-1]
```{r}
plotCol(thisTS,ind = 27)
```

### TETE_i (unitless) [1-1]
```{r}
plotCol(thisTS,ind = 28)
```

### TETE (unitless) [1-1]
```{r}
plotCol(thisTS,ind = 29)
```

### TETE_s (unitless) [1-1]
```{r}
plotCol(thisTS,ind = 30)
```

### TETE/3 (unitless) [1-1]
```{r}
plotCol(thisTS,ind = 31)
```

### SETE_i (unitless) [1-1]
```{r}
plotCol(thisTS,ind = 32)
```

### SETE (unitless) [1-1]
```{r}
plotCol(thisTS,ind = 33)
```

### SETE_s (unitless) [1-1]
```{r}
plotCol(thisTS,ind = 34)
```

### SETE/3 (unitless) [1-1]
```{r}
plotCol(thisTS,ind = 35)
```

### IMON1953_i (unitless) [1-1]
```{r}
plotCol(thisTS,ind = 36)
```

### IMON1953_s (unitless) [1-1]
```{r}
plotCol(thisTS,ind = 38)
```

### IMON1953/3 (unitless) [1-1]
```{r}
plotCol(thisTS,ind = 39)
```

### TAUG (degC) [1-2]
```{r}
plotCol(thisTS,ind = 61)
```

### depth-range (cm) [1-2]
```{r}
plotCol(thisTS,ind = 40)
```

### TFEV_i (unitless) [1-2]
```{r}
plotCol(thisTS,ind = 44)
```

### TFEV (unitless) [1-2]
```{r}
plotCol(thisTS,ind = 45)
```

### TFEV_s (unitless) [1-2]
```{r}
plotCol(thisTS,ind = 46)
```

### TFEV/3 (unitless) [1-2]
```{r}
plotCol(thisTS,ind = 47)
```

### SFEV_i (unitless) [1-2]
```{r}
plotCol(thisTS,ind = 48)
```

### SFEV (unitless) [1-2]
```{r}
plotCol(thisTS,ind = 49)
```

### SFEV_s (unitless) [1-2]
```{r}
plotCol(thisTS,ind = 50)
```

### SFEV/3 (unitless) [1-2]
```{r}
plotCol(thisTS,ind = 51)
```

### THIV_i (unitless) [1-2]
```{r}
plotCol(thisTS,ind = 52)
```

### THIV (unitless) [1-2]
```{r}
plotCol(thisTS,ind = 53)
```

### THIV_s (unitless) [1-2]
```{r}
plotCol(thisTS,ind = 54)
```

### THIV/3 (unitless) [1-2]
```{r}
plotCol(thisTS,ind = 55)
```

### SHIV_i (unitless) [1-2]
```{r}
plotCol(thisTS,ind = 56)
```

### SHIV (unitless) [1-2]
```{r}
plotCol(thisTS,ind = 57)
```

### SHIV_s (unitless) [1-2]
```{r}
plotCol(thisTS,ind = 58)
```

### SHIV/3 (unitless) [1-2]
```{r}
plotCol(thisTS,ind = 59)
```

### TAUG_i (unitless) [1-2]
```{r}
plotCol(thisTS,ind = 60)
```

### TAUG_s (unitless) [1-2]
```{r}
plotCol(thisTS,ind = 62)
```

### TAUG/3 (degC) [1-2]
```{r}
plotCol(thisTS,ind = 63)
```

### SAUG_i (unitless) [1-2]
```{r}
plotCol(thisTS,ind = 64)
```

### SAUG (unitless) [1-2]
```{r}
plotCol(thisTS,ind = 65)
```

### SAUG_s (unitless) [1-2]
```{r}
plotCol(thisTS,ind = 66)
```

### SAUG/3 (unitless) [1-2]
```{r}
plotCol(thisTS,ind = 67)
```

### TETE_i (unitless) [1-2]
```{r}
plotCol(thisTS,ind = 68)
```

### TETE (unitless) [1-2]
```{r}
plotCol(thisTS,ind = 69)
```

### TETE_s (unitless) [1-2]
```{r}
plotCol(thisTS,ind = 70)
```

### TETE/3 (unitless) [1-2]
```{r}
plotCol(thisTS,ind = 71)
```

### SETE_i (unitless) [1-2]
```{r}
plotCol(thisTS,ind = 72)
```

### SETE (unitless) [1-2]
```{r}
plotCol(thisTS,ind = 73)
```

### SETE_s (unitless) [1-2]
```{r}
plotCol(thisTS,ind = 74)
```

### SETE/3 (unitless) [1-2]
```{r}
plotCol(thisTS,ind = 75)
```

### IMON1953_i (unitless) [1-2]
```{r}
plotCol(thisTS,ind = 76)
```

### IMON1953 (unitless) [1-2]
```{r}
plotCol(thisTS,ind = 77)
```

### IMON1953_s (unitless) [1-2]
```{r}
plotCol(thisTS,ind = 78)
```

### IMON1953/3 (unitless) [1-2]
```{r}
plotCol(thisTS,ind = 79)
```

### TAUG (degC) [1-3]
```{r}
plotCol(thisTS,ind = 101)
```

### depth-range (cm) [1-3]
```{r}
plotCol(thisTS,ind = 80)
```

### TFEV_i (unitless) [1-3]
```{r}
plotCol(thisTS,ind = 84)
```

### TFEV (unitless) [1-3]
```{r}
plotCol(thisTS,ind = 85)
```

### TFEV_s (unitless) [1-3]
```{r}
plotCol(thisTS,ind = 86)
```

### TFEV/3 (unitless) [1-3]
```{r}
plotCol(thisTS,ind = 87)
```

### SFEV_i (unitless) [1-3]
```{r}
plotCol(thisTS,ind = 88)
```

### SFEV (unitless) [1-3]
```{r}
plotCol(thisTS,ind = 89)
```

### SFEV_s (unitless) [1-3]
```{r}
plotCol(thisTS,ind = 90)
```

### SFEV/3 (unitless) [1-3]
```{r}
plotCol(thisTS,ind = 91)
```

### THIV_i (unitless) [1-3]
```{r}
plotCol(thisTS,ind = 92)
```

### THIV (unitless) [1-3]
```{r}
plotCol(thisTS,ind = 93)
```

### THIV_s (unitless) [1-3]
```{r}
plotCol(thisTS,ind = 94)
```

### THIV/3 (unitless) [1-3]
```{r}
plotCol(thisTS,ind = 95)
```

### SHIV_i (unitless) [1-3]
```{r}
plotCol(thisTS,ind = 96)
```

### SHIV (unitless) [1-3]
```{r}
plotCol(thisTS,ind = 97)
```

### SHIV_s (unitless) [1-3]
```{r}
plotCol(thisTS,ind = 98)
```

### SHIV/3 (unitless) [1-3]
```{r}
plotCol(thisTS,ind = 99)
```

### TAUG_i (unitless) [1-3]
```{r}
plotCol(thisTS,ind = 100)
```

### TAUG_s (unitless) [1-3]
```{r}
plotCol(thisTS,ind = 102)
```

### TAUG/3 (unitless) [1-3]
```{r}
plotCol(thisTS,ind = 103)
```

### SAUG_i (unitless) [1-3]
```{r}
plotCol(thisTS,ind = 104)
```

### SAUG (unitless) [1-3]
```{r}
plotCol(thisTS,ind = 105)
```

### SAUG_s (unitless) [1-3]
```{r}
plotCol(thisTS,ind = 106)
```

### SAUG/3 (unitless) [1-3]
```{r}
plotCol(thisTS,ind = 107)
```

### TETE_i (unitless) [1-3]
```{r}
plotCol(thisTS,ind = 108)
```

### TETE (unitless) [1-3]
```{r}
plotCol(thisTS,ind = 109)
```

### TETE_s (unitless) [1-3]
```{r}
plotCol(thisTS,ind = 110)
```

### TETE/3 (unitless) [1-3]
```{r}
plotCol(thisTS,ind = 111)
```

### SETE_i (unitless) [1-3]
```{r}
plotCol(thisTS,ind = 112)
```

### SETE (unitless) [1-3]
```{r}
plotCol(thisTS,ind = 113)
```

### SETE_s (unitless) [1-3]
```{r}
plotCol(thisTS,ind = 114)
```

### SETE/3 (unitless) [1-3]
```{r}
plotCol(thisTS,ind = 115)
```

### IMON1953_i (unitless) [1-3]
```{r}
plotCol(thisTS,ind = 116)
```

### IMON1953 (unitless) [1-3]
```{r}
plotCol(thisTS,ind = 117)
```

### IMON1953_s (unitless) [1-3]
```{r}
plotCol(thisTS,ind = 118)
```

### IMON1953/3 (unitless) [1-3]
```{r}
plotCol(thisTS,ind = 119)
```
