---
title: "TN062-0550.Barron.2018"
output: 
  flexdashboard::flex_dashboard:
    theme: bootstrap
    source_code: embed
    orientation: rows
---

```{r setup, include = FALSE}
library(flexdashboard)
library(maptools)
library(tidyverse)
library(purrr)
library(leaflet)
library(plotly)
library(lipdR)
library(dygraphs)
library(geoChronR)

#read functions
source("../../functions.R")


load("../../temp.Rdata")

#remove columns we don't want to plot
varNames <- sapply(TS, "[[","paleoData_variableName")

# good <- which(!(varNames %in% c("year","depth","age")))
# TS <- TS[good]


#All datasets
dsn <- sapply(TS,"[[","dataSetName")
ui <- which(!duplicated(dsn))
udsn <- dsn[ui]
lat <- as.numeric(sapply(TS,"[[","geo_latitude")[ui])
lon <- as.numeric(sapply(TS,"[[","geo_longitude")[ui])
#elev <- sapply(TS,"[[","geo_elevation")[ui]
archiveType <- sapply(TS,"[[","archiveType")[ui]
link <- paste0(udsn,".html") %>% 
  str_replace_all("'","_")

#Organize metadata for map
map.meta <- data.frame(dataSetName = udsn, #datasetname
                       lat = lat,#lat
                       lon = lon,#lon
                      # elev = elev,#elevation
                       archiveType = factor(archiveType),#archiveType
                       link = link)#Link


#set index number

i = 123
thisTS <- TS[which(udsn[i] == dsn)]
```
#TN062-0550.Barron.2018

Metadata {.sidebar}
-------------------------------------
[Download LiPD file](TN062-0550.Barron.2018.lpd)
            

[Edit LiPD file](http://lipd.net/playground?source=http://lipdverse.org/wNAm0_1_0/TN062-0550.Barron.2018.lpd)
            

[Download data only (csv)](TN062-0550.Barron.2018.csv)
            

[Report an issue (include dataset name)](https://github.com/nickmckay/LiPDverse/issues)

<details open style="margin-left: 0px">
<summary>root</summary>
<p style="margin-left: 0px"><strong>archiveType: </strong>marine sediment
<p style="margin-left: 0px"><strong>lipdVersion: </strong>1.3
</details>
<details>
<summary>pub</summary>
<details style="margin-left: 10px">
<summary>pub1</summary>
<p style="margin-left: 10px"><strong>journal: </strong>Quaternary International
<p style="margin-left: 10px"><strong>volume: </strong>469
<p style="margin-left: 10px"><strong>pages: </strong>109-119
<p style="margin-left: 10px"><strong>pubYear: </strong>NA
<p style="margin-left: 10px"><strong>title: </strong>High-resolution climate of the past ∼7300 years of coastal northernmost California: Results from diatoms, silicoflagellates, and pollen
</details>
</details>
<details open style="margin-left: 0px">
<summary>geo</summary>
<p style="margin-left: 0px"><strong>latitude: </strong>40.8656
<p style="margin-left: 0px"><strong>longitude: </strong>-124.573
<p style="margin-left: 0px"><strong>elevation: </strong>-569
<p style="margin-left: 0px"><strong>siteName: </strong>TN062-0550
</details>
<details open>
<summary>PaleoData columns</summary>
<details style="margin-left: 10px">
<summary>depth (cm) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB9bb9e2f9
<p style="margin-left: 10px"><strong>variableName: </strong>depth
<p style="margin-left: 10px"><strong>units: </strong>cm
<p style="margin-left: 10px"><strong>description: </strong>composite depth
</details>
<details style="margin-left: 10px">
<summary>age (yr BP) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB5bbb384d
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>yr BP
<p style="margin-left: 10px"><strong>description: </strong>Original age in years before 1950 AD
</details>
<details style="margin-left: 10px">
<summary>Picea (percent) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBe7dad2eb
<p style="margin-left: 10px"><strong>variableName: </strong>Picea
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>description: </strong>Picea = proxy for winter temp
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>TRUE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>direction: </strong>positive
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>seasonality: </strong>winter
<p style="margin-left: 20px"><strong>variable: </strong>T
<p style="margin-left: 20px"><strong>variableDetail: </strong>air@surface
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>Sequoia (percent) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBa93dede4
<p style="margin-left: 10px"><strong>variableName: </strong>Sequoia
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>description: </strong>Sequoia = proxy for coastal fog (=upwelling) and has also been interpreted as coastal hydroclimate
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>TRUE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>direction: </strong>positive
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>seasonality: </strong>not specified
<p style="margin-left: 20px"><strong>variable: </strong>M
<p style="margin-left: 20px"><strong>variableDetail: </strong>upwelling/coastal fog
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>Quercus (percent) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB49245d00
<p style="margin-left: 10px"><strong>variableName: </strong>Quercus
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>description: </strong>Quercus = warm, dry, mostly from interior. Effective moisture
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>TRUE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>direction: </strong>negative
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>seasonality: </strong>summer
<p style="margin-left: 20px"><strong>variable: </strong>M
<p style="margin-left: 20px"><strong>variableDetail: </strong>eff
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>Alnus (percent) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBeb8b7a07
<p style="margin-left: 10px"><strong>variableName: </strong>Alnus
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>description: </strong>Anus (alder) = wet along river banks
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>TRUE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>direction: </strong>positive
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>seasonality: </strong>not specified
<p style="margin-left: 20px"><strong>variable: </strong>M
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>depthRange (cm) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBe8c80314
<p style="margin-left: 10px"><strong>variableName: </strong>depthRange
<p style="margin-left: 10px"><strong>units: </strong>cm
</details>
<details style="margin-left: 10px">
<summary>Calibrated (unitless) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB5f263302
<p style="margin-left: 10px"><strong>variableName: </strong>Calibrated
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>description: </strong>R for radiocarbon and CAL for calibrated age
</details>
<details style="margin-left: 10px">
<summary>depth (cm) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB39869b05
<p style="margin-left: 10px"><strong>variableName: </strong>depth
<p style="margin-left: 10px"><strong>units: </strong>cm
<p style="margin-left: 10px"><strong>description: </strong>composite depth
</details>
<details style="margin-left: 10px">
<summary>age (yr BP) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB3b97d1b8
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>yr BP
<p style="margin-left: 10px"><strong>description: </strong>calibarated years before 1950
</details>
<details style="margin-left: 10px">
<summary>depthRange (cm) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB7439db68
<p style="margin-left: 10px"><strong>variableName: </strong>depthRange
<p style="margin-left: 10px"><strong>units: </strong>cm
</details>
<details style="margin-left: 10px">
<summary>Calibrated (unitless) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB1edd6bbb
<p style="margin-left: 10px"><strong>variableName: </strong>Calibrated
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>description: </strong>R for radiocarbon, CAL for calibrated age
</details>
<details style="margin-left: 10px">
<summary>Fragilariopsis (percent) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB05d286cd
<p style="margin-left: 10px"><strong>variableName: </strong>Fragilariopsis
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>description: </strong>Fragilariopsis doliolus. Winter SST proxy
</details>
<details style="margin-left: 10px">
<summary>depth (cm) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB3e7e56fc
<p style="margin-left: 10px"><strong>variableName: </strong>depth
<p style="margin-left: 10px"><strong>units: </strong>cm
<p style="margin-left: 10px"><strong>description: </strong>Composite depth
</details>
<details style="margin-left: 10px">
<summary>age (yr BP) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB52b1937a
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>yr BP
<p style="margin-left: 10px"><strong>description: </strong>original age
</details>
<details style="margin-left: 10px">
<summary>Dc_stapedia (percent) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB47918ab8
<p style="margin-left: 10px"><strong>variableName: </strong>Dc_stapedia
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>description: </strong>proxy for subtropical water
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>TRUE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>direction: </strong>negative
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>seasonality: </strong>spring/summer
<p style="margin-left: 20px"><strong>variable: </strong>upwelling
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>Dc_stapedia_aspinosa (percent) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB5e293c85
<p style="margin-left: 10px"><strong>variableName: </strong>Dc_stapedia_aspinosa
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>description: </strong>Dc. stapedia aspinosa proxy for subtropical water
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>TRUE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>direction: </strong>negative
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>seasonality: </strong>spring/summer
<p style="margin-left: 20px"><strong>variable: </strong>upwelling
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>Dc_stapedia_spinosa (percent) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBfd6711c4
<p style="margin-left: 10px"><strong>variableName: </strong>Dc_stapedia_spinosa
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>description: </strong>Dc. stapedia spinosa proxy for subtropical water
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>TRUE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>direction: </strong>negative
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>seasonality: </strong>spring/summer
<p style="margin-left: 20px"><strong>variable: </strong>upwelling
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>total_Dc_stapedia (percent) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB773c247c
<p style="margin-left: 10px"><strong>variableName: </strong>total_Dc_stapedia
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>description: </strong>total Dc. stapedia proxy for subtropical water
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>TRUE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>direction: </strong>negative
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>seasonality: </strong>spring/summer
<p style="margin-left: 20px"><strong>variable: </strong>upwelling
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>S_speculum_var_minutus (percent) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBd49b515b
<p style="margin-left: 10px"><strong>variableName: </strong>S_speculum_var_minutus
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>description: </strong>S..speculum var. minutus proxy for cold upwelling water
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>TRUE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>direction: </strong>positive
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>seasonality: </strong>spring/summer
<p style="margin-left: 20px"><strong>variable: </strong>upwelling
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>depthRange (cm) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBafc93b60
<p style="margin-left: 10px"><strong>variableName: </strong>depthRange
<p style="margin-left: 10px"><strong>units: </strong>cm
</details>
<details style="margin-left: 10px">
<summary>Calibrated (unitless) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB173a177b
<p style="margin-left: 10px"><strong>variableName: </strong>Calibrated
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>description: </strong>R for radiocarbon and CAL for calibrated age
</details>

Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### Sitemap

```{r}
  map.meta.split <- split(map.meta, map.meta$archiveType)


factpal <- colorFactor("Paired",map.meta$archiveType)
buff <- 15
l <- leaflet() %>% 
  addTiles() %>% 
  fitBounds(map.meta$lon[i]-buff,map.meta$lat[i]-buff,map.meta$lon[i]+buff,map.meta$lat[i]+buff)
  

  
  
names(map.meta.split) %>%
  purrr::walk( function(df) {
    l <<- l %>%
      addMarkers(data=map.meta.split[[df]],
                 lng=~lon, lat=~lat,
                 label=~as.character(archiveType),
                 popup=~paste(str_c('Dataset: <a href="',link,'">',dataSetName,'</a>'),
                                 # str_c("Elevation: ",elev),
                                  str_c("Archive Type: ",archiveType),
                                  sep = "<br>"),
                 group = df,
                 clusterOptions = markerClusterOptions(removeOutsideVisibleBounds = F),
                 labelOptions = labelOptions(noHide = F,
                                             direction = 'auto'))
  })

l %>%
  addLayersControl(position = "bottomleft",
    overlayGroups = names(map.meta.split),
    options = layersControlOptions(collapsed = FALSE,
                                   opacity = 0.8)
  )
```

### Search the LiPDverse (Beta! doesn't work well yet)
```{r}
#Add google search bar
htmltools::includeHTML("../../googleSearchChunk.html")
```


Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### Picea (percent) [1-1]
```{r}
plotCol(thisTS,ind = 5)
```

### Sequoia (percent) [1-1]
```{r}
plotCol(thisTS,ind = 6)
```

### Quercus (percent) [1-1]
```{r}
plotCol(thisTS,ind = 7)
```

### Alnus (percent) [1-1]
```{r}
plotCol(thisTS,ind = 8)
```

### depthRange (cm) [1-1]
```{r}
plotCol(thisTS,ind = 1)
```

### Calibrated (unitless) [1-1]
```{r}
plotCol(thisTS,ind = 4)
```

### depthRange (cm) [1-2]
```{r}
plotCol(thisTS,ind = 9)
```

### Calibrated (unitless) [1-2]
```{r}
plotCol(thisTS,ind = 12)
```

### Fragilariopsis (percent) [1-2]
```{r}
plotCol(thisTS,ind = 13)
```

### Dc_stapedia (percent) [1-3]
```{r}
plotCol(thisTS,ind = 18)
```

### Dc_stapedia_aspinosa (percent) [1-3]
```{r}
plotCol(thisTS,ind = 19)
```

### Dc_stapedia_spinosa (percent) [1-3]
```{r}
plotCol(thisTS,ind = 20)
```

### total_Dc_stapedia (percent) [1-3]
```{r}
plotCol(thisTS,ind = 21)
```

### S_speculum_var_minutus (percent) [1-3]
```{r}
plotCol(thisTS,ind = 22)
```

### depthRange (cm) [1-3]
```{r}
plotCol(thisTS,ind = 14)
```

### Calibrated (unitless) [1-3]
```{r}
plotCol(thisTS,ind = 17)
```
