---
title: "Aus-WilkinsKeilambeteGnotuk"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
    theme: bootstrap
    source_code: embed
    orientation: rows
---

```{r setup, include = FALSE}
library(flexdashboard)
library(maptools)
library(tidyverse)
library(purrr)
library(leaflet)
library(plotly)
library(lipdR)
library(dygraphs)
library(geoChronR)
library(lipdverseR)
#read functions
load("../../temp.Rdata")
load("../../chronTemp.Rdata")


#remove columns we don't want to plot
varNames <- sapply(TS, "[[","paleoData_variableName")

# good <- which(!(varNames %in% c("year","depth","age")))
# TS <- TS[good]


#All datasets
dsn <- sapply(TS,"[[","dataSetName")
ui <- which(!duplicated(dsn))
udsn <- dsn[ui]
lat <- as.numeric(sapply(TS,"[[","geo_latitude")[ui])
lon <- as.numeric(sapply(TS,"[[","geo_longitude")[ui])
#elev <- sapply(TS,"[[","geo_elevation")[ui]
archiveType <- sapply(TS,"[[","archiveType")[ui]
link <- paste0(udsn,".html") %>% 
  str_replace_all("'","_")

#Organize metadata for map
map.meta <- data.frame(dataSetName = udsn, #datasetname
                       lat = lat,#lat
                       lon = lon,#lon
                      # elev = elev,#elevation
                       archiveType = factor(archiveType),#archiveType
                       link = link)#Link


#set index number

i = 37
thisTS <- TS[which(udsn[i] == dsn)]
```
#Aus-WilkinsKeilambeteGnotuk

Metadata {.sidebar}
-------------------------------------
[Download LiPD file](Aus-WilkinsKeilambeteGnotuk.lpd)
            

[Edit LiPD file](http://lipd.net/playground?source=http://lipdverse.org/globalHolocene/0_25_5/Aus-WilkinsKeilambeteGnotuk.lpd)
            

[Download paleoData only (csv)](Aus-WilkinsKeilambeteGnotuk.csv)
            

[Report an issue (include dataset name)](https://github.com/nickmckay/LiPDverse/issues)

<details open style="margin-left: 0px">
<summary>root</summary>
<p style="margin-left: 0px"><strong>archiveType: </strong>LakeSediment
<p style="margin-left: 0px"><strong>lipdVersion: </strong>1.3
</details>
<details>
<summary>pub</summary>
<details style="margin-left: 10px">
<summary>pub1</summary>
<p style="margin-left: 10px"><strong>author: </strong>list(list(name = "NEEDS AUTHORS!"))
<p style="margin-left: 10px"><strong>citeKey: </strong>needs0holocenelakelevelfluctuat
<p style="margin-left: 10px"><strong>journal: </strong>The Holocene
<p style="margin-left: 10px"><strong>volume: </strong>9
<p style="margin-left: 10px"><strong>pages: </strong>75-85
<p style="margin-left: 10px"><strong>title: </strong>Holocene lake-level fluctuations in Lakes Keilambete and Gnotuk, southwestern Victoria, Australia
</details>
<details style="margin-left: 10px">
<summary>pub2</summary>
<p style="margin-left: 10px"><strong>author: </strong>list(list(name = NA))
</details>
</details>
<details open style="margin-left: 0px">
<summary>geo</summary>
<p style="margin-left: 0px"><strong>latitude: </strong>-38.2135
<p style="margin-left: 0px"><strong>longitude: </strong>142.989
<p style="margin-left: 0px"><strong>elevation: </strong>104
<p style="margin-left: 0px"><strong>siteName: </strong>Lake Keilambete
<p style="margin-left: 0px"><strong>pages2kRegion: </strong>Aus
</details>
<details open>
<summary>PaleoData columns</summary>
<details style="margin-left: 10px">
<summary>year (AD) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RVsjuqEUeEh
<p style="margin-left: 10px"><strong>variableName: </strong>year
<p style="margin-left: 10px"><strong>units: </strong>AD
<p style="margin-left: 10px"><strong>description: </strong>Year AD
</details>
<details style="margin-left: 10px">
<summary>age (BP) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RWzx9zELfHc
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>BP
<p style="margin-left: 10px"><strong>description: </strong>Years before present (1950) BP
</details>
<details style="margin-left: 10px">
<summary>MS (cgs) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>Aus_235
<p style="margin-left: 10px"><strong>variableName: </strong>MS
<p style="margin-left: 10px"><strong>units: </strong>cgs
<p style="margin-left: 10px"><strong>description: </strong>Magnetic Susceptibility
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>year (AD) [2-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RSLSy7ZgMQs
<p style="margin-left: 10px"><strong>variableName: </strong>year
<p style="margin-left: 10px"><strong>units: </strong>AD
<p style="margin-left: 10px"><strong>description: </strong>Year AD
</details>
<details style="margin-left: 10px">
<summary>age (BP) [2-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>R0C4bSC4t7O
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>BP
<p style="margin-left: 10px"><strong>description: </strong>Years before present (1950) BP
</details>
<details style="margin-left: 10px">
<summary>density (g/cm3) [2-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>Aus_234
<p style="margin-left: 10px"><strong>variableName: </strong>density
<p style="margin-left: 10px"><strong>units: </strong>g/cm3
<p style="margin-left: 10px"><strong>description: </strong>Density
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>year (AD) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RqmyW1y2Dxa
<p style="margin-left: 10px"><strong>variableName: </strong>year
<p style="margin-left: 10px"><strong>units: </strong>AD
<p style="margin-left: 10px"><strong>description: </strong>Year AD
</details>
<details style="margin-left: 10px">
<summary>age (BP) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>R4lwFCuYFGD
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>BP
<p style="margin-left: 10px"><strong>description: </strong>Years before present (1950) BP
</details>
<details style="margin-left: 10px">
<summary>Laminae (missing) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>Aus_239
<p style="margin-left: 10px"><strong>variableName: </strong>Laminae
<p style="margin-left: 10px"><strong>units: </strong>missing
<p style="margin-left: 10px"><strong>description: </strong>number of laminae within a one centimeter interval
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>TRUE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>basis: </strong>correlation with historic records by Bowler (1970) and Timms (1976) measurements made on modern environment
<p style="margin-left: 20px"><strong>direction: </strong>negative
<p style="margin-left: 20px"><strong>interpDirection: </strong>negative
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>variable: </strong>M
<p style="margin-left: 20px"><strong>variableDetail: </strong>P/E LakeCatchment
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>depth.top (cm) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>Aus_236
<p style="margin-left: 10px"><strong>variableName: </strong>depth.top
<p style="margin-left: 10px"><strong>units: </strong>cm
<p style="margin-left: 10px"><strong>description: </strong>Top Depth of Sample
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>depth.bottom (cm) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>Aus_237
<p style="margin-left: 10px"><strong>variableName: </strong>depth.bottom
<p style="margin-left: 10px"><strong>units: </strong>cm
<p style="margin-left: 10px"><strong>description: </strong>Bottom Depth of Sample
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>year (AD) [4-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RsS21fbLP1d
<p style="margin-left: 10px"><strong>variableName: </strong>year
<p style="margin-left: 10px"><strong>units: </strong>AD
<p style="margin-left: 10px"><strong>description: </strong>Year AD
</details>
<details style="margin-left: 10px">
<summary>age (BP) [4-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>Rrdz1FHuPHr
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>BP
<p style="margin-left: 10px"><strong>description: </strong>Years before present (1950) BP
</details>
<details style="margin-left: 10px">
<summary>depth.top (cm) [4-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>Aus_240
<p style="margin-left: 10px"><strong>variableName: </strong>depth.top
<p style="margin-left: 10px"><strong>units: </strong>cm
<p style="margin-left: 10px"><strong>description: </strong>Top Depth of Sample
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>depth.bottom (cm) [4-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>Aus_241
<p style="margin-left: 10px"><strong>variableName: </strong>depth.bottom
<p style="margin-left: 10px"><strong>units: </strong>cm
<p style="margin-left: 10px"><strong>description: </strong>Bottom Depth of Sample
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>waterContent (percent) [4-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>Aus_243
<p style="margin-left: 10px"><strong>variableName: </strong>waterContent
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>description: </strong>water content of sample
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>LOI (percent) [4-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>Aus_244
<p style="margin-left: 10px"><strong>variableName: </strong>LOI
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>description: </strong>Loss on Ignition of sample
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>year (AD) [5-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RL1OqergeXY
<p style="margin-left: 10px"><strong>variableName: </strong>year
<p style="margin-left: 10px"><strong>units: </strong>AD
<p style="margin-left: 10px"><strong>description: </strong>Year AD
</details>
<details style="margin-left: 10px">
<summary>age (BP) [5-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>R8HVX1FitNl
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>BP
<p style="margin-left: 10px"><strong>description: </strong>Years before present (1950) BP
</details>
<details style="margin-left: 10px">
<summary>depth.lake (m) [5-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>Aus_247
<p style="margin-left: 10px"><strong>variableName: </strong>depth.lake
<p style="margin-left: 10px"><strong>units: </strong>m
<p style="margin-left: 10px"><strong>description: </strong>lake depth relative to modern lake levels
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>basis: </strong>correlation with historic records by Bowler (1970) and Timms (1976)
<p style="margin-left: 20px"><strong>direction: </strong>positive
<p style="margin-left: 20px"><strong>interpDirection: </strong>positive
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>variable: </strong>M
<p style="margin-left: 20px"><strong>variableDetail: </strong>P/E LakeCatchment
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>sedimentWeight (percent) [5-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>Aus_248
<p style="margin-left: 10px"><strong>variableName: </strong>sedimentWeight
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>description: </strong>percentage of sediment with grain size greater than 63um
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>basis: </strong>correlation with historic records by Bowler (1970) and Timms (1976)
<p style="margin-left: 20px"><strong>direction: </strong>negative
<p style="margin-left: 20px"><strong>interpDirection: </strong>negative
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>variable: </strong>M
<p style="margin-left: 20px"><strong>variableDetail: </strong>P/E LakeCatchment
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>year (AD) [6-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>Rs5EpeOUFWm
<p style="margin-left: 10px"><strong>variableName: </strong>year
<p style="margin-left: 10px"><strong>units: </strong>AD
<p style="margin-left: 10px"><strong>description: </strong>Year AD
</details>
<details style="margin-left: 10px">
<summary>age (BP) [6-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RHQiBYMX7RY
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>BP
<p style="margin-left: 10px"><strong>description: </strong>Years before present (1950) BP
</details>
<details style="margin-left: 10px">
<summary>sedimentWeight (percent) [6-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>Aus_257
<p style="margin-left: 10px"><strong>variableName: </strong>sedimentWeight
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>description: </strong>percentage of sediment with grain size greater than 63um
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>basis: </strong>correlation with historic records by Bowler (1970) and Timms (1976)
<p style="margin-left: 20px"><strong>direction: </strong>negative
<p style="margin-left: 20px"><strong>interpDirection: </strong>negative
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>variable: </strong>M
<p style="margin-left: 20px"><strong>variableDetail: </strong>P/E LakeCatchment
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>depth.lake (m) [6-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>Aus_260
<p style="margin-left: 10px"><strong>variableName: </strong>depth.lake
<p style="margin-left: 10px"><strong>units: </strong>m
<p style="margin-left: 10px"><strong>description: </strong>lake depth relative to modern lake levels
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>direction: </strong>positive
<p style="margin-left: 20px"><strong>interpDirection: </strong>positive
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>variable: </strong>M
<p style="margin-left: 20px"><strong>variableDetail: </strong>P/E LakeCatchment
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>depth.top (cm) [6-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>Aus_249
<p style="margin-left: 10px"><strong>variableName: </strong>depth.top
<p style="margin-left: 10px"><strong>units: </strong>cm
<p style="margin-left: 10px"><strong>description: </strong>Top Depth of Sample
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>depth.bottom (cm) [6-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>Aus_252
<p style="margin-left: 10px"><strong>variableName: </strong>depth.bottom
<p style="margin-left: 10px"><strong>units: </strong>cm
<p style="margin-left: 10px"><strong>description: </strong>Bottom Depth of Sample
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>year (AD) [7-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RPxGWSfZAOE
<p style="margin-left: 10px"><strong>variableName: </strong>year
<p style="margin-left: 10px"><strong>units: </strong>AD
<p style="margin-left: 10px"><strong>description: </strong>Year AD
</details>
<details style="margin-left: 10px">
<summary>age (BP) [7-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RRX6TAkysIx
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>BP
<p style="margin-left: 10px"><strong>description: </strong>Years before present (1950) BP
</details>
<details style="margin-left: 10px">
<summary>CaCO3 (percent) [7-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>Aus_258
<p style="margin-left: 10px"><strong>variableName: </strong>CaCO3
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>description: </strong>percentage of whole sample that is composed of carbonate
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>TRUE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>basis: </strong>correlation with historic records by Bowler (1970) and Timms (1976)
<p style="margin-left: 20px"><strong>direction: </strong>negative
<p style="margin-left: 20px"><strong>interpDirection: </strong>negative
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>variable: </strong>M
<p style="margin-left: 20px"><strong>variableDetail: </strong>P/E LakeCatchment
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>year (AD) [8-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RE3pqISsyQe
<p style="margin-left: 10px"><strong>variableName: </strong>year
<p style="margin-left: 10px"><strong>units: </strong>AD
<p style="margin-left: 10px"><strong>description: </strong>Year AD
</details>
<details style="margin-left: 10px">
<summary>age (BP) [8-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RSP4scFcgc1
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>BP
<p style="margin-left: 10px"><strong>description: </strong>Years before present (1950) BP
</details>
<details style="margin-left: 10px">
<summary>CaCO3 (percent) [8-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>Aus_265
<p style="margin-left: 10px"><strong>variableName: </strong>CaCO3
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>description: </strong>percentage of 63um size fraction that is comprised of carbonate
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>TRUE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>basis: </strong>correlation with historic records by Bowler (1970) and Timms (1976)
<p style="margin-left: 20px"><strong>direction: </strong>negative
<p style="margin-left: 20px"><strong>interpDirection: </strong>negative
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>variable: </strong>M
<p style="margin-left: 20px"><strong>variableDetail: </strong>P/E LakeCatchment
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>depth.top (cm) [8-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>Aus_261
<p style="margin-left: 10px"><strong>variableName: </strong>depth.top
<p style="margin-left: 10px"><strong>units: </strong>cm
<p style="margin-left: 10px"><strong>description: </strong>Top Depth of Sample
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>depth.bottom (cm) [8-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>Aus_262
<p style="margin-left: 10px"><strong>variableName: </strong>depth.bottom
<p style="margin-left: 10px"><strong>units: </strong>cm
<p style="margin-left: 10px"><strong>description: </strong>Bottom Depth of Sample
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>year (AD) [9-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RbOmIQ3zKAm
<p style="margin-left: 10px"><strong>variableName: </strong>year
<p style="margin-left: 10px"><strong>units: </strong>AD
<p style="margin-left: 10px"><strong>description: </strong>Year AD
</details>
<details style="margin-left: 10px">
<summary>age (BP) [9-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>Raye13BpdMo
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>BP
<p style="margin-left: 10px"><strong>description: </strong>Years before present (1950) BP
</details>
<details style="margin-left: 10px">
<summary>CaCO3 (percent) [9-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>Aus_263
<p style="margin-left: 10px"><strong>variableName: </strong>CaCO3
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>description: </strong>percentage of 63um size fraction that is comprised of carbonate
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>basis: </strong>correlation with historic records by Bowler (1970) and Timms (1976)
<p style="margin-left: 20px"><strong>direction: </strong>negative
<p style="margin-left: 20px"><strong>interpDirection: </strong>negative
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>variable: </strong>M
<p style="margin-left: 20px"><strong>variableDetail: </strong>P/E LakeCatchment
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>year (AD) [10-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RFOWjOjNgFR
<p style="margin-left: 10px"><strong>variableName: </strong>year
<p style="margin-left: 10px"><strong>units: </strong>AD
<p style="margin-left: 10px"><strong>description: </strong>Year AD
</details>
<details style="margin-left: 10px">
<summary>age (BP) [10-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RGXmVj5wMHy
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>BP
<p style="margin-left: 10px"><strong>description: </strong>Years before present (1950) BP
</details>
<details style="margin-left: 10px">
<summary>Laminae (missing) [10-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>Aus_266
<p style="margin-left: 10px"><strong>variableName: </strong>Laminae
<p style="margin-left: 10px"><strong>units: </strong>missing
<p style="margin-left: 10px"><strong>description: </strong>number of laminae within a one centimeter interval
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>TRUE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>basis: </strong>correlation with historic records by Bowler (1970) and Timms (1976) measurements made on modern environment
<p style="margin-left: 20px"><strong>direction: </strong>negative
<p style="margin-left: 20px"><strong>interpDirection: </strong>negative
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>variable: </strong>M
<p style="margin-left: 20px"><strong>variableDetail: </strong>P/E LakeCatchment
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>year (AD) [11-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RORqMwtZJ5O
<p style="margin-left: 10px"><strong>variableName: </strong>year
<p style="margin-left: 10px"><strong>units: </strong>AD
<p style="margin-left: 10px"><strong>description: </strong>Year AD
</details>
<details style="margin-left: 10px">
<summary>age (BP) [11-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RmQLTp1oOca
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>BP
<p style="margin-left: 10px"><strong>description: </strong>Years before present (1950) BP
</details>
<details style="margin-left: 10px">
<summary>waterContent (percent) [11-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>Aus_267
<p style="margin-left: 10px"><strong>variableName: </strong>waterContent
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>description: </strong>water content of sample
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>year (AD) [12-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RjOELGxOwPF
<p style="margin-left: 10px"><strong>variableName: </strong>year
<p style="margin-left: 10px"><strong>units: </strong>AD
<p style="margin-left: 10px"><strong>description: </strong>Year AD
</details>
<details style="margin-left: 10px">
<summary>age (BP) [12-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>Rx4rmKEyjCt
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>BP
<p style="margin-left: 10px"><strong>description: </strong>Years before present (1950) BP
</details>
<details style="margin-left: 10px">
<summary>MS (cgs) [12-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>Aus_271
<p style="margin-left: 10px"><strong>variableName: </strong>MS
<p style="margin-left: 10px"><strong>units: </strong>cgs
<p style="margin-left: 10px"><strong>description: </strong>Magnetic Susceptibility
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>year (AD) [13-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RWma6tD28rd
<p style="margin-left: 10px"><strong>variableName: </strong>year
<p style="margin-left: 10px"><strong>units: </strong>AD
<p style="margin-left: 10px"><strong>description: </strong>Year AD
</details>
<details style="margin-left: 10px">
<summary>age (BP) [13-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RkdUVDqu7Uh
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>BP
<p style="margin-left: 10px"><strong>description: </strong>Years before present (1950) BP
</details>
<details style="margin-left: 10px">
<summary>density (g/cm3) [13-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>Aus_270
<p style="margin-left: 10px"><strong>variableName: </strong>density
<p style="margin-left: 10px"><strong>units: </strong>g/cm3
<p style="margin-left: 10px"><strong>description: </strong>Density
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>year (AD) [14-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>Rb0S74h1vr6
<p style="margin-left: 10px"><strong>variableName: </strong>year
<p style="margin-left: 10px"><strong>units: </strong>AD
<p style="margin-left: 10px"><strong>description: </strong>Year AD
</details>
<details style="margin-left: 10px">
<summary>age (BP) [14-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>Riw5MPfgeea
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>BP
<p style="margin-left: 10px"><strong>description: </strong>Years before present (1950) BP
</details>
<details style="margin-left: 10px">
<summary>TDS (mg/L) [14-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>Aus_277
<p style="margin-left: 10px"><strong>variableName: </strong>TDS
<p style="margin-left: 10px"><strong>units: </strong>mg/L
<p style="margin-left: 10px"><strong>description: </strong>Reconstructed salinity
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>TRUE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>basis: </strong>491 modern salinity measurements
<p style="margin-left: 20px"><strong>direction: </strong>negative
<p style="margin-left: 20px"><strong>interpDirection: </strong>negative
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>variable: </strong>M
<p style="margin-left: 20px"><strong>variableDetail: </strong>P/E LakeWater
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>DiacyprisCompacta (mmol/mol) [14-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>Aus_283
<p style="margin-left: 10px"><strong>variableName: </strong>DiacyprisCompacta
<p style="margin-left: 10px"><strong>units: </strong>mmol/mol
<p style="margin-left: 10px"><strong>description: </strong>Calculated Sr/Ca ratio of water from measured Sr/Ca of ostracod test
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>basis: </strong>Relationship established by: Chivas AR, De Deckker P and Shelley JMG (1985) Strontium content of ostracods indicates lacustrine palaeosalinity. Nature 316: 251253.
<p style="margin-left: 20px"><strong>direction: </strong>positive
<p style="margin-left: 20px"><strong>interpDirection: </strong>positive
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>variable: </strong>S
<p style="margin-left: 20px"><strong>variableDetail: </strong>Salinity LakeWater
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>MytilocyprisPraenuncia (mmol/mol) [14-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>Aus_284
<p style="margin-left: 10px"><strong>variableName: </strong>MytilocyprisPraenuncia
<p style="margin-left: 10px"><strong>units: </strong>mmol/mol
<p style="margin-left: 10px"><strong>description: </strong>Calculated Sr/Ca ratio of water from measured Sr/Ca of ostracod test
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>basis: </strong>Relationship established by: Chivas AR, De Deckker P and Shelley JMG (1985) Strontium content of ostracods indicates lacustrine palaeosalinity. Nature 316: 251253.
<p style="margin-left: 20px"><strong>direction: </strong>positive
<p style="margin-left: 20px"><strong>interpDirection: </strong>positive
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>variable: </strong>S
<p style="margin-left: 20px"><strong>variableDetail: </strong>Salinity LakeWater
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>depth.top (cm) [14-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>Aus_272
<p style="margin-left: 10px"><strong>variableName: </strong>depth.top
<p style="margin-left: 10px"><strong>units: </strong>cm
<p style="margin-left: 10px"><strong>description: </strong>Top Depth of Sample
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>depth.bottom (cm) [14-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>Aus_273
<p style="margin-left: 10px"><strong>variableName: </strong>depth.bottom
<p style="margin-left: 10px"><strong>units: </strong>cm
<p style="margin-left: 10px"><strong>description: </strong>Bottom Depth of Sample
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>AustralocyprisRobusta (missing) [14-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>Aus_275
<p style="margin-left: 10px"><strong>variableName: </strong>AustralocyprisRobusta
<p style="margin-left: 10px"><strong>units: </strong>missing
<p style="margin-left: 10px"><strong>description: </strong>Count of Ostracod tests
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>ReticyprisHerbstii (missing) [14-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>Aus_276
<p style="margin-left: 10px"><strong>variableName: </strong>ReticyprisHerbstii
<p style="margin-left: 10px"><strong>units: </strong>missing
<p style="margin-left: 10px"><strong>description: </strong>Count of Ostracod tests
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>SE (mg/L) [14-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>Aus_278
<p style="margin-left: 10px"><strong>variableName: </strong>SE
<p style="margin-left: 10px"><strong>units: </strong>mg/L
<p style="margin-left: 10px"><strong>description: </strong>Standard Error
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Sr/Ca (mmol/mol) [14-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>Aus_281
<p style="margin-left: 10px"><strong>variableName: </strong>Sr/Ca
<p style="margin-left: 10px"><strong>units: </strong>mmol/mol
<p style="margin-left: 10px"><strong>description: </strong>Sr/Ca ratio in ostracod valve
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>year (AD) [15-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>ReVexuoy2eT
<p style="margin-left: 10px"><strong>variableName: </strong>year
<p style="margin-left: 10px"><strong>units: </strong>AD
<p style="margin-left: 10px"><strong>description: </strong>Year AD
</details>
<details style="margin-left: 10px">
<summary>age (BP) [15-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RtK6RgMBiNK
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>BP
<p style="margin-left: 10px"><strong>description: </strong>Years before present (1950) BP
</details>
<details style="margin-left: 10px">
<summary>AustralocyprisRobusta (mmol/mol) [15-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>Aus_282
<p style="margin-left: 10px"><strong>variableName: </strong>AustralocyprisRobusta
<p style="margin-left: 10px"><strong>units: </strong>mmol/mol
<p style="margin-left: 10px"><strong>description: </strong>Calculated Sr/Ca ratio of water from measured Sr/Ca of ostracod test
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>basis: </strong>Relationship established by: Chivas AR, De Deckker P and Shelley JMG (1985) Strontium content of ostracods indicates lacustrine palaeosalinity. Nature 316: 251253.
<p style="margin-left: 20px"><strong>direction: </strong>positive
<p style="margin-left: 20px"><strong>interpDirection: </strong>positive
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>variable: </strong>S
<p style="margin-left: 20px"><strong>variableDetail: </strong>Salinity LakeWater
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>ReticyprisSp (mmol/mol) [15-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>Aus_285
<p style="margin-left: 10px"><strong>variableName: </strong>ReticyprisSp
<p style="margin-left: 10px"><strong>units: </strong>mmol/mol
<p style="margin-left: 10px"><strong>description: </strong>Calculated Sr/Ca ratio of water from measured Sr/Ca of ostracod test
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>basis: </strong>Relationship established by: Chivas AR, De Deckker P and Shelley JMG (1985) Strontium content of ostracods indicates lacustrine palaeosalinity. Nature 316: 251253.
<p style="margin-left: 20px"><strong>direction: </strong>positive
<p style="margin-left: 20px"><strong>interpDirection: </strong>positive
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>variable: </strong>S
<p style="margin-left: 20px"><strong>variableDetail: </strong>Salinity LakeWater
</details>
</details>
</details>

Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### Sitemap

```{r}
  map.meta.split <- split(map.meta, map.meta$archiveType)


factpal <- colorFactor("Paired",map.meta$archiveType)
buff <- 15
l <- leaflet() %>% 
  addTiles() %>% 
  fitBounds(map.meta$lon[i]-buff,map.meta$lat[i]-buff,map.meta$lon[i]+buff,map.meta$lat[i]+buff)
  

  
  
names(map.meta.split) %>%
  purrr::walk( function(df) {
    l <<- l %>%
      addMarkers(data=map.meta.split[[df]],
                 lng=~lon, lat=~lat,
                 label=~as.character(archiveType),
                 popup=~paste(str_c('Dataset: <a href="',link,'">',dataSetName,'</a>'),
                                 # str_c("Elevation: ",elev),
                                  str_c("Archive Type: ",archiveType),
                                  sep = "<br>"),
                 group = df,
                 clusterOptions = markerClusterOptions(removeOutsideVisibleBounds = F),
                 labelOptions = labelOptions(noHide = F,
                                             direction = 'auto'))
  })

l %>%
  addLayersControl(position = "bottomleft",
    overlayGroups = names(map.meta.split),
    options = layersControlOptions(collapsed = FALSE,
                                   opacity = 0.8)
  )
```

### Search the LiPDverse (Beta! doesn't work well yet)
```{r}
#Add google search bar
htmltools::includeHTML("../../googleSearchChunk.html")
```


Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### MS (cgs) [1-1]
```{r}
plotCol(thisTS,ind = 1)
```

### density (g/cm3) [2-1]
```{r}
plotCol(thisTS,ind = 4)
```

### Laminae (missing) [3-1]
```{r}
plotCol(thisTS,ind = 11)
```

### depth.top (cm) [3-1]
```{r}
plotCol(thisTS,ind = 7)
```

### depth.bottom (cm) [3-1]
```{r}
plotCol(thisTS,ind = 10)
```

### depth.top (cm) [4-1]
```{r}
plotCol(thisTS,ind = 12)
```

### depth.bottom (cm) [4-1]
```{r}
plotCol(thisTS,ind = 15)
```

### waterContent (percent) [4-1]
```{r}
plotCol(thisTS,ind = 16)
```

### LOI (percent) [4-1]
```{r}
plotCol(thisTS,ind = 17)
```

### depth.lake (m) [5-1]
```{r}
plotCol(thisTS,ind = 18)
```

### sedimentWeight (percent) [5-1]
```{r}
plotCol(thisTS,ind = 21)
```

### sedimentWeight (percent) [6-1]
```{r}
plotCol(thisTS,ind = 26)
```

### depth.lake (m) [6-1]
```{r}
plotCol(thisTS,ind = 27)
```

### depth.top (cm) [6-1]
```{r}
plotCol(thisTS,ind = 22)
```

### depth.bottom (cm) [6-1]
```{r}
plotCol(thisTS,ind = 25)
```

### CaCO3 (percent) [7-1]
```{r}
plotCol(thisTS,ind = 28)
```

### CaCO3 (percent) [8-1]
```{r}
plotCol(thisTS,ind = 35)
```

### depth.top (cm) [8-1]
```{r}
plotCol(thisTS,ind = 31)
```

### depth.bottom (cm) [8-1]
```{r}
plotCol(thisTS,ind = 34)
```

### CaCO3 (percent) [9-1]
```{r}
plotCol(thisTS,ind = 36)
```

### Laminae (missing) [10-1]
```{r}
plotCol(thisTS,ind = 39)
```

### waterContent (percent) [11-1]
```{r}
plotCol(thisTS,ind = 42)
```

### MS (cgs) [12-1]
```{r}
plotCol(thisTS,ind = 45)
```

### density (g/cm3) [13-1]
```{r}
plotCol(thisTS,ind = 48)
```

### TDS (mg/L) [14-1]
```{r}
plotCol(thisTS,ind = 57)
```

### DiacyprisCompacta (mmol/mol) [14-1]
```{r}
plotCol(thisTS,ind = 60)
```

### MytilocyprisPraenuncia (mmol/mol) [14-1]
```{r}
plotCol(thisTS,ind = 61)
```

### depth.top (cm) [14-1]
```{r}
plotCol(thisTS,ind = 51)
```

### depth.bottom (cm) [14-1]
```{r}
plotCol(thisTS,ind = 54)
```

### AustralocyprisRobusta (missing) [14-1]
```{r}
plotCol(thisTS,ind = 55)
```

### ReticyprisHerbstii (missing) [14-1]
```{r}
plotCol(thisTS,ind = 56)
```

### SE (mg/L) [14-1]
```{r}
plotCol(thisTS,ind = 58)
```

### Sr/Ca (mmol/mol) [14-1]
```{r}
plotCol(thisTS,ind = 59)
```

### AustralocyprisRobusta (mmol/mol) [15-1]
```{r}
plotCol(thisTS,ind = 62)
```

### ReticyprisSp (mmol/mol) [15-1]
```{r}
plotCol(thisTS,ind = 65)
```
