---
title: "DSDP480.Barron.2004"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
    theme: bootstrap
    source_code: embed
    orientation: rows
---

```{r setup, include = FALSE}
library(flexdashboard)
library(maptools)
library(tidyverse)
library(purrr)
library(leaflet)
library(plotly)
library(lipdR)
library(dygraphs)
library(geoChronR)
library(lipdverseR)
#read functions
load("../../temp.Rdata")
load("../../chronTemp.Rdata")


#remove columns we don't want to plot
varNames <- sapply(TS, "[[","paleoData_variableName")

# good <- which(!(varNames %in% c("year","depth","age")))
# TS <- TS[good]


#All datasets
dsn <- sapply(TS,"[[","dataSetName")
ui <- which(!duplicated(dsn))
udsn <- dsn[ui]
lat <- as.numeric(sapply(TS,"[[","geo_latitude")[ui])
lon <- as.numeric(sapply(TS,"[[","geo_longitude")[ui])
#elev <- sapply(TS,"[[","geo_elevation")[ui]
archiveType <- sapply(TS,"[[","archiveType")[ui]
link <- paste0(udsn,".html") %>% 
  str_replace_all("'","_")

#Organize metadata for map
map.meta <- data.frame(dataSetName = udsn, #datasetname
                       lat = lat,#lat
                       lon = lon,#lon
                      # elev = elev,#elevation
                       archiveType = factor(archiveType),#archiveType
                       link = link)#Link


#set index number

i = 172
thisTS <- TS[which(udsn[i] == dsn)]
```
#DSDP480.Barron.2004

Metadata {.sidebar}
-------------------------------------
[Download LiPD file](DSDP480.Barron.2004.lpd)
            

[Edit LiPD file](http://lipd.net/playground?source=http://lipdverse.org/globalHolocene/0_25_5/DSDP480.Barron.2004.lpd)
            

[Download paleoData only (csv)](DSDP480.Barron.2004.csv)
            

[Download chronData only (csv)](DSDP480.Barron.2004-chron.csv)
            

[Report an issue (include dataset name)](https://github.com/nickmckay/LiPDverse/issues)

<details open style="margin-left: 0px">
<summary>root</summary>
<p style="margin-left: 0px"><strong>archiveType: </strong>MarineSediment
<p style="margin-left: 0px"><strong>originalDataURL: </strong>https://www.ncdc.noaa.gov/paleo-search/study/5855
<p style="margin-left: 0px"><strong>lipdVersion: </strong>1.3
</details>
<details>
<summary>pub</summary>
<details style="margin-left: 10px">
<summary>pub1</summary>
<p style="margin-left: 10px"><strong>author: </strong>list(list(name = "Barron, John A"), list(name = "Bukry, David"), list(name = "Bischoff, James L"))
<p style="margin-left: 10px"><strong>journal: </strong>Marine Micropaleontology
<p style="margin-left: 10px"><strong>volume: </strong>50
<p style="margin-left: 10px"><strong>pages: </strong>185-207
<p style="margin-left: 10px"><strong>title: </strong>High resolution paleoceanography of the Guaymas Basin, Gulf of California, during the past 15 000 years
</details>
<details style="margin-left: 10px">
<summary>pub2</summary>
<p style="margin-left: 10px"><strong>author: </strong>list(list(name = NA))
</details>
</details>
<details>
<summary>funding</summary>
<details style="margin-left: 10px">
<summary>funding1</summary>
<p style="margin-left: 10px"><strong>agency: </strong>Funding Agency
<p style="margin-left: 10px"><strong>grant: </strong>Grant name or number
</details>
</details>
<details open style="margin-left: 0px">
<summary>geo</summary>
<p style="margin-left: 0px"><strong>latitude: </strong>27.9
<p style="margin-left: 0px"><strong>longitude: </strong>-111.65
<p style="margin-left: 0px"><strong>elevation: </strong>-655
</details>
<details open>
<summary>PaleoData columns</summary>
<details style="margin-left: 10px">
<summary>year (AD) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB801f8b00
<p style="margin-left: 10px"><strong>variableName: </strong>year
<p style="margin-left: 10px"><strong>units: </strong>AD
<p style="margin-left: 10px"><strong>description: </strong>Year AD
</details>
<details style="margin-left: 10px">
<summary>age (BP) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBb8905979
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>BP
<p style="margin-left: 10px"><strong>description: </strong>Years before present (1950) BP
</details>
<details style="margin-left: 10px">
<summary>depth (cm) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBf85198b8
<p style="margin-left: 10px"><strong>variableName: </strong>depth
<p style="margin-left: 10px"><strong>units: </strong>cm
<p style="margin-left: 10px"><strong>description: </strong>depth
</details>
<details style="margin-left: 10px">
<summary>Actinocyclus_curvatulus (missing) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD2475c83d
<p style="margin-left: 10px"><strong>variableName: </strong>Actinocyclus_curvatulus
<p style="margin-left: 10px"><strong>units: </strong>missing
<p style="margin-left: 10px"><strong>description: </strong>cold water
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>direction: </strong>negative
<p style="margin-left: 20px"><strong>interpDirection: </strong>negative
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>variable: </strong>T
<p style="margin-left: 20px"><strong>variableDetail: </strong>upwelling
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>Roperia_tesselata (missing) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD09a8f867
<p style="margin-left: 10px"><strong>variableName: </strong>Roperia_tesselata
<p style="margin-left: 10px"><strong>units: </strong>missing
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>direction: </strong>positive
<p style="margin-left: 20px"><strong>interpDirection: </strong>positive
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>seasonality: </strong>winter
<p style="margin-left: 20px"><strong>variable: </strong>upwelling
<p style="margin-left: 20px"><strong>variableDetail: </strong>upwelling
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>CAL (missing) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDc50b4e08
<p style="margin-left: 10px"><strong>variableName: </strong>CAL
<p style="margin-left: 10px"><strong>units: </strong>missing
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Actinocyclus_octonarius (missing) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD079db6d8
<p style="margin-left: 10px"><strong>variableName: </strong>Actinocyclus_octonarius
<p style="margin-left: 10px"><strong>units: </strong>missing
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Actinoptychus_spp. (missing) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD2714616c
<p style="margin-left: 10px"><strong>variableName: </strong>Actinoptychus_spp.
<p style="margin-left: 10px"><strong>units: </strong>missing
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Azpeitia_nodulifer (missing) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDee5ae93d
<p style="margin-left: 10px"><strong>variableName: </strong>Azpeitia_nodulifer
<p style="margin-left: 10px"><strong>units: </strong>missing
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Coscinodiscus_spp. (missing) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDf547b905
<p style="margin-left: 10px"><strong>variableName: </strong>Coscinodiscus_spp.
<p style="margin-left: 10px"><strong>units: </strong>missing
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Cyclotella_spp. (missing) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD22b774d2
<p style="margin-left: 10px"><strong>variableName: </strong>Cyclotella_spp.
<p style="margin-left: 10px"><strong>units: </strong>missing
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Stephanopyxis_spp. (missing) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD1d428358
<p style="margin-left: 10px"><strong>variableName: </strong>Stephanopyxis_spp.
<p style="margin-left: 10px"><strong>units: </strong>missing
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Number_counted (missing) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDdd024e46
<p style="margin-left: 10px"><strong>variableName: </strong>Number_counted
<p style="margin-left: 10px"><strong>units: </strong>missing
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>year (AD) [2-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBfe97db44
<p style="margin-left: 10px"><strong>variableName: </strong>year
<p style="margin-left: 10px"><strong>units: </strong>AD
<p style="margin-left: 10px"><strong>description: </strong>Year AD
</details>
<details style="margin-left: 10px">
<summary>age (BP) [2-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB02bdf54d
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>BP
<p style="margin-left: 10px"><strong>description: </strong>Years before present (1950) BP
</details>
<details style="margin-left: 10px">
<summary>depth (cm) [2-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB05e8377e
<p style="margin-left: 10px"><strong>variableName: </strong>depth
<p style="margin-left: 10px"><strong>units: </strong>cm
<p style="margin-left: 10px"><strong>description: </strong>depth
</details>
<details style="margin-left: 10px">
<summary>CAL (missing) [2-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDd4b2585a
<p style="margin-left: 10px"><strong>variableName: </strong>CAL
<p style="margin-left: 10px"><strong>units: </strong>missing
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Dictyocha_acueata (missing) [2-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDdedcba9a
<p style="margin-left: 10px"><strong>variableName: </strong>Dictyocha_acueata
<p style="margin-left: 10px"><strong>units: </strong>missing
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>D_aff_D_aculeata (missing) [2-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD57eac7f0
<p style="margin-left: 10px"><strong>variableName: </strong>D_aff_D_aculeata
<p style="margin-left: 10px"><strong>units: </strong>missing
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>D_aspinosa (missing) [2-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD84323569
<p style="margin-left: 10px"><strong>variableName: </strong>D_aspinosa
<p style="margin-left: 10px"><strong>units: </strong>missing
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>D_calida (missing) [2-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD67b4a07c
<p style="margin-left: 10px"><strong>variableName: </strong>D_calida
<p style="margin-left: 10px"><strong>units: </strong>missing
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>D_calida_ampliata (missing) [2-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD79bab6ef
<p style="margin-left: 10px"><strong>variableName: </strong>D_calida_ampliata
<p style="margin-left: 10px"><strong>units: </strong>missing
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>D_perlaevis (missing) [2-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD07be0e72
<p style="margin-left: 10px"><strong>variableName: </strong>D_perlaevis
<p style="margin-left: 10px"><strong>units: </strong>missing
<p style="margin-left: 10px"><strong>description: </strong>oligotrophic, warm
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>D_stapedia (missing) [2-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD54035ff8
<p style="margin-left: 10px"><strong>variableName: </strong>D_stapedia
<p style="margin-left: 10px"><strong>units: </strong>missing
<p style="margin-left: 10px"><strong>description: </strong>subtropical
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Ds_speculum (missing) [2-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD9bff0e41
<p style="margin-left: 10px"><strong>variableName: </strong>Ds_speculum
<p style="margin-left: 10px"><strong>units: </strong>missing
<p style="margin-left: 10px"><strong>description: </strong>cold water, california current
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Octactis_pulchra_(lrg) (missing) [2-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDee4b6a0d
<p style="margin-left: 10px"><strong>variableName: </strong>Octactis_pulchra_(lrg)
<p style="margin-left: 10px"><strong>units: </strong>missing
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>O_pulchra_(med) (missing) [2-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDc4d52a33
<p style="margin-left: 10px"><strong>variableName: </strong>O_pulchra_(med)
<p style="margin-left: 10px"><strong>units: </strong>missing
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>O_pulchra_(small) (missing) [2-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD6b75a5f1
<p style="margin-left: 10px"><strong>variableName: </strong>O_pulchra_(small)
<p style="margin-left: 10px"><strong>units: </strong>missing
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>O_pulchra_(thick) (missing) [2-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDee007ba7
<p style="margin-left: 10px"><strong>variableName: </strong>O_pulchra_(thick)
<p style="margin-left: 10px"><strong>units: </strong>missing
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Numbe_counted (missing) [2-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD57ee54a5
<p style="margin-left: 10px"><strong>variableName: </strong>Numbe_counted
<p style="margin-left: 10px"><strong>units: </strong>missing
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>year (AD) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBf1668c08
<p style="margin-left: 10px"><strong>variableName: </strong>year
<p style="margin-left: 10px"><strong>units: </strong>AD
<p style="margin-left: 10px"><strong>description: </strong>Year AD
</details>
<details style="margin-left: 10px">
<summary>age (BP) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB01528b9d
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>BP
<p style="margin-left: 10px"><strong>description: </strong>Years before present (1950) BP
</details>
<details style="margin-left: 10px">
<summary>depth (cm) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB77650183
<p style="margin-left: 10px"><strong>variableName: </strong>depth
<p style="margin-left: 10px"><strong>units: </strong>cm
<p style="margin-left: 10px"><strong>description: </strong>depth
</details>
<details style="margin-left: 10px">
<summary>BSi (percent) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD3a4d6b46
<p style="margin-left: 10px"><strong>variableName: </strong>BSi
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>description: </strong>production
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>direction: </strong>positive
<p style="margin-left: 20px"><strong>interpDirection: </strong>positive
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>seasonality: </strong>winter
<p style="margin-left: 20px"><strong>variable: </strong>upwelling
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>CAL (missing) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDdb35ffcd
<p style="margin-left: 10px"><strong>variableName: </strong>CAL
<p style="margin-left: 10px"><strong>units: </strong>missing
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Al (percent) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD028a26ef
<p style="margin-left: 10px"><strong>variableName: </strong>Al
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Si (percent) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDb1734732
<p style="margin-left: 10px"><strong>variableName: </strong>Si
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Fe (percent) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD73f66f5e
<p style="margin-left: 10px"><strong>variableName: </strong>Fe
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>%Ti (percent) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD60b72d70
<p style="margin-left: 10px"><strong>variableName: </strong>%Ti
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>%Mg (percent) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDe6dd0dd1
<p style="margin-left: 10px"><strong>variableName: </strong>%Mg
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>%K (percent) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDf7e74c93
<p style="margin-left: 10px"><strong>variableName: </strong>%K
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>%P (percent) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD61f8f3a7
<p style="margin-left: 10px"><strong>variableName: </strong>%P
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Ba (ppm) (missing) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD4d416388
<p style="margin-left: 10px"><strong>variableName: </strong>Ba (ppm)
<p style="margin-left: 10px"><strong>units: </strong>missing
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Sr (ppm) (missing) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDeff87f79
<p style="margin-left: 10px"><strong>variableName: </strong>Sr (ppm)
<p style="margin-left: 10px"><strong>units: </strong>missing
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>% Total C (percent) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD25b7279a
<p style="margin-left: 10px"><strong>variableName: </strong>% Total C
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>TIC (percent) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDa42f7341
<p style="margin-left: 10px"><strong>variableName: </strong>TIC
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>TOC (percent) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDaf2ace86
<p style="margin-left: 10px"><strong>variableName: </strong>TOC
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>CaCO3 (percent) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDb7754b0a
<p style="margin-left: 10px"><strong>variableName: </strong>CaCO3
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>description: </strong>tropical, oligotrophic
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details>
<summary>ChronData columns</summary>
<details style="margin-left: 10px">
<summary>depth (cm)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD1cdde6e8
<p style="margin-left: 10px"><strong>variableName: </strong>depth
<p style="margin-left: 10px"><strong>units: </strong>cm
</details>
<details style="margin-left: 10px">
<summary>age (yr BP)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD0f7465c0
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>yr BP
</details>
<details style="margin-left: 10px">
<summary>Reference (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD47622b4d
<p style="margin-left: 10px"><strong>variableName: </strong>Reference
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>core (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD2a4a57b6
<p style="margin-left: 10px"><strong>variableName: </strong>core
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>material (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD5bc7369c
<p style="margin-left: 10px"><strong>variableName: </strong>material
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>error (yr)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDb9ad1a5b
<p style="margin-left: 10px"><strong>variableName: </strong>error
<p style="margin-left: 10px"><strong>units: </strong>yr
</details>
<details style="margin-left: 10px">
<summary>14C age_oldest (yrs before 1950 AD) (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD2b06dc5a
<p style="margin-left: 10px"><strong>variableName: </strong>14C age_oldest (yrs before 1950 AD)
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>calibrated (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD679f1636
<p style="margin-left: 10px"><strong>variableName: </strong>calibrated
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>youngest_calibrated_age (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD6c7b873a
<p style="margin-left: 10px"><strong>variableName: </strong>youngest_calibrated_age
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>oldest_calibrated_age (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD5afa92d8
<p style="margin-left: 10px"><strong>variableName: </strong>oldest_calibrated_age
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>Reservoir_Correction/R (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD43ecc255
<p style="margin-left: 10px"><strong>variableName: </strong>Reservoir_Correction/R
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>Calibration_used (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD3f345677
<p style="margin-left: 10px"><strong>variableName: </strong>Calibration_used
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>Comments (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD1867b723
<p style="margin-left: 10px"><strong>variableName: </strong>Comments
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>

Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### Sitemap

```{r}
  map.meta.split <- split(map.meta, map.meta$archiveType)


factpal <- colorFactor("Paired",map.meta$archiveType)
buff <- 15
l <- leaflet() %>% 
  addTiles() %>% 
  fitBounds(map.meta$lon[i]-buff,map.meta$lat[i]-buff,map.meta$lon[i]+buff,map.meta$lat[i]+buff)
  

  
  
names(map.meta.split) %>%
  purrr::walk( function(df) {
    l <<- l %>%
      addMarkers(data=map.meta.split[[df]],
                 lng=~lon, lat=~lat,
                 label=~as.character(archiveType),
                 popup=~paste(str_c('Dataset: <a href="',link,'">',dataSetName,'</a>'),
                                 # str_c("Elevation: ",elev),
                                  str_c("Archive Type: ",archiveType),
                                  sep = "<br>"),
                 group = df,
                 clusterOptions = markerClusterOptions(removeOutsideVisibleBounds = F),
                 labelOptions = labelOptions(noHide = F,
                                             direction = 'auto'))
  })

l %>%
  addLayersControl(position = "bottomleft",
    overlayGroups = names(map.meta.split),
    options = layersControlOptions(collapsed = FALSE,
                                   opacity = 0.8)
  )
```

### Search the LiPDverse (Beta! doesn't work well yet)
```{r}
#Add google search bar
htmltools::includeHTML("../../googleSearchChunk.html")
```


Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### Actinocyclus_curvatulus (missing) [1-1]
```{r}
plotCol(thisTS,ind = 5)
```

### Roperia_tesselata (missing) [1-1]
```{r}
plotCol(thisTS,ind = 11)
```

### CAL (missing) [1-1]
```{r}
plotCol(thisTS,ind = 1)
```

### Actinocyclus_octonarius (missing) [1-1]
```{r}
plotCol(thisTS,ind = 6)
```

### Actinoptychus_spp. (missing) [1-1]
```{r}
plotCol(thisTS,ind = 7)
```

### Azpeitia_nodulifer (missing) [1-1]
```{r}
plotCol(thisTS,ind = 8)
```

### Coscinodiscus_spp. (missing) [1-1]
```{r}
plotCol(thisTS,ind = 9)
```

### Cyclotella_spp. (missing) [1-1]
```{r}
plotCol(thisTS,ind = 10)
```

### Stephanopyxis_spp. (missing) [1-1]
```{r}
plotCol(thisTS,ind = 12)
```

### Number_counted (missing) [1-1]
```{r}
plotCol(thisTS,ind = 13)
```

### CAL (missing) [2-1]
```{r}
plotCol(thisTS,ind = 14)
```

### Dictyocha_acueata (missing) [2-1]
```{r}
plotCol(thisTS,ind = 18)
```

### D_aff_D_aculeata (missing) [2-1]
```{r}
plotCol(thisTS,ind = 19)
```

### D_aspinosa (missing) [2-1]
```{r}
plotCol(thisTS,ind = 20)
```

### D_calida (missing) [2-1]
```{r}
plotCol(thisTS,ind = 21)
```

### D_calida_ampliata (missing) [2-1]
```{r}
plotCol(thisTS,ind = 22)
```

### D_perlaevis (missing) [2-1]
```{r}
plotCol(thisTS,ind = 23)
```

### D_stapedia (missing) [2-1]
```{r}
plotCol(thisTS,ind = 24)
```

### Ds_speculum (missing) [2-1]
```{r}
plotCol(thisTS,ind = 25)
```

### Octactis_pulchra_(lrg) (missing) [2-1]
```{r}
plotCol(thisTS,ind = 26)
```

### O_pulchra_(med) (missing) [2-1]
```{r}
plotCol(thisTS,ind = 27)
```

### O_pulchra_(small) (missing) [2-1]
```{r}
plotCol(thisTS,ind = 28)
```

### O_pulchra_(thick) (missing) [2-1]
```{r}
plotCol(thisTS,ind = 29)
```

### Numbe_counted (missing) [2-1]
```{r}
plotCol(thisTS,ind = 30)
```

### BSi (percent) [3-1]
```{r}
plotCol(thisTS,ind = 48)
```

### CAL (missing) [3-1]
```{r}
plotCol(thisTS,ind = 31)
```

### Al (percent) [3-1]
```{r}
plotCol(thisTS,ind = 35)
```

### Si (percent) [3-1]
```{r}
plotCol(thisTS,ind = 36)
```

### Fe (percent) [3-1]
```{r}
plotCol(thisTS,ind = 37)
```

### %Ti (percent) [3-1]
```{r}
plotCol(thisTS,ind = 38)
```

### %Mg (percent) [3-1]
```{r}
plotCol(thisTS,ind = 39)
```

### %K (percent) [3-1]
```{r}
plotCol(thisTS,ind = 40)
```

### %P (percent) [3-1]
```{r}
plotCol(thisTS,ind = 41)
```

### Ba (ppm) (missing) [3-1]
```{r}
plotCol(thisTS,ind = 42)
```

### Sr (ppm) (missing) [3-1]
```{r}
plotCol(thisTS,ind = 43)
```

### % Total C (percent) [3-1]
```{r}
plotCol(thisTS,ind = 44)
```

### TIC (percent) [3-1]
```{r}
plotCol(thisTS,ind = 45)
```

### TOC (percent) [3-1]
```{r}
plotCol(thisTS,ind = 46)
```

### CaCO3 (percent) [3-1]
```{r}
plotCol(thisTS,ind = 47)
```

Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### depth (cm)
```{r}
plotCol(chronTS,ind = 4)
```

### age (yr BP)
```{r}
plotCol(chronTS,ind = 5)
```

### Reference (unitless)
```{r}
plotCol(chronTS,ind = 1)
```

### core (unitless)
```{r}
plotCol(chronTS,ind = 2)
```

### material (unitless)
```{r}
plotCol(chronTS,ind = 3)
```

### error (yr)
```{r}
plotCol(chronTS,ind = 6)
```

### 14C age_oldest (yrs before 1950 AD) (unitless)
```{r}
plotCol(chronTS,ind = 7)
```

### calibrated (unitless)
```{r}
plotCol(chronTS,ind = 8)
```

### youngest_calibrated_age (unitless)
```{r}
plotCol(chronTS,ind = 9)
```

### oldest_calibrated_age (unitless)
```{r}
plotCol(chronTS,ind = 10)
```

### Reservoir_Correction/R (unitless)
```{r}
plotCol(chronTS,ind = 11)
```

### Calibration_used (unitless)
```{r}
plotCol(chronTS,ind = 12)
```

### Comments (unitless)
```{r}
plotCol(chronTS,ind = 13)
```
