---
title: "Heshang.Wang.2018"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
    theme: bootstrap
    source_code: embed
    orientation: rows
---

```{r setup, include = FALSE}
library(flexdashboard)
library(maptools)
library(tidyverse)
library(purrr)
library(leaflet)
library(plotly)
library(lipdR)
library(dygraphs)
library(geoChronR)
library(lipdverseR)
#read functions
load("../../temp.Rdata")
load("../../chronTemp.Rdata")


#remove columns we don't want to plot
varNames <- sapply(TS, "[[","paleoData_variableName")

# good <- which(!(varNames %in% c("year","depth","age")))
# TS <- TS[good]


#All datasets
dsn <- sapply(TS,"[[","dataSetName")
ui <- which(!duplicated(dsn))
udsn <- dsn[ui]
lat <- as.numeric(sapply(TS,"[[","geo_latitude")[ui])
lon <- as.numeric(sapply(TS,"[[","geo_longitude")[ui])
#elev <- sapply(TS,"[[","geo_elevation")[ui]
archiveType <- sapply(TS,"[[","archiveType")[ui]
link <- paste0(udsn,".html") %>% 
  str_replace_all("'","_")

#Organize metadata for map
map.meta <- data.frame(dataSetName = udsn, #datasetname
                       lat = lat,#lat
                       lon = lon,#lon
                      # elev = elev,#elevation
                       archiveType = factor(archiveType),#archiveType
                       link = link)#Link


#set index number

i = 303
thisTS <- TS[which(udsn[i] == dsn)]
```
#Heshang.Wang.2018

Metadata {.sidebar}
-------------------------------------
[Download LiPD file](Heshang.Wang.2018.lpd)
            

[Edit LiPD file](http://lipd.net/playground?source=http://lipdverse.org/globalHolocene/0_25_5/Heshang.Wang.2018.lpd)
            

[Download paleoData only (csv)](Heshang.Wang.2018.csv)
            

[Download chronData only (csv)](Heshang.Wang.2018-chron.csv)
            

[Report an issue (include dataset name)](https://github.com/nickmckay/LiPDverse/issues)

<details open style="margin-left: 0px">
<summary>root</summary>
<p style="margin-left: 0px"><strong>archiveType: </strong>Speleothem
<p style="margin-left: 0px"><strong>lipdVersion: </strong>1.3
</details>
<details>
<summary>pub</summary>
<details style="margin-left: 10px">
<summary>pub1</summary>
<p style="margin-left: 10px"><strong>author: </strong>list(list(name = "Wang, Canfa"), list(name = "Bendle, James A."), list(name = "Zhang, Hongbin"), list(name = "Yang, Yi"), list(name = "Liu, Deng"), list(name = "Huang, Junhua"), list(name = "Cui, Jingwei"), list(name = "Xie, Shucheng"))
<p style="margin-left: 10px"><strong>journal: </strong>Quaternary Science Reviews
<p style="margin-left: 10px"><strong>volume: </strong>192
<p style="margin-left: 10px"><strong>pages: </strong>97-105
<p style="margin-left: 10px"><strong>title: </strong>Holocene temperature and hydrological changes reconstructed by bacterial 3-hydroxy fatty acids in a stalagmite from central China
</details>
<details style="margin-left: 10px">
<summary>pub2</summary>
<p style="margin-left: 10px"><strong>author: </strong>list(list(name = NA))
</details>
</details>
<details open style="margin-left: 0px">
<summary>geo</summary>
<p style="margin-left: 0px"><strong>latitude: </strong>30.45
<p style="margin-left: 0px"><strong>longitude: </strong>110.4167
<p style="margin-left: 0px"><strong>elevation: </strong>294
<p style="margin-left: 0px"><strong>siteName: </strong>Heshang Cave
</details>
<details open>
<summary>PaleoData columns</summary>
<details style="margin-left: 10px">
<summary>age (BP)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB5967da4c
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>BP
</details>
<details style="margin-left: 10px">
<summary>RAN15MAAT (degC)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB4f8fa23d
<p style="margin-left: 10px"><strong>variableName: </strong>RAN15MAAT
<p style="margin-left: 10px"><strong>units: </strong>degC
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>TRUE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>direction: </strong>positive
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>variable: </strong>T
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>sampleID (missing)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBd28360dd
<p style="margin-left: 10px"><strong>variableName: </strong>sampleID
<p style="margin-left: 10px"><strong>units: </strong>missing
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>RAN15 (missing)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB7baf4af4
<p style="margin-left: 10px"><strong>variableName: </strong>RAN15
<p style="margin-left: 10px"><strong>units: </strong>missing
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details>
<summary>ChronData columns</summary>
<details style="margin-left: 10px">
<summary>depth (cm)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBbae766cc
<p style="margin-left: 10px"><strong>variableName: </strong>depth
<p style="margin-left: 10px"><strong>units: </strong>cm
</details>
<details style="margin-left: 10px">
<summary>238Uconc (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB9793a220
<p style="margin-left: 10px"><strong>variableName: </strong>238Uconc
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>238Uconc_error (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBccf1309b
<p style="margin-left: 10px"><strong>variableName: </strong>238Uconc_error
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>232Thconc (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB8a456381
<p style="margin-left: 10px"><strong>variableName: </strong>232Thconc
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>232Thconc_error (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB12a56bfc
<p style="margin-left: 10px"><strong>variableName: </strong>232Thconc_error
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>d234Ua (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB7777c230
<p style="margin-left: 10px"><strong>variableName: </strong>d234Ua
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>d234Ua_error (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB33d7101d
<p style="margin-left: 10px"><strong>variableName: </strong>d234Ua_error
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>(230Th/232Th)b (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB0db3f7f0
<p style="margin-left: 10px"><strong>variableName: </strong>(230Th/232Th)b
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>(230Th/232Th)b_error (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB5fb9cffd
<p style="margin-left: 10px"><strong>variableName: </strong>(230Th/232Th)b_error
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>(230Th/238Th)b (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB6ee44518
<p style="margin-left: 10px"><strong>variableName: </strong>(230Th/238Th)b
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>(230Th/238Th)b_error (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB7f58c492
<p style="margin-left: 10px"><strong>variableName: </strong>(230Th/238Th)b_error
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>Age(raw)c (yr bp)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBbb21c8e4
<p style="margin-left: 10px"><strong>variableName: </strong>Age(raw)c
<p style="margin-left: 10px"><strong>units: </strong>yr bp
</details>
<details style="margin-left: 10px">
<summary>Age(raw)c_error (yr)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBd88943c0
<p style="margin-left: 10px"><strong>variableName: </strong>Age(raw)c_error
<p style="margin-left: 10px"><strong>units: </strong>yr
</details>
<details style="margin-left: 10px">
<summary>Age(corr)d (yr bp)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB32bc03b9
<p style="margin-left: 10px"><strong>variableName: </strong>Age(corr)d
<p style="margin-left: 10px"><strong>units: </strong>yr bp
</details>
<details style="margin-left: 10px">
<summary>Age(corr)d_error (yr)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB98c7f47f
<p style="margin-left: 10px"><strong>variableName: </strong>Age(corr)d_error
<p style="margin-left: 10px"><strong>units: </strong>yr
</details>

Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### Sitemap

```{r}
  map.meta.split <- split(map.meta, map.meta$archiveType)


factpal <- colorFactor("Paired",map.meta$archiveType)
buff <- 15
l <- leaflet() %>% 
  addTiles() %>% 
  fitBounds(map.meta$lon[i]-buff,map.meta$lat[i]-buff,map.meta$lon[i]+buff,map.meta$lat[i]+buff)
  

  
  
names(map.meta.split) %>%
  purrr::walk( function(df) {
    l <<- l %>%
      addMarkers(data=map.meta.split[[df]],
                 lng=~lon, lat=~lat,
                 label=~as.character(archiveType),
                 popup=~paste(str_c('Dataset: <a href="',link,'">',dataSetName,'</a>'),
                                 # str_c("Elevation: ",elev),
                                  str_c("Archive Type: ",archiveType),
                                  sep = "<br>"),
                 group = df,
                 clusterOptions = markerClusterOptions(removeOutsideVisibleBounds = F),
                 labelOptions = labelOptions(noHide = F,
                                             direction = 'auto'))
  })

l %>%
  addLayersControl(position = "bottomleft",
    overlayGroups = names(map.meta.split),
    options = layersControlOptions(collapsed = FALSE,
                                   opacity = 0.8)
  )
```

### Search the LiPDverse (Beta! doesn't work well yet)
```{r}
#Add google search bar
htmltools::includeHTML("../../googleSearchChunk.html")
```


Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### RAN15MAAT (degC)
```{r}
plotCol(thisTS,ind = 4)
```

### sampleID (missing)
```{r}
plotCol(thisTS,ind = 1)
```

### RAN15 (missing)
```{r}
plotCol(thisTS,ind = 3)
```

Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### depth (cm)
```{r}
plotCol(chronTS,ind = 1)
```

### 238Uconc (unitless)
```{r}
plotCol(chronTS,ind = 2)
```

### 238Uconc_error (unitless)
```{r}
plotCol(chronTS,ind = 3)
```

### 232Thconc (unitless)
```{r}
plotCol(chronTS,ind = 4)
```

### 232Thconc_error (unitless)
```{r}
plotCol(chronTS,ind = 5)
```

### d234Ua (unitless)
```{r}
plotCol(chronTS,ind = 6)
```

### d234Ua_error (unitless)
```{r}
plotCol(chronTS,ind = 7)
```

### (230Th/232Th)b (unitless)
```{r}
plotCol(chronTS,ind = 8)
```

### (230Th/232Th)b_error (unitless)
```{r}
plotCol(chronTS,ind = 9)
```

### (230Th/238Th)b (unitless)
```{r}
plotCol(chronTS,ind = 10)
```

### (230Th/238Th)b_error (unitless)
```{r}
plotCol(chronTS,ind = 11)
```

### Age(raw)c (yr bp)
```{r}
plotCol(chronTS,ind = 12)
```

### Age(raw)c_error (yr)
```{r}
plotCol(chronTS,ind = 13)
```

### Age(corr)d (yr bp)
```{r}
plotCol(chronTS,ind = 14)
```

### Age(corr)d_error (yr)
```{r}
plotCol(chronTS,ind = 15)
```
