---
title: "KinderlinskayaCave.Baker.2017"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
    theme: bootstrap
    source_code: embed
    orientation: rows
---

```{r setup, include = FALSE}
library(flexdashboard)
library(maptools)
library(tidyverse)
library(purrr)
library(leaflet)
library(plotly)
library(lipdR)
library(dygraphs)
library(geoChronR)
library(lipdverseR)
#read functions
load("../../temp.Rdata")
load("../../chronTemp.Rdata")


#remove columns we don't want to plot
varNames <- sapply(TS, "[[","paleoData_variableName")

# good <- which(!(varNames %in% c("year","depth","age")))
# TS <- TS[good]


#All datasets
dsn <- sapply(TS,"[[","dataSetName")
ui <- which(!duplicated(dsn))
udsn <- dsn[ui]
lat <- as.numeric(sapply(TS,"[[","geo_latitude")[ui])
lon <- as.numeric(sapply(TS,"[[","geo_longitude")[ui])
#elev <- sapply(TS,"[[","geo_elevation")[ui]
archiveType <- sapply(TS,"[[","archiveType")[ui]
link <- paste0(udsn,".html") %>% 
  str_replace_all("'","_")

#Organize metadata for map
map.meta <- data.frame(dataSetName = udsn, #datasetname
                       lat = lat,#lat
                       lon = lon,#lon
                      # elev = elev,#elevation
                       archiveType = factor(archiveType),#archiveType
                       link = link)#Link


#set index number

i = 383
thisTS <- TS[which(udsn[i] == dsn)]
```
#KinderlinskayaCave.Baker.2017

Metadata {.sidebar}
-------------------------------------
[Download LiPD file](KinderlinskayaCave.Baker.2017.lpd)
            

[Edit LiPD file](http://lipd.net/playground?source=http://lipdverse.org/globalHolocene/0_25_5/KinderlinskayaCave.Baker.2017.lpd)
            

[Download paleoData only (csv)](KinderlinskayaCave.Baker.2017.csv)
            

[Download chronData only (csv)](KinderlinskayaCave.Baker.2017-chron.csv)
            

[Report an issue (include dataset name)](https://github.com/nickmckay/LiPDverse/issues)

<details open style="margin-left: 0px">
<summary>root</summary>
<p style="margin-left: 0px"><strong>archiveType: </strong>Speleothem
<p style="margin-left: 0px"><strong>lipdVersion: </strong>1.3
</details>
<details>
<summary>pub</summary>
<details style="margin-left: 10px">
<summary>pub1</summary>
<p style="margin-left: 10px"><strong>author: </strong>list(list(name = "Baker, Jonathan L."), list(name = "Lachniet, Matthew S."), list(name = "Chervyatsova, Olga"), list(name = "Asmerom, Yemane"), list(name = "Polyak, Victor J."))
<p style="margin-left: 10px"><strong>journal: </strong>Nature Geoscience
<p style="margin-left: 10px"><strong>volume: </strong>10
<p style="margin-left: 10px"><strong>pages: </strong>430-435
<p style="margin-left: 10px"><strong>title: </strong>Holocene warming in western continental Eurasia driven by glacial retreat and greenhouse forcing
</details>
<details style="margin-left: 10px">
<summary>pub2</summary>
<p style="margin-left: 10px"><strong>author: </strong>list(list(name = NA))
</details>
</details>
<details open style="margin-left: 0px">
<summary>geo</summary>
<p style="margin-left: 0px"><strong>latitude: </strong>54.2
<p style="margin-left: 0px"><strong>longitude: </strong>56.9
<p style="margin-left: 0px"><strong>elevation: </strong>240
<p style="margin-left: 0px"><strong>siteName: </strong>Kinderlinskaya Cave
</details>
<details open>
<summary>PaleoData columns</summary>
<details style="margin-left: 10px">
<summary>age (BP) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBe4f07140
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>BP
</details>
<details style="margin-left: 10px">
<summary>d18O (permil) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB6f612252
<p style="margin-left: 10px"><strong>variableName: </strong>d18O
<p style="margin-left: 10px"><strong>units: </strong>permil
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>TRUE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>direction: </strong>positive
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>seasonality: </strong>winter
<p style="margin-left: 20px"><strong>variable: </strong>T
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>depth (mm) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB112fcdfc
<p style="margin-left: 10px"><strong>variableName: </strong>depth
<p style="margin-left: 10px"><strong>units: </strong>mm
</details>
<details style="margin-left: 10px">
<summary>age (BP) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBc9f7de7f
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>BP
</details>
<details style="margin-left: 10px">
<summary>d18O (permil) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB8bafc4b5
<p style="margin-left: 10px"><strong>variableName: </strong>d18O
<p style="margin-left: 10px"><strong>units: </strong>permil
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>d13C (permil) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBa0c476c2
<p style="margin-left: 10px"><strong>variableName: </strong>d13C
<p style="margin-left: 10px"><strong>units: </strong>permil
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>notes (missing) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB5338b0d0
<p style="margin-left: 10px"><strong>variableName: </strong>notes
<p style="margin-left: 10px"><strong>units: </strong>missing
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>depth (mm) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBc5e9c59d
<p style="margin-left: 10px"><strong>variableName: </strong>depth
<p style="margin-left: 10px"><strong>units: </strong>mm
</details>
<details style="margin-left: 10px">
<summary>age (BP) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBe61281e0
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>BP
</details>
<details style="margin-left: 10px">
<summary>d18O (permil) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB0e6e07c5
<p style="margin-left: 10px"><strong>variableName: </strong>d18O
<p style="margin-left: 10px"><strong>units: </strong>permil
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>d13C (permil) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBa98d68e2
<p style="margin-left: 10px"><strong>variableName: </strong>d13C
<p style="margin-left: 10px"><strong>units: </strong>permil
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>notes (missing) [1-3]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB367ac433
<p style="margin-left: 10px"><strong>variableName: </strong>notes
<p style="margin-left: 10px"><strong>units: </strong>missing
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details>
<summary>ChronData columns</summary>
<details style="margin-left: 10px">
<summary>depth (mm)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB05c1d91a
<p style="margin-left: 10px"><strong>variableName: </strong>depth
<p style="margin-left: 10px"><strong>units: </strong>mm
</details>
<details style="margin-left: 10px">
<summary>core (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBd7d19c42
<p style="margin-left: 10px"><strong>variableName: </strong>core
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>238U (ng/g)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB5c4c9a71
<p style="margin-left: 10px"><strong>variableName: </strong>238U
<p style="margin-left: 10px"><strong>units: </strong>ng/g
</details>
<details style="margin-left: 10px">
<summary>238U_error (ng/g) (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB46fa1e2c
<p style="margin-left: 10px"><strong>variableName: </strong>238U_error (ng/g)
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>232Th (pg/g)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB2a14544b
<p style="margin-left: 10px"><strong>variableName: </strong>232Th
<p style="margin-left: 10px"><strong>units: </strong>pg/g
</details>
<details style="margin-left: 10px">
<summary>232Th_error (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB793cd461
<p style="margin-left: 10px"><strong>variableName: </strong>232Th_error
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>230Th/232Th (ratio)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB63b0027e
<p style="margin-left: 10px"><strong>variableName: </strong>230Th/232Th
<p style="margin-left: 10px"><strong>units: </strong>ratio
</details>
<details style="margin-left: 10px">
<summary>230Th/232Th_error (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBb27d106f
<p style="margin-left: 10px"><strong>variableName: </strong>230Th/232Th_error
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>230Th/238U (ratio)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBd2be3b52
<p style="margin-left: 10px"><strong>variableName: </strong>230Th/238U
<p style="margin-left: 10px"><strong>units: </strong>ratio
</details>
<details style="margin-left: 10px">
<summary>230Th/238U_error (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBd4c638d0
<p style="margin-left: 10px"><strong>variableName: </strong>230Th/238U_error
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>d234U (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBe9f58046
<p style="margin-left: 10px"><strong>variableName: </strong>d234U
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>d234U_error (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB0e03afff
<p style="margin-left: 10px"><strong>variableName: </strong>d234U_error
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>initial_d234U (permil)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB7bc71e9c
<p style="margin-left: 10px"><strong>variableName: </strong>initial_d234U
<p style="margin-left: 10px"><strong>units: </strong>permil
</details>
<details style="margin-left: 10px">
<summary>d234U_error (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBf491d21b
<p style="margin-left: 10px"><strong>variableName: </strong>d234U_error
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>uncorrected_age (yr bp)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEBbdc0072a
<p style="margin-left: 10px"><strong>variableName: </strong>uncorrected_age
<p style="margin-left: 10px"><strong>units: </strong>yr bp
</details>
<details style="margin-left: 10px">
<summary>uncorrected_age_error (yr)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB02057d36
<p style="margin-left: 10px"><strong>variableName: </strong>uncorrected_age_error
<p style="margin-left: 10px"><strong>units: </strong>yr
</details>
<details style="margin-left: 10px">
<summary>Corrected_age (yr bp)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB6de99713
<p style="margin-left: 10px"><strong>variableName: </strong>Corrected_age
<p style="margin-left: 10px"><strong>units: </strong>yr bp
<p style="margin-left: 10px"><strong>description: </strong>Corrected ages use an average crustal value for the initial 230Th/232Th atomic ratio = 4.4 <c2><b1> 2.2 ppm.
</details>
<details style="margin-left: 10px">
<summary>Corrected_age_error (yr)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB428dd991
<p style="margin-left: 10px"><strong>variableName: </strong>Corrected_age_error
<p style="margin-left: 10px"><strong>units: </strong>yr
</details>

Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### Sitemap

```{r}
  map.meta.split <- split(map.meta, map.meta$archiveType)


factpal <- colorFactor("Paired",map.meta$archiveType)
buff <- 15
l <- leaflet() %>% 
  addTiles() %>% 
  fitBounds(map.meta$lon[i]-buff,map.meta$lat[i]-buff,map.meta$lon[i]+buff,map.meta$lat[i]+buff)
  

  
  
names(map.meta.split) %>%
  purrr::walk( function(df) {
    l <<- l %>%
      addMarkers(data=map.meta.split[[df]],
                 lng=~lon, lat=~lat,
                 label=~as.character(archiveType),
                 popup=~paste(str_c('Dataset: <a href="',link,'">',dataSetName,'</a>'),
                                 # str_c("Elevation: ",elev),
                                  str_c("Archive Type: ",archiveType),
                                  sep = "<br>"),
                 group = df,
                 clusterOptions = markerClusterOptions(removeOutsideVisibleBounds = F),
                 labelOptions = labelOptions(noHide = F,
                                             direction = 'auto'))
  })

l %>%
  addLayersControl(position = "bottomleft",
    overlayGroups = names(map.meta.split),
    options = layersControlOptions(collapsed = FALSE,
                                   opacity = 0.8)
  )
```

### Search the LiPDverse (Beta! doesn't work well yet)
```{r}
#Add google search bar
htmltools::includeHTML("../../googleSearchChunk.html")
```


Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### d18O (permil)
```{r}
plotCol(thisTS,ind = 2)
```

### d18O (permil)
```{r}
plotCol(thisTS,ind = 5)
```

### d13C (permil)
```{r}
plotCol(thisTS,ind = 6)
```

### notes (missing)
```{r}
plotCol(thisTS,ind = 7)
```

### d18O (permil)
```{r}
plotCol(thisTS,ind = 10)
```

### d13C (permil)
```{r}
plotCol(thisTS,ind = 11)
```

### notes (missing)
```{r}
plotCol(thisTS,ind = 12)
```

Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### depth (mm)
```{r}
plotCol(chronTS,ind = 2)
```

### core (unitless)
```{r}
plotCol(chronTS,ind = 1)
```

### 238U (ng/g)
```{r}
plotCol(chronTS,ind = 3)
```

### 238U_error (ng/g) (unitless)
```{r}
plotCol(chronTS,ind = 4)
```

### 232Th (pg/g)
```{r}
plotCol(chronTS,ind = 5)
```

### 232Th_error (unitless)
```{r}
plotCol(chronTS,ind = 6)
```

### 230Th/232Th (ratio)
```{r}
plotCol(chronTS,ind = 7)
```

### 230Th/232Th_error (unitless)
```{r}
plotCol(chronTS,ind = 8)
```

### 230Th/238U (ratio)
```{r}
plotCol(chronTS,ind = 9)
```

### 230Th/238U_error (unitless)
```{r}
plotCol(chronTS,ind = 10)
```

### d234U (unitless)
```{r}
plotCol(chronTS,ind = 11)
```

### d234U_error (unitless)
```{r}
plotCol(chronTS,ind = 12)
```

### initial_d234U (permil)
```{r}
plotCol(chronTS,ind = 13)
```

### d234U_error (unitless)
```{r}
plotCol(chronTS,ind = 14)
```

### uncorrected_age (yr bp)
```{r}
plotCol(chronTS,ind = 15)
```

### uncorrected_age_error (yr)
```{r}
plotCol(chronTS,ind = 16)
```

### Corrected_age (yr bp)
```{r}
plotCol(chronTS,ind = 17)
```

### Corrected_age_error (yr)
```{r}
plotCol(chronTS,ind = 18)
```
