---
title: "Kotokel.Tarasov.2009"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
    theme: bootstrap
    source_code: embed
    orientation: rows
---

```{r setup, include = FALSE}
library(flexdashboard)
library(maptools)
library(tidyverse)
library(purrr)
library(leaflet)
library(plotly)
library(lipdR)
library(dygraphs)
library(geoChronR)
library(lipdverseR)
#read functions
load("../../temp.Rdata")
load("../../chronTemp.Rdata")


#remove columns we don't want to plot
varNames <- sapply(TS, "[[","paleoData_variableName")

# good <- which(!(varNames %in% c("year","depth","age")))
# TS <- TS[good]


#All datasets
dsn <- sapply(TS,"[[","dataSetName")
ui <- which(!duplicated(dsn))
udsn <- dsn[ui]
lat <- as.numeric(sapply(TS,"[[","geo_latitude")[ui])
lon <- as.numeric(sapply(TS,"[[","geo_longitude")[ui])
#elev <- sapply(TS,"[[","geo_elevation")[ui]
archiveType <- sapply(TS,"[[","archiveType")[ui]
link <- paste0(udsn,".html") %>% 
  str_replace_all("'","_")

#Organize metadata for map
map.meta <- data.frame(dataSetName = udsn, #datasetname
                       lat = lat,#lat
                       lon = lon,#lon
                      # elev = elev,#elevation
                       archiveType = factor(archiveType),#archiveType
                       link = link)#Link


#set index number

i = 395
thisTS <- TS[which(udsn[i] == dsn)]
```
#Kotokel.Tarasov.2009

Metadata {.sidebar}
-------------------------------------
[Download LiPD file](Kotokel.Tarasov.2009.lpd)
            

[Edit LiPD file](http://lipd.net/playground?source=http://lipdverse.org/globalHolocene/0_25_5/Kotokel.Tarasov.2009.lpd)
            

[Download paleoData only (csv)](Kotokel.Tarasov.2009.csv)
            

[Report an issue (include dataset name)](https://github.com/nickmckay/LiPDverse/issues)

<details open style="margin-left: 0px">
<summary>root</summary>
<p style="margin-left: 0px"><strong>archiveType: </strong>LakeSediment
<p style="margin-left: 0px"><strong>lipdVersion: </strong>1.3
</details>
<details>
<summary>pub</summary>
<details style="margin-left: 10px">
<summary>pub1</summary>
<p style="margin-left: 10px"><strong>author: </strong>list(list(name = "Tarasov, P. E."), list(name = "Bezrukova, E. V."), list(name = "Krivonogov, S. K."))
<p style="margin-left: 10px"><strong>citeKey: </strong>tarasov2009lateglacialandholocenecha
<p style="margin-left: 10px"><strong>journal: </strong>Climate of the Past
<p style="margin-left: 10px"><strong>volume: </strong>5
<p style="margin-left: 10px"><strong>pages: </strong>285-295
<p style="margin-left: 10px"><strong>title: </strong>Late Glacial and Holocene changes in vegetation cover and climate in southern Siberia derived from a 15 kyr long pollen record from Lake Kotokel
</details>
<details style="margin-left: 10px">
<summary>pub2</summary>
<p style="margin-left: 10px"><strong>author: </strong>list(list(name = NA))
</details>
</details>
<details open style="margin-left: 0px">
<summary>geo</summary>
<p style="margin-left: 0px"><strong>latitude: </strong>52.7928
<p style="margin-left: 0px"><strong>longitude: </strong>108.1244
<p style="margin-left: 0px"><strong>elevation: </strong>458
<p style="margin-left: 0px"><strong>siteName: </strong>LakeKotokel
</details>
<details open>
<summary>PaleoData columns</summary>
<details style="margin-left: 10px">
<summary>year (AD)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>Ru5vvaHj39H
<p style="margin-left: 10px"><strong>variableName: </strong>year
<p style="margin-left: 10px"><strong>units: </strong>AD
<p style="margin-left: 10px"><strong>description: </strong>Year AD
</details>
<details style="margin-left: 10px">
<summary>age (BP)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>RhWZvVN69ra
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>BP
<p style="margin-left: 10px"><strong>description: </strong>Years before present (1950) BP
</details>
<details style="margin-left: 10px">
<summary>map_mm (mm/yr)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>GHa91c9112
<p style="margin-left: 10px"><strong>variableName: </strong>map_mm
<p style="margin-left: 10px"><strong>units: </strong>mm/yr
<p style="margin-left: 10px"><strong>description: </strong>Precipitation
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>direction: </strong>positive
<p style="margin-left: 20px"><strong>interpDirection: </strong>positive
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>variable: </strong>M
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>temperature (degC)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>GHc1441dab
<p style="margin-left: 10px"><strong>variableName: </strong>temperature
<p style="margin-left: 10px"><strong>units: </strong>degC
<p style="margin-left: 10px"><strong>description: </strong>wintertemperature
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>direction: </strong>positive
<p style="margin-left: 20px"><strong>interpDirection: </strong>positive
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>seasonality: </strong>winter
<p style="margin-left: 20px"><strong>variable: </strong>T
<p style="margin-left: 20px"><strong>variableDetail: </strong>air@surface
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>temperature (degC)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>GHa85a120f
<p style="margin-left: 10px"><strong>variableName: </strong>temperature
<p style="margin-left: 10px"><strong>units: </strong>degC
<p style="margin-left: 10px"><strong>description: </strong>summertemperature
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>direction: </strong>positive
<p style="margin-left: 20px"><strong>interpDirection: </strong>positive
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>seasonality: </strong>Summer
<p style="margin-left: 20px"><strong>variable: </strong>T
<p style="margin-left: 20px"><strong>variableDetail: </strong>air@surface
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>temperature (degC)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>GHf27a4b77
<p style="margin-left: 10px"><strong>variableName: </strong>temperature
<p style="margin-left: 10px"><strong>units: </strong>degC
<p style="margin-left: 10px"><strong>description: </strong>annualtemperature
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>TRUE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>direction: </strong>positive
<p style="margin-left: 20px"><strong>interpDirection: </strong>positive
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>seasonality: </strong>1 2 3 4 5 6 7 8 9 10 11 12
<p style="margin-left: 20px"><strong>variable: </strong>T
<p style="margin-left: 20px"><strong>variableDetail: </strong>air@surface
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>BroadleavedWoodyCover___ (missing)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>GH4beb6e47
<p style="margin-left: 10px"><strong>variableName: </strong>BroadleavedWoodyCover___
<p style="margin-left: 10px"><strong>units: </strong>missing
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>stdDev___ (missing)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>GHf44e1593
<p style="margin-left: 10px"><strong>variableName: </strong>stdDev___
<p style="margin-left: 10px"><strong>units: </strong>missing
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>NeedleleavedWoodyCover___ (missing)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>GH9c8ac391
<p style="margin-left: 10px"><strong>variableName: </strong>NeedleleavedWoodyCover___
<p style="margin-left: 10px"><strong>units: </strong>missing
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>NeedleavedWoodyCoverStdDev___ (missing)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>GH8de84ae8
<p style="margin-left: 10px"><strong>variableName: </strong>NeedleavedWoodyCoverStdDev___
<p style="margin-left: 10px"><strong>units: </strong>missing
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>WoodyCover___ (missing)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>NAm2kHydro237
<p style="margin-left: 10px"><strong>variableName: </strong>WoodyCover___
<p style="margin-left: 10px"><strong>units: </strong>missing
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>OpenVegetation___ (missing)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>NAm2kHydro238
<p style="margin-left: 10px"><strong>variableName: </strong>OpenVegetation___
<p style="margin-left: 10px"><strong>units: </strong>missing
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Score_Tundra_ (degC)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>NAm2kHydro239
<p style="margin-left: 10px"><strong>variableName: </strong>Score_Tundra_
<p style="margin-left: 10px"><strong>units: </strong>degC
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Score_Taiga_ (degC)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>GH46d7498e
<p style="margin-left: 10px"><strong>variableName: </strong>Score_Taiga_
<p style="margin-left: 10px"><strong>units: </strong>degC
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Score_Steppe_ (degC)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDa7ecbe2b
<p style="margin-left: 10px"><strong>variableName: </strong>Score_Steppe_
<p style="margin-left: 10px"><strong>units: </strong>degC
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>BorealTrees___ (missing)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDb3fd6c2c
<p style="margin-left: 10px"><strong>variableName: </strong>BorealTrees___
<p style="margin-left: 10px"><strong>units: </strong>missing
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>BorealShrubs___ (missing)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD267e1654
<p style="margin-left: 10px"><strong>variableName: </strong>BorealShrubs___
<p style="margin-left: 10px"><strong>units: </strong>missing
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Herbs___ (missing)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDb1ac0aee
<p style="margin-left: 10px"><strong>variableName: </strong>Herbs___
<p style="margin-left: 10px"><strong>units: </strong>missing
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>Pollen_spores_Total___ (total)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD481e546f
<p style="margin-left: 10px"><strong>variableName: </strong>Pollen_spores_Total___
<p style="margin-left: 10px"><strong>units: </strong>total
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>

Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### Sitemap

```{r}
  map.meta.split <- split(map.meta, map.meta$archiveType)


factpal <- colorFactor("Paired",map.meta$archiveType)
buff <- 15
l <- leaflet() %>% 
  addTiles() %>% 
  fitBounds(map.meta$lon[i]-buff,map.meta$lat[i]-buff,map.meta$lon[i]+buff,map.meta$lat[i]+buff)
  

  
  
names(map.meta.split) %>%
  purrr::walk( function(df) {
    l <<- l %>%
      addMarkers(data=map.meta.split[[df]],
                 lng=~lon, lat=~lat,
                 label=~as.character(archiveType),
                 popup=~paste(str_c('Dataset: <a href="',link,'">',dataSetName,'</a>'),
                                 # str_c("Elevation: ",elev),
                                  str_c("Archive Type: ",archiveType),
                                  sep = "<br>"),
                 group = df,
                 clusterOptions = markerClusterOptions(removeOutsideVisibleBounds = F),
                 labelOptions = labelOptions(noHide = F,
                                             direction = 'auto'))
  })

l %>%
  addLayersControl(position = "bottomleft",
    overlayGroups = names(map.meta.split),
    options = layersControlOptions(collapsed = FALSE,
                                   opacity = 0.8)
  )
```

### Search the LiPDverse (Beta! doesn't work well yet)
```{r}
#Add google search bar
htmltools::includeHTML("../../googleSearchChunk.html")
```


Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### map_mm (mm/yr)
```{r}
plotCol(thisTS,ind = 1)
```

### temperature (degC)
```{r}
plotCol(thisTS,ind = 4)
```

### temperature (degC)
```{r}
plotCol(thisTS,ind = 5)
```

### temperature (degC)
```{r}
plotCol(thisTS,ind = 6)
```

### BroadleavedWoodyCover___ (missing)
```{r}
plotCol(thisTS,ind = 7)
```

### stdDev___ (missing)
```{r}
plotCol(thisTS,ind = 8)
```

### NeedleleavedWoodyCover___ (missing)
```{r}
plotCol(thisTS,ind = 9)
```

### NeedleavedWoodyCoverStdDev___ (missing)
```{r}
plotCol(thisTS,ind = 10)
```

### WoodyCover___ (missing)
```{r}
plotCol(thisTS,ind = 11)
```

### OpenVegetation___ (missing)
```{r}
plotCol(thisTS,ind = 12)
```

### Score_Tundra_ (degC)
```{r}
plotCol(thisTS,ind = 13)
```

### Score_Taiga_ (degC)
```{r}
plotCol(thisTS,ind = 14)
```

### Score_Steppe_ (degC)
```{r}
plotCol(thisTS,ind = 15)
```

### BorealTrees___ (missing)
```{r}
plotCol(thisTS,ind = 16)
```

### BorealShrubs___ (missing)
```{r}
plotCol(thisTS,ind = 17)
```

### Herbs___ (missing)
```{r}
plotCol(thisTS,ind = 18)
```

### Pollen_spores_Total___ (total)
```{r}
plotCol(thisTS,ind = 19)
```
