---
title: "Leviathan.Lachniet.2014"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
    theme: bootstrap
    source_code: embed
    orientation: rows
---

```{r setup, include = FALSE}
library(flexdashboard)
library(maptools)
library(tidyverse)
library(purrr)
library(leaflet)
library(plotly)
library(lipdR)
library(dygraphs)
library(geoChronR)
library(lipdverseR)
#read functions
load("../../temp.Rdata")
load("../../chronTemp.Rdata")


#remove columns we don't want to plot
varNames <- sapply(TS, "[[","paleoData_variableName")

# good <- which(!(varNames %in% c("year","depth","age")))
# TS <- TS[good]


#All datasets
dsn <- sapply(TS,"[[","dataSetName")
ui <- which(!duplicated(dsn))
udsn <- dsn[ui]
lat <- as.numeric(sapply(TS,"[[","geo_latitude")[ui])
lon <- as.numeric(sapply(TS,"[[","geo_longitude")[ui])
#elev <- sapply(TS,"[[","geo_elevation")[ui]
archiveType <- sapply(TS,"[[","archiveType")[ui]
link <- paste0(udsn,".html") %>% 
  str_replace_all("'","_")

#Organize metadata for map
map.meta <- data.frame(dataSetName = udsn, #datasetname
                       lat = lat,#lat
                       lon = lon,#lon
                      # elev = elev,#elevation
                       archiveType = factor(archiveType),#archiveType
                       link = link)#Link


#set index number

i = 460
thisTS <- TS[which(udsn[i] == dsn)]
```
#Leviathan.Lachniet.2014

Metadata {.sidebar}
-------------------------------------
[Download LiPD file](Leviathan.Lachniet.2014.lpd)
            

[Edit LiPD file](http://lipd.net/playground?source=http://lipdverse.org/globalHolocene/0_25_5/Leviathan.Lachniet.2014.lpd)
            

[Download paleoData only (csv)](Leviathan.Lachniet.2014.csv)
            

[Download chronData only (csv)](Leviathan.Lachniet.2014-chron.csv)
            

[Report an issue (include dataset name)](https://github.com/nickmckay/LiPDverse/issues)

<details open style="margin-left: 0px">
<summary>root</summary>
<p style="margin-left: 0px"><strong>archiveType: </strong>Speleothem
<p style="margin-left: 0px"><strong>originalDataURL: </strong>https://www.ncdc.noaa.gov/paleo/study/16517
<p style="margin-left: 0px"><strong>lipdVersion: </strong>1.3
</details>
<details>
<summary>pub</summary>
<details style="margin-left: 10px">
<summary>pub1</summary>
<p style="margin-left: 10px"><strong>author: </strong>list(list(name = "Lachniet, Matthew S."), list(name = "Denniston, Rhawn F."), list(name = "Asmerom, Yemane"), list(name = "Polyak, Victor J."))
<p style="margin-left: 10px"><strong>citeKey: </strong>lachniet2014orbitalcontrolofwesternno
<p style="margin-left: 10px"><strong>journal: </strong>Nature Communications
<p style="margin-left: 10px"><strong>volume: </strong>5
<p style="margin-left: 10px"><strong>title: </strong>Orbital control of western North America atmospheric circulation and climate over two glacial cycles
</details>
<details style="margin-left: 10px">
<summary>pub2</summary>
<p style="margin-left: 10px"><strong>author: </strong>list(list(name = NA))
</details>
</details>
<details open style="margin-left: 0px">
<summary>geo</summary>
<p style="margin-left: 0px"><strong>latitude: </strong>37.89
<p style="margin-left: 0px"><strong>longitude: </strong>-115.58
<p style="margin-left: 0px"><strong>elevation: </strong>2400
<p style="margin-left: 0px"><strong>siteName: </strong>Leviathan
</details>
<details open>
<summary>PaleoData columns</summary>
<details style="margin-left: 10px">
<summary>year (AD) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDa57620f7
<p style="margin-left: 10px"><strong>variableName: </strong>year
<p style="margin-left: 10px"><strong>units: </strong>AD
<p style="margin-left: 10px"><strong>description: </strong>Year AD
</details>
<details style="margin-left: 10px">
<summary>age (BP) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD94e74028
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>BP
<p style="margin-left: 10px"><strong>description: </strong>Years before present (1950) yr BP
</details>
<details style="margin-left: 10px">
<summary>d18O (permil) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDe1fb72db
<p style="margin-left: 10px"><strong>variableName: </strong>d18O
<p style="margin-left: 10px"><strong>units: </strong>permil
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>direction: </strong>positive
<p style="margin-left: 20px"><strong>interpDirection: </strong>positive
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>seasonality: </strong>1 2 3 4 5 6 7 8 9 10 11 12
<p style="margin-left: 20px"><strong>variable: </strong>T
<p style="margin-left: 20px"><strong>variableDetail: </strong>air@surface
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>depth (missing) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDe1fb72dbaa
<p style="margin-left: 10px"><strong>variableName: </strong>depth
<p style="margin-left: 10px"><strong>units: </strong>missing
</details>
<details style="margin-left: 10px">
<summary>age (BP) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD94e74028dd
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>BP
</details>
<details style="margin-left: 10px">
<summary>d13C (permil) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDa57620f7bb
<p style="margin-left: 10px"><strong>variableName: </strong>d13C
<p style="margin-left: 10px"><strong>units: </strong>permil
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>TRUE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>direction: </strong>negative
<p style="margin-left: 20px"><strong>interpDirection: </strong>negative
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>seasonality: </strong>1 2 3 4 5 6 7 8 9 10 11 12
<p style="margin-left: 20px"><strong>variable: </strong>M
<p style="margin-left: 20px"><strong>variableDetail: </strong>soil
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>d18O (permil) [1-2]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD94e74028cc
<p style="margin-left: 10px"><strong>variableName: </strong>d18O
<p style="margin-left: 10px"><strong>units: </strong>permil
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>TRUE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>direction: </strong>positive
<p style="margin-left: 20px"><strong>interpDirection: </strong>positive
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>seasonality: </strong>1 2 3 4 5 6 7 8 9 10 11 12
<p style="margin-left: 20px"><strong>variable: </strong>T
<p style="margin-left: 20px"><strong>variableDetail: </strong>air@surface
</details>
</details>
</details>
<details>
<summary>ChronData columns</summary>
<details style="margin-left: 10px">
<summary>depth (mm)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDe7708f4b
<p style="margin-left: 10px"><strong>variableName: </strong>depth
<p style="margin-left: 10px"><strong>units: </strong>mm
</details>
<details style="margin-left: 10px">
<summary>age (yr BP)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD6375b741
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>yr BP
</details>
<details style="margin-left: 10px">
<summary>x238U_ng_g_ (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD1cc72e30
<p style="margin-left: 10px"><strong>variableName: </strong>x238U_ng_g_
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>error_ng_g_ (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD9979b697
<p style="margin-left: 10px"><strong>variableName: </strong>error_ng_g_
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>x232Th_pg_g_ (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD257214a7
<p style="margin-left: 10px"><strong>variableName: </strong>x232Th_pg_g_
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>error_pg_g_ (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD80155fb9
<p style="margin-left: 10px"><strong>variableName: </strong>error_pg_g_
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>x230Th_232ThActivityRatio (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDe86e42a4
<p style="margin-left: 10px"><strong>variableName: </strong>x230Th_232ThActivityRatio
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>error230Th_232ThActivityRatio (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD24503af4
<p style="margin-left: 10px"><strong>variableName: </strong>error230Th_232ThActivityRatio
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>x230Th_238UActivityRatio (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD9f859727
<p style="margin-left: 10px"><strong>variableName: </strong>x230Th_238UActivityRatio
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>error230Th_238UActivityRatio (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD248cb8ef
<p style="margin-left: 10px"><strong>variableName: </strong>error230Th_238UActivityRatio
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>Measured_234U___ (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD74e8d312
<p style="margin-left: 10px"><strong>variableName: </strong>Measured_234U___
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>errorMeasured_234U___ (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD776b7bec
<p style="margin-left: 10px"><strong>variableName: </strong>errorMeasured_234U___
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>Initial_234U___ (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD0fe90f66
<p style="margin-left: 10px"><strong>variableName: </strong>Initial_234U___
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>errorInitial_234U___ (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD87fd8d60
<p style="margin-left: 10px"><strong>variableName: </strong>errorInitial_234U___
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>UncorrectedAge_yrBP_ (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD5578b6f4
<p style="margin-left: 10px"><strong>variableName: </strong>UncorrectedAge_yrBP_
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>error (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDbe7e0702
<p style="margin-left: 10px"><strong>variableName: </strong>error
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>error1 (yr)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD03892251
<p style="margin-left: 10px"><strong>variableName: </strong>error1
<p style="margin-left: 10px"><strong>units: </strong>yr
</details>

Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### Sitemap

```{r}
  map.meta.split <- split(map.meta, map.meta$archiveType)


factpal <- colorFactor("Paired",map.meta$archiveType)
buff <- 15
l <- leaflet() %>% 
  addTiles() %>% 
  fitBounds(map.meta$lon[i]-buff,map.meta$lat[i]-buff,map.meta$lon[i]+buff,map.meta$lat[i]+buff)
  

  
  
names(map.meta.split) %>%
  purrr::walk( function(df) {
    l <<- l %>%
      addMarkers(data=map.meta.split[[df]],
                 lng=~lon, lat=~lat,
                 label=~as.character(archiveType),
                 popup=~paste(str_c('Dataset: <a href="',link,'">',dataSetName,'</a>'),
                                 # str_c("Elevation: ",elev),
                                  str_c("Archive Type: ",archiveType),
                                  sep = "<br>"),
                 group = df,
                 clusterOptions = markerClusterOptions(removeOutsideVisibleBounds = F),
                 labelOptions = labelOptions(noHide = F,
                                             direction = 'auto'))
  })

l %>%
  addLayersControl(position = "bottomleft",
    overlayGroups = names(map.meta.split),
    options = layersControlOptions(collapsed = FALSE,
                                   opacity = 0.8)
  )
```

### Search the LiPDverse (Beta! doesn't work well yet)
```{r}
#Add google search bar
htmltools::includeHTML("../../googleSearchChunk.html")
```


Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### d18O (permil)
```{r}
plotCol(thisTS,ind = 1)
```

### d13C (permil)
```{r}
plotCol(thisTS,ind = 5)
```

### d18O (permil)
```{r}
plotCol(thisTS,ind = 6)
```

Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### depth (mm)
```{r}
plotCol(chronTS,ind = 1)
```

### age (yr BP)
```{r}
plotCol(chronTS,ind = 16)
```

### x238U_ng_g_ (unitless)
```{r}
plotCol(chronTS,ind = 2)
```

### error_ng_g_ (unitless)
```{r}
plotCol(chronTS,ind = 3)
```

### x232Th_pg_g_ (unitless)
```{r}
plotCol(chronTS,ind = 4)
```

### error_pg_g_ (unitless)
```{r}
plotCol(chronTS,ind = 5)
```

### x230Th_232ThActivityRatio (unitless)
```{r}
plotCol(chronTS,ind = 6)
```

### error230Th_232ThActivityRatio (unitless)
```{r}
plotCol(chronTS,ind = 7)
```

### x230Th_238UActivityRatio (unitless)
```{r}
plotCol(chronTS,ind = 8)
```

### error230Th_238UActivityRatio (unitless)
```{r}
plotCol(chronTS,ind = 9)
```

### Measured_234U___ (unitless)
```{r}
plotCol(chronTS,ind = 10)
```

### errorMeasured_234U___ (unitless)
```{r}
plotCol(chronTS,ind = 11)
```

### Initial_234U___ (unitless)
```{r}
plotCol(chronTS,ind = 12)
```

### errorInitial_234U___ (unitless)
```{r}
plotCol(chronTS,ind = 13)
```

### UncorrectedAge_yrBP_ (unitless)
```{r}
plotCol(chronTS,ind = 14)
```

### error (unitless)
```{r}
plotCol(chronTS,ind = 15)
```

### error1 (yr)
```{r}
plotCol(chronTS,ind = 17)
```
