---
title: "OregonCaves.Ersek.2012"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
    theme: bootstrap
    source_code: embed
    orientation: rows
---

```{r setup, include = FALSE}
library(flexdashboard)
library(maptools)
library(tidyverse)
library(purrr)
library(leaflet)
library(plotly)
library(lipdR)
library(dygraphs)
library(geoChronR)
library(lipdverseR)
#read functions
load("../../temp.Rdata")
load("../../chronTemp.Rdata")


#remove columns we don't want to plot
varNames <- sapply(TS, "[[","paleoData_variableName")

# good <- which(!(varNames %in% c("year","depth","age")))
# TS <- TS[good]


#All datasets
dsn <- sapply(TS,"[[","dataSetName")
ui <- which(!duplicated(dsn))
udsn <- dsn[ui]
lat <- as.numeric(sapply(TS,"[[","geo_latitude")[ui])
lon <- as.numeric(sapply(TS,"[[","geo_longitude")[ui])
#elev <- sapply(TS,"[[","geo_elevation")[ui]
archiveType <- sapply(TS,"[[","archiveType")[ui]
link <- paste0(udsn,".html") %>% 
  str_replace_all("'","_")

#Organize metadata for map
map.meta <- data.frame(dataSetName = udsn, #datasetname
                       lat = lat,#lat
                       lon = lon,#lon
                      # elev = elev,#elevation
                       archiveType = factor(archiveType),#archiveType
                       link = link)#Link


#set index number

i = 655
thisTS <- TS[which(udsn[i] == dsn)]
```
#OregonCaves.Ersek.2012

Metadata {.sidebar}
-------------------------------------
[Download LiPD file](OregonCaves.Ersek.2012.lpd)
            

[Edit LiPD file](http://lipd.net/playground?source=http://lipdverse.org/globalHolocene/0_25_5/OregonCaves.Ersek.2012.lpd)
            

[Download paleoData only (csv)](OregonCaves.Ersek.2012.csv)
            

[Download chronData only (csv)](OregonCaves.Ersek.2012-chron.csv)
            

[Report an issue (include dataset name)](https://github.com/nickmckay/LiPDverse/issues)

<details open style="margin-left: 0px">
<summary>root</summary>
<p style="margin-left: 0px"><strong>archiveType: </strong>Speleothem
<p style="margin-left: 0px"><strong>originalDataURL: </strong>https://www.ncdc.noaa.gov/paleo/study/13543
<p style="margin-left: 0px"><strong>lipdVersion: </strong>1.3
</details>
<details>
<summary>pub</summary>
<details style="margin-left: 10px">
<summary>pub1</summary>
<p style="margin-left: 10px"><strong>author: </strong>list(list(name = "Ersek, Vasile"), list(name = "Clark, Peter U."), list(name = "Mix, Alan C."), list(name = "Cheng, Hai"), list(name = "Lawrence Edwards, R."))
<p style="margin-left: 10px"><strong>citeKey: </strong>ersek2012holocenewinterclimatevari
<p style="margin-left: 10px"><strong>journal: </strong>Nature Communications
<p style="margin-left: 10px"><strong>volume: </strong>3
<p style="margin-left: 10px"><strong>pages: </strong>1219
<p style="margin-left: 10px"><strong>title: </strong>Holocene winter climate variability in mid-latitude western North America
</details>
<details style="margin-left: 10px">
<summary>pub2</summary>
<p style="margin-left: 10px"><strong>author: </strong>list(list(name = NA))
</details>
</details>
<details open style="margin-left: 0px">
<summary>geo</summary>
<p style="margin-left: 0px"><strong>latitude: </strong>42.083
<p style="margin-left: 0px"><strong>longitude: </strong>-123.416
<p style="margin-left: 0px"><strong>elevation: </strong>1390
<p style="margin-left: 0px"><strong>siteName: </strong>OregonCaves
</details>
<details open>
<summary>PaleoData columns</summary>
<details style="margin-left: 10px">
<summary>year (AD)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB6671fe0f
<p style="margin-left: 10px"><strong>variableName: </strong>year
<p style="margin-left: 10px"><strong>units: </strong>AD
<p style="margin-left: 10px"><strong>description: </strong>Year AD
</details>
<details style="margin-left: 10px">
<summary>age (BP)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB23ec07a5
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>BP
<p style="margin-left: 10px"><strong>description: </strong>Years before present (1950) yr BP
</details>
<details style="margin-left: 10px">
<summary>depth (cm)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB054d4a48
<p style="margin-left: 10px"><strong>variableName: </strong>depth
<p style="margin-left: 10px"><strong>units: </strong>cm
<p style="margin-left: 10px"><strong>description: </strong>depth
</details>
<details style="margin-left: 10px">
<summary>d13C (permil)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>GHb0707701
<p style="margin-left: 10px"><strong>variableName: </strong>d13C
<p style="margin-left: 10px"><strong>units: </strong>permil
<p style="margin-left: 10px"><strong>description: </strong>d13C of speleothem calcite
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>TRUE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>direction: </strong>positive
<p style="margin-left: 20px"><strong>interpDirection: </strong>positive
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>seasonality: </strong>winter
<p style="margin-left: 20px"><strong>variable: </strong>M
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>d18O (permil)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>GHe7662255
<p style="margin-left: 10px"><strong>variableName: </strong>d18O
<p style="margin-left: 10px"><strong>units: </strong>permil
<p style="margin-left: 10px"><strong>description: </strong>d18O of speleothem calcite
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>TRUE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>direction: </strong>positive
<p style="margin-left: 20px"><strong>interpDirection: </strong>positive
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>seasonality: </strong>winter
<p style="margin-left: 20px"><strong>variable: </strong>T
<p style="margin-left: 20px"><strong>variableDetail: </strong>air@condensationLevel
</details>
</details>
</details>
<details>
<summary>ChronData columns</summary>
<details style="margin-left: 10px">
<summary>Reference (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD03892251
<p style="margin-left: 10px"><strong>variableName: </strong>Reference
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>SiteName (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD6493a31e
<p style="margin-left: 10px"><strong>variableName: </strong>SiteName
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>CoreID (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD77171425
<p style="margin-left: 10px"><strong>variableName: </strong>CoreID
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>LabID (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD5eec1767
<p style="margin-left: 10px"><strong>variableName: </strong>LabID
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>TypeOfMaterialDated (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDf41c0fcf
<p style="margin-left: 10px"><strong>variableName: </strong>TypeOfMaterialDated
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>AverageSampleDepth_cm_ (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDc9f78438
<p style="margin-left: 10px"><strong>variableName: </strong>AverageSampleDepth_cm_
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>x238U_ppb_ (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDbf535196
<p style="margin-left: 10px"><strong>variableName: </strong>x238U_ppb_
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>x238UError (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDe7e3cd79
<p style="margin-left: 10px"><strong>variableName: </strong>x238UError
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>x232Th_ppt_ (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD1498ea89
<p style="margin-left: 10px"><strong>variableName: </strong>x232Th_ppt_
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>x232ThError (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD10b51e01
<p style="margin-left: 10px"><strong>variableName: </strong>x232ThError
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>x230Th_232Th_atomicX10_6_ (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD77004298
<p style="margin-left: 10px"><strong>variableName: </strong>x230Th_232Th_atomicX10_6_
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>x230Th_232ThError_atomicX10_6_ (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD17e7bf78
<p style="margin-left: 10px"><strong>variableName: </strong>x230Th_232ThError_atomicX10_6_
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>d234U_Measured (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD79b9b793
<p style="margin-left: 10px"><strong>variableName: </strong>d234U_Measured
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>d234U_Error (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDd465f31a
<p style="margin-left: 10px"><strong>variableName: </strong>d234U_Error
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>x230Th_238UActivity (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD139be9da
<p style="margin-left: 10px"><strong>variableName: </strong>x230Th_238UActivity
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>x230Th_238UActivityError (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDc7037769
<p style="margin-left: 10px"><strong>variableName: </strong>x230Th_238UActivityError
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>x230ThAgeUncorrected_yr_ (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD7c286fee
<p style="margin-left: 10px"><strong>variableName: </strong>x230ThAgeUncorrected_yr_
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>x230ThAgeUncorrectedError_yr_ (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD7be6185d
<p style="margin-left: 10px"><strong>variableName: </strong>x230ThAgeUncorrectedError_yr_
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>x230ThAgeCorrected_yr_ (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD33714919
<p style="margin-left: 10px"><strong>variableName: </strong>x230ThAgeCorrected_yr_
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>x230ThAgeCorrectedError_yr_ (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDe85bf987
<p style="margin-left: 10px"><strong>variableName: </strong>x230ThAgeCorrectedError_yr_
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>d234UInitial_Corrected (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD378db911
<p style="margin-left: 10px"><strong>variableName: </strong>d234UInitial_Corrected
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>d234UInitial_CorrectedError (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD77707982
<p style="margin-left: 10px"><strong>variableName: </strong>d234UInitial_CorrectedError
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>x230ThAge_B1950___Corrected (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDbc4843c1
<p style="margin-left: 10px"><strong>variableName: </strong>x230ThAge_B1950___Corrected
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>x230ThAge__CorrectedError (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD3f77f1de
<p style="margin-left: 10px"><strong>variableName: </strong>x230ThAge__CorrectedError
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>

Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### Sitemap

```{r}
  map.meta.split <- split(map.meta, map.meta$archiveType)


factpal <- colorFactor("Paired",map.meta$archiveType)
buff <- 15
l <- leaflet() %>% 
  addTiles() %>% 
  fitBounds(map.meta$lon[i]-buff,map.meta$lat[i]-buff,map.meta$lon[i]+buff,map.meta$lat[i]+buff)
  

  
  
names(map.meta.split) %>%
  purrr::walk( function(df) {
    l <<- l %>%
      addMarkers(data=map.meta.split[[df]],
                 lng=~lon, lat=~lat,
                 label=~as.character(archiveType),
                 popup=~paste(str_c('Dataset: <a href="',link,'">',dataSetName,'</a>'),
                                 # str_c("Elevation: ",elev),
                                  str_c("Archive Type: ",archiveType),
                                  sep = "<br>"),
                 group = df,
                 clusterOptions = markerClusterOptions(removeOutsideVisibleBounds = F),
                 labelOptions = labelOptions(noHide = F,
                                             direction = 'auto'))
  })

l %>%
  addLayersControl(position = "bottomleft",
    overlayGroups = names(map.meta.split),
    options = layersControlOptions(collapsed = FALSE,
                                   opacity = 0.8)
  )
```

### Search the LiPDverse (Beta! doesn't work well yet)
```{r}
#Add google search bar
htmltools::includeHTML("../../googleSearchChunk.html")
```


Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### d13C (permil)
```{r}
plotCol(thisTS,ind = 1)
```

### d18O (permil)
```{r}
plotCol(thisTS,ind = 5)
```

Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### Reference (unitless)
```{r}
plotCol(chronTS,ind = 1)
```

### SiteName (unitless)
```{r}
plotCol(chronTS,ind = 2)
```

### CoreID (unitless)
```{r}
plotCol(chronTS,ind = 3)
```

### LabID (unitless)
```{r}
plotCol(chronTS,ind = 4)
```

### TypeOfMaterialDated (unitless)
```{r}
plotCol(chronTS,ind = 5)
```

### AverageSampleDepth_cm_ (unitless)
```{r}
plotCol(chronTS,ind = 6)
```

### x238U_ppb_ (unitless)
```{r}
plotCol(chronTS,ind = 7)
```

### x238UError (unitless)
```{r}
plotCol(chronTS,ind = 8)
```

### x232Th_ppt_ (unitless)
```{r}
plotCol(chronTS,ind = 9)
```

### x232ThError (unitless)
```{r}
plotCol(chronTS,ind = 10)
```

### x230Th_232Th_atomicX10_6_ (unitless)
```{r}
plotCol(chronTS,ind = 11)
```

### x230Th_232ThError_atomicX10_6_ (unitless)
```{r}
plotCol(chronTS,ind = 12)
```

### d234U_Measured (unitless)
```{r}
plotCol(chronTS,ind = 13)
```

### d234U_Error (unitless)
```{r}
plotCol(chronTS,ind = 14)
```

### x230Th_238UActivity (unitless)
```{r}
plotCol(chronTS,ind = 15)
```

### x230Th_238UActivityError (unitless)
```{r}
plotCol(chronTS,ind = 16)
```

### x230ThAgeUncorrected_yr_ (unitless)
```{r}
plotCol(chronTS,ind = 17)
```

### x230ThAgeUncorrectedError_yr_ (unitless)
```{r}
plotCol(chronTS,ind = 18)
```

### x230ThAgeCorrected_yr_ (unitless)
```{r}
plotCol(chronTS,ind = 19)
```

### x230ThAgeCorrectedError_yr_ (unitless)
```{r}
plotCol(chronTS,ind = 20)
```

### d234UInitial_Corrected (unitless)
```{r}
plotCol(chronTS,ind = 21)
```

### d234UInitial_CorrectedError (unitless)
```{r}
plotCol(chronTS,ind = 22)
```

### x230ThAge_B1950___Corrected (unitless)
```{r}
plotCol(chronTS,ind = 23)
```

### x230ThAge__CorrectedError (unitless)
```{r}
plotCol(chronTS,ind = 24)
```
