---
title: "OwensLake.Benson.2002"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
    theme: bootstrap
    source_code: embed
    orientation: rows
---

```{r setup, include = FALSE}
library(flexdashboard)
library(maptools)
library(tidyverse)
library(purrr)
library(leaflet)
library(plotly)
library(lipdR)
library(dygraphs)
library(geoChronR)
library(lipdverseR)
#read functions
load("../../temp.Rdata")
load("../../chronTemp.Rdata")


#remove columns we don't want to plot
varNames <- sapply(TS, "[[","paleoData_variableName")

# good <- which(!(varNames %in% c("year","depth","age")))
# TS <- TS[good]


#All datasets
dsn <- sapply(TS,"[[","dataSetName")
ui <- which(!duplicated(dsn))
udsn <- dsn[ui]
lat <- as.numeric(sapply(TS,"[[","geo_latitude")[ui])
lon <- as.numeric(sapply(TS,"[[","geo_longitude")[ui])
#elev <- sapply(TS,"[[","geo_elevation")[ui]
archiveType <- sapply(TS,"[[","archiveType")[ui]
link <- paste0(udsn,".html") %>% 
  str_replace_all("'","_")

#Organize metadata for map
map.meta <- data.frame(dataSetName = udsn, #datasetname
                       lat = lat,#lat
                       lon = lon,#lon
                      # elev = elev,#elevation
                       archiveType = factor(archiveType),#archiveType
                       link = link)#Link


#set index number

i = 657
thisTS <- TS[which(udsn[i] == dsn)]
```
#OwensLake.Benson.2002

Metadata {.sidebar}
-------------------------------------
[Download LiPD file](OwensLake.Benson.2002.lpd)
            

[Edit LiPD file](http://lipd.net/playground?source=http://lipdverse.org/globalHolocene/0_25_5/OwensLake.Benson.2002.lpd)
            

[Download paleoData only (csv)](OwensLake.Benson.2002.csv)
            

[Download chronData only (csv)](OwensLake.Benson.2002-chron.csv)
            

[Report an issue (include dataset name)](https://github.com/nickmckay/LiPDverse/issues)

<details open style="margin-left: 0px">
<summary>root</summary>
<p style="margin-left: 0px"><strong>archiveType: </strong>LakeSediment
<p style="margin-left: 0px"><strong>lipdVersion: </strong>1.3
</details>
<details>
<summary>pub</summary>
<details style="margin-left: 10px">
<summary>pub1</summary>
<p style="margin-left: 10px"><strong>author: </strong>list(list(name = "Benson, Larry"), list(name = "Kashgarian, Michaele"), list(name = "Rye, Robert"), list(name = "Lund, Steve"), list(name = "Paillet, Fred"), list(name = "Smoot, Joseph"), list(name = "Kester, Cynthia"), list(name = "Mensing, Scott"), list(name = "Meko, Dave"), list(name = "Lindstroem, Susan"))
<p style="margin-left: 10px"><strong>citeKey: </strong>benson2002holocenemultidecadalandmu
<p style="margin-left: 10px"><strong>journal: </strong>Quaternary Science Reviews
<p style="margin-left: 10px"><strong>volume: </strong>21
<p style="margin-left: 10px"><strong>pages: </strong>659-682
<p style="margin-left: 10px"><strong>title: </strong>Holocene multidecadal and multicentennial droughts affecting Northern California and Nevada
</details>
<details style="margin-left: 10px">
<summary>pub2</summary>
<p style="margin-left: 10px"><strong>author: </strong>list(list(name = NA))
</details>
</details>
<details open style="margin-left: 0px">
<summary>geo</summary>
<p style="margin-left: 0px"><strong>latitude: </strong>36.4367
<p style="margin-left: 0px"><strong>longitude: </strong>-117.9683
<p style="margin-left: 0px"><strong>elevation: </strong>1085
<p style="margin-left: 0px"><strong>siteName: </strong>OwensLake
</details>
<details open>
<summary>PaleoData columns</summary>
<details style="margin-left: 10px">
<summary>year (AD)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB49c3356c
<p style="margin-left: 10px"><strong>variableName: </strong>year
<p style="margin-left: 10px"><strong>units: </strong>AD
<p style="margin-left: 10px"><strong>description: </strong>Year AD
</details>
<details style="margin-left: 10px">
<summary>age (BP)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>WEB90348afc
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>BP
<p style="margin-left: 10px"><strong>description: </strong>Years before present (1950) yr BP
</details>
<details style="margin-left: 10px">
<summary>d18O (permil)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>GHff49b8d3
<p style="margin-left: 10px"><strong>variableName: </strong>d18O
<p style="margin-left: 10px"><strong>units: </strong>permil
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>TRUE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>direction: </strong>positive
<p style="margin-left: 20px"><strong>interpDirection: </strong>positive
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>seasonality: </strong>1 2 3 4 5 6 7 8 9 10 11 12
<p style="margin-left: 20px"><strong>variable: </strong>M
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>d13C (permil)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>GHc872eada
<p style="margin-left: 10px"><strong>variableName: </strong>d13C
<p style="margin-left: 10px"><strong>units: </strong>permil
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details style="margin-left: 10px">
<summary>TIC (percent)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>GHc974cdd7
<p style="margin-left: 10px"><strong>variableName: </strong>TIC
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>direction: </strong>positive
<p style="margin-left: 20px"><strong>interpDirection: </strong>positive
<p style="margin-left: 20px"><strong>scope: </strong>climate
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>TOC (percent)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>GHfd14c67f
<p style="margin-left: 10px"><strong>variableName: </strong>TOC
<p style="margin-left: 10px"><strong>units: </strong>percent
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
</details>
<details>
<summary>ChronData columns</summary>
<details style="margin-left: 10px">
<summary>depth (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD73aa5800
<p style="margin-left: 10px"><strong>variableName: </strong>depth
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>description: </strong>cm
</details>
<details style="margin-left: 10px">
<summary>age (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDc1accbf5
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>description: </strong>yr BP
</details>
<details style="margin-left: 10px">
<summary>Reference (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDe897b7c7
<p style="margin-left: 10px"><strong>variableName: </strong>Reference
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>SiteName (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDe1fb72db
<p style="margin-left: 10px"><strong>variableName: </strong>SiteName
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>State (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD7457ad38
<p style="margin-left: 10px"><strong>variableName: </strong>State
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>CoreID (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD74bc6584
<p style="margin-left: 10px"><strong>variableName: </strong>CoreID
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>LabID (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD26449f3e
<p style="margin-left: 10px"><strong>variableName: </strong>LabID
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>ageErrorYoungest (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDf7af3f2e
<p style="margin-left: 10px"><strong>variableName: </strong>ageErrorYoungest
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>description: </strong>yr BP
</details>
<details style="margin-left: 10px">
<summary>ageErrorOldest (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDf2047c95
<p style="margin-left: 10px"><strong>variableName: </strong>ageErrorOldest
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>description: </strong>yr BP
</details>
<details style="margin-left: 10px">
<summary>ReservoirCorrected14CAge_yrsBefore1950AD_ (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD7d948e2c
<p style="margin-left: 10px"><strong>variableName: </strong>ReservoirCorrected14CAge_yrsBefore1950AD_
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>calibratedAge_yrsBefore1950AD_ (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD3100fe0a
<p style="margin-left: 10px"><strong>variableName: </strong>calibratedAge_yrsBefore1950AD_
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>ReservoirCorrection__R (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDf316b97e
<p style="margin-left: 10px"><strong>variableName: </strong>ReservoirCorrection__R
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>
<details style="margin-left: 10px">
<summary>Comments (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPD08287935
<p style="margin-left: 10px"><strong>variableName: </strong>Comments
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>

Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### Sitemap

```{r}
  map.meta.split <- split(map.meta, map.meta$archiveType)


factpal <- colorFactor("Paired",map.meta$archiveType)
buff <- 15
l <- leaflet() %>% 
  addTiles() %>% 
  fitBounds(map.meta$lon[i]-buff,map.meta$lat[i]-buff,map.meta$lon[i]+buff,map.meta$lat[i]+buff)
  

  
  
names(map.meta.split) %>%
  purrr::walk( function(df) {
    l <<- l %>%
      addMarkers(data=map.meta.split[[df]],
                 lng=~lon, lat=~lat,
                 label=~as.character(archiveType),
                 popup=~paste(str_c('Dataset: <a href="',link,'">',dataSetName,'</a>'),
                                 # str_c("Elevation: ",elev),
                                  str_c("Archive Type: ",archiveType),
                                  sep = "<br>"),
                 group = df,
                 clusterOptions = markerClusterOptions(removeOutsideVisibleBounds = F),
                 labelOptions = labelOptions(noHide = F,
                                             direction = 'auto'))
  })

l %>%
  addLayersControl(position = "bottomleft",
    overlayGroups = names(map.meta.split),
    options = layersControlOptions(collapsed = FALSE,
                                   opacity = 0.8)
  )
```

### Search the LiPDverse (Beta! doesn't work well yet)
```{r}
#Add google search bar
htmltools::includeHTML("../../googleSearchChunk.html")
```


Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### d18O (permil)
```{r}
plotCol(thisTS,ind = 4)
```

### d13C (permil)
```{r}
plotCol(thisTS,ind = 1)
```

### TIC (percent)
```{r}
plotCol(thisTS,ind = 5)
```

### TOC (percent)
```{r}
plotCol(thisTS,ind = 6)
```

Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### depth (unitless)
```{r}
plotCol(chronTS,ind = 6)
```

### age (unitless)
```{r}
plotCol(chronTS,ind = 7)
```

### Reference (unitless)
```{r}
plotCol(chronTS,ind = 1)
```

### SiteName (unitless)
```{r}
plotCol(chronTS,ind = 2)
```

### State (unitless)
```{r}
plotCol(chronTS,ind = 3)
```

### CoreID (unitless)
```{r}
plotCol(chronTS,ind = 4)
```

### LabID (unitless)
```{r}
plotCol(chronTS,ind = 5)
```

### ageErrorYoungest (unitless)
```{r}
plotCol(chronTS,ind = 8)
```

### ageErrorOldest (unitless)
```{r}
plotCol(chronTS,ind = 9)
```

### ReservoirCorrected14CAge_yrsBefore1950AD_ (unitless)
```{r}
plotCol(chronTS,ind = 10)
```

### calibratedAge_yrsBefore1950AD_ (unitless)
```{r}
plotCol(chronTS,ind = 11)
```

### ReservoirCorrection__R (unitless)
```{r}
plotCol(chronTS,ind = 12)
```

### Comments (unitless)
```{r}
plotCol(chronTS,ind = 13)
```
