---
title: "SK237-GC04.Saraswat.2013"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
    theme: bootstrap
    source_code: embed
    orientation: rows
---

```{r setup, include = FALSE}
library(flexdashboard)
library(maptools)
library(tidyverse)
library(purrr)
library(leaflet)
library(plotly)
library(lipdR)
library(dygraphs)
library(geoChronR)
library(lipdverseR)
#read functions
load("../../temp.Rdata")
load("../../chronTemp.Rdata")


#remove columns we don't want to plot
varNames <- sapply(TS, "[[","paleoData_variableName")

# good <- which(!(varNames %in% c("year","depth","age")))
# TS <- TS[good]


#All datasets
dsn <- sapply(TS,"[[","dataSetName")
ui <- which(!duplicated(dsn))
udsn <- dsn[ui]
lat <- as.numeric(sapply(TS,"[[","geo_latitude")[ui])
lon <- as.numeric(sapply(TS,"[[","geo_longitude")[ui])
#elev <- sapply(TS,"[[","geo_elevation")[ui]
archiveType <- sapply(TS,"[[","archiveType")[ui]
link <- paste0(udsn,".html") %>% 
  str_replace_all("'","_")

#Organize metadata for map
map.meta <- data.frame(dataSetName = udsn, #datasetname
                       lat = lat,#lat
                       lon = lon,#lon
                      # elev = elev,#elevation
                       archiveType = factor(archiveType),#archiveType
                       link = link)#Link


#set index number

i = 756
thisTS <- TS[which(udsn[i] == dsn)]
```
#SK237-GC04.Saraswat.2013

Metadata {.sidebar}
-------------------------------------
[Download LiPD file](SK237-GC04.Saraswat.2013.lpd)
            

[Edit LiPD file](http://lipd.net/playground?source=http://lipdverse.org/globalHolocene/0_25_5/SK237-GC04.Saraswat.2013.lpd)
            

[Download paleoData only (csv)](SK237-GC04.Saraswat.2013.csv)
            

[Download chronData only (csv)](SK237-GC04.Saraswat.2013-chron.csv)
            

[Report an issue (include dataset name)](https://github.com/nickmckay/LiPDverse/issues)

<details open style="margin-left: 0px">
<summary>root</summary>
<p style="margin-left: 0px"><strong>archiveType: </strong>MarineSediment
<p style="margin-left: 0px"><strong>originalDataURL: </strong>ftp://ftp.ncdc.noaa.gov/pub/data/paleo/contributions_by_author/saraswat2013/saraswat2013-sk237gc04.txt
<p style="margin-left: 0px"><strong>lipdVersion: </strong>1.3
<p style="margin-left: 0px"><strong>dataContributor: </strong>HLF
</details>
<details>
<summary>pub</summary>
<details style="margin-left: 10px">
<summary>pub1</summary>
<p style="margin-left: 10px"><strong>author: </strong>list(list(name = "Saraswat, Rajeev"), list(name = "Lea, David W."), list(name = "Nigam, Rajiv"), list(name = "Mackensen, Andreas"), list(name = "Naik, Dinesh K."))
<p style="margin-left: 10px"><strong>citeKey: </strong>saraswat2013deglaciation
<p style="margin-left: 10px"><strong>journal: </strong>Earth and Planetary Science Letters
<p style="margin-left: 10px"><strong>volume: </strong>375
<p style="margin-left: 10px"><strong>pages: </strong>166-175
<p style="margin-left: 10px"><strong>title: </strong>Deglaciation in the tropical Indian Ocean driven by interplay between the regional monsoon and global teleconnections
</details>
<details style="margin-left: 10px">
<summary>pub2</summary>
<p style="margin-left: 10px"><strong>author: </strong>list(list(name = NA))
<p style="margin-left: 10px"><strong>citeKey: </strong>saraswat2014o2klrDataCitation
<p style="margin-left: 10px"><strong>title: </strong>O2kLR-SWCoastOfIndia.Saraswat.2013
</details>
</details>
<details open style="margin-left: 0px">
<summary>geo</summary>
<p style="margin-left: 0px"><strong>latitude: </strong>10.98
<p style="margin-left: 0px"><strong>longitude: </strong>74.9993
<p style="margin-left: 0px"><strong>elevation: </strong>-1245
<p style="margin-left: 0px"><strong>siteName: </strong>SW coast of India, Indian ocean
<p style="margin-left: 0px"><strong>pages2kRegion: </strong>Ocean
</details>
<details open>
<summary>PaleoData columns</summary>
<details style="margin-left: 10px">
<summary>year (AD) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>MAT63674e7a05
<p style="margin-left: 10px"><strong>variableName: </strong>year
<p style="margin-left: 10px"><strong>units: </strong>AD
<p style="margin-left: 10px"><strong>description: </strong>Year AD
</details>
<details style="margin-left: 10px">
<summary>depth (cm) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>MAT551d02c7f8
<p style="margin-left: 10px"><strong>variableName: </strong>depth
<p style="margin-left: 10px"><strong>units: </strong>cm
<p style="margin-left: 10px"><strong>description: </strong>depth
</details>
<details style="margin-left: 10px">
<summary>temperature (permil) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>MS13RSAS01b
<p style="margin-left: 10px"><strong>variableName: </strong>temperature
<p style="margin-left: 10px"><strong>units: </strong>permil
<p style="margin-left: 10px"><strong>description: </strong>inferred seawater
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>basis: </strong>NaN
<p style="margin-left: 20px"><strong>direction: </strong>negative
<p style="margin-left: 20px"><strong>interpDirection: </strong>increase
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>seasonality: </strong>NaN
<p style="margin-left: 20px"><strong>variable: </strong>salinity
<p style="margin-left: 20px"><strong>variableDetail: </strong>sea@surface
</details>
<details style="margin-left: 20px">
<summary>2</summary>
<p style="margin-left: 20px"><strong>coefficient: </strong>NaN
<p style="margin-left: 20px"><strong>direction: </strong>positive
<p style="margin-left: 20px"><strong>equilibriumEvidence: </strong>NaN
<p style="margin-left: 20px"><strong>fraction: </strong>NaN
<p style="margin-left: 20px"><strong>inferredMaterial: </strong>seawater
<p style="margin-left: 20px"><strong>integrationTime: </strong>NaN
<p style="margin-left: 20px"><strong>integrationTimeBasis: </strong>NaN
<p style="margin-left: 20px"><strong>integrationTimeUncertainty: </strong>NaN
<p style="margin-left: 20px"><strong>integrationTimeUncertaintyType: </strong>NaN
<p style="margin-left: 20px"><strong>integrationTimeUnits: </strong>NaN
<p style="margin-left: 20px"><strong>mathematicalRelation: </strong>linear
<p style="margin-left: 20px"><strong>rank: </strong>NA
<p style="margin-left: 20px"><strong>scope: </strong>isotope
<p style="margin-left: 20px"><strong>seasonality: </strong>not applicable (always)
<p style="margin-left: 20px"><strong>variable: </strong>Salinity
</details>
<details style="margin-left: 20px">
<summary>3</summary>
<p style="margin-left: 20px"><strong>coefficient: </strong>NA
<p style="margin-left: 20px"><strong>fraction: </strong>NA
<p style="margin-left: 20px"><strong>rank: </strong>NA
<p style="margin-left: 20px"><strong>scope: </strong>isotope
</details>
<details style="margin-left: 20px">
<summary>4</summary>
<p style="margin-left: 20px"><strong>coefficient: </strong>NA
<p style="margin-left: 20px"><strong>fraction: </strong>NA
<p style="margin-left: 20px"><strong>rank: </strong>NA
<p style="margin-left: 20px"><strong>scope: </strong>isotope
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>Mg/Ca (degC) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>O2kLR_118q
<p style="margin-left: 10px"><strong>variableName: </strong>Mg/Ca
<p style="margin-left: 10px"><strong>units: </strong>degC
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>direction: </strong>positive
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>variable: </strong>T
</details>
<details style="margin-left: 20px">
<summary>2</summary>
<p style="margin-left: 20px"><strong>coefficient: </strong>NA
<p style="margin-left: 20px"><strong>fraction: </strong>NA
<p style="margin-left: 20px"><strong>rank: </strong>NA
<p style="margin-left: 20px"><strong>scope: </strong>isotope
</details>
<details style="margin-left: 20px">
<summary>3</summary>
<p style="margin-left: 20px"><strong>coefficient: </strong>NA
<p style="margin-left: 20px"><strong>fraction: </strong>NA
<p style="margin-left: 20px"><strong>rank: </strong>NA
<p style="margin-left: 20px"><strong>scope: </strong>isotope
</details>
<details style="margin-left: 20px">
<summary>4</summary>
<p style="margin-left: 20px"><strong>coefficient: </strong>NA
<p style="margin-left: 20px"><strong>fraction: </strong>NA
<p style="margin-left: 20px"><strong>rank: </strong>NA
<p style="margin-left: 20px"><strong>scope: </strong>isotope
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>temperature (permil) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>MS13RSAS01a
<p style="margin-left: 10px"><strong>variableName: </strong>temperature
<p style="margin-left: 10px"><strong>units: </strong>permil
<p style="margin-left: 10px"><strong>description: </strong>carbonate
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>basis: </strong>NaN
<p style="margin-left: 20px"><strong>interpDirection: </strong>decrease/increase
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>seasonality: </strong>NaN
<p style="margin-left: 20px"><strong>variable: </strong>temperature/salinity
<p style="margin-left: 20px"><strong>variableDetail: </strong>sea@surface
</details>
<details style="margin-left: 20px">
<summary>2</summary>
<p style="margin-left: 20px"><strong>basis: </strong>Urey, H. C. 1948. Oxygen isotopes in nature and in the laboratory. Science, 108:489?496.
<p style="margin-left: 20px"><strong>coefficient: </strong>NaN
<p style="margin-left: 20px"><strong>direction: </strong>decrease
<p style="margin-left: 20px"><strong>equilibriumEvidence: </strong>NaN
<p style="margin-left: 20px"><strong>fraction: </strong>NaN
<p style="margin-left: 20px"><strong>inferredMaterial: </strong>seawater
<p style="margin-left: 20px"><strong>integrationTime: </strong>NaN
<p style="margin-left: 20px"><strong>integrationTimeBasis: </strong>NaN
<p style="margin-left: 20px"><strong>integrationTimeUncertainty: </strong>NaN
<p style="margin-left: 20px"><strong>integrationTimeUncertaintyType: </strong>NaN
<p style="margin-left: 20px"><strong>integrationTimeUnits: </strong>NaN
<p style="margin-left: 20px"><strong>mathematicalRelation: </strong>non-linear
<p style="margin-left: 20px"><strong>scope: </strong>isotope
<p style="margin-left: 20px"><strong>seasonality: </strong>not applicable (always)
<p style="margin-left: 20px"><strong>variable: </strong>Temperature_water
</details>
<details style="margin-left: 20px">
<summary>3</summary>
<p style="margin-left: 20px"><strong>basis: </strong>Urey, H. C. 1948. Oxygen isotopes in nature and in the laboratory. Science, 108:489?496.
<p style="margin-left: 20px"><strong>coefficient: </strong>NaN
<p style="margin-left: 20px"><strong>direction: </strong>decrease
<p style="margin-left: 20px"><strong>equilibriumEvidence: </strong>NaN
<p style="margin-left: 20px"><strong>fraction: </strong>NaN
<p style="margin-left: 20px"><strong>inferredMaterial: </strong>calcite; sea surface water
<p style="margin-left: 20px"><strong>integrationTime: </strong>NaN
<p style="margin-left: 20px"><strong>integrationTimeBasis: </strong>NaN
<p style="margin-left: 20px"><strong>integrationTimeUncertainty: </strong>NaN
<p style="margin-left: 20px"><strong>integrationTimeUncertaintyType: </strong>NaN
<p style="margin-left: 20px"><strong>integrationTimeUnits: </strong>NaN
<p style="margin-left: 20px"><strong>mathematicalRelation: </strong>non-linear
<p style="margin-left: 20px"><strong>scope: </strong>isotope
<p style="margin-left: 20px"><strong>seasonality: </strong>not applicable (always)
<p style="margin-left: 20px"><strong>variable: </strong>seawater_isotope
</details>
<details style="margin-left: 20px">
<summary>4</summary>
<p style="margin-left: 20px"><strong>basis: </strong>Spero, H.J., Bijma, J., Lea, D.W., Bemis, B.E., 1997. Effect of seawater carbonate concentration on foraminiferal carbon and oxygen isotopes. Nature 390, 497-500.
<p style="margin-left: 20px"><strong>coefficient: </strong>NaN
<p style="margin-left: 20px"><strong>direction: </strong>negative
<p style="margin-left: 20px"><strong>equilibriumEvidence: </strong>NaN
<p style="margin-left: 20px"><strong>fraction: </strong>NaN
<p style="margin-left: 20px"><strong>inferredMaterial: </strong>calcite; sea surface water
<p style="margin-left: 20px"><strong>integrationTime: </strong>NaN
<p style="margin-left: 20px"><strong>integrationTimeBasis: </strong>NaN
<p style="margin-left: 20px"><strong>integrationTimeUncertainty: </strong>NaN
<p style="margin-left: 20px"><strong>integrationTimeUncertaintyType: </strong>NaN
<p style="margin-left: 20px"><strong>integrationTimeUnits: </strong>NaN
<p style="margin-left: 20px"><strong>mathematicalRelation: </strong>linear
<p style="margin-left: 20px"><strong>scope: </strong>isotope
<p style="margin-left: 20px"><strong>seasonality: </strong>not applicable (always)
<p style="margin-left: 20px"><strong>variable: </strong>Carbonate_ion_concentration
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>d18O (mmol/mol) [1-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>LPDc1accbf5t
<p style="margin-left: 10px"><strong>variableName: </strong>d18O
<p style="margin-left: 10px"><strong>units: </strong>mmol/mol
<p style="margin-left: 10px"><strong>description: </strong>Mg/Ca of foraminiferal calcite
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>coefficient: </strong>NA
<p style="margin-left: 20px"><strong>fraction: </strong>NA
<p style="margin-left: 20px"><strong>rank: </strong>NA
<p style="margin-left: 20px"><strong>scope: </strong>isotope
</details>
<details style="margin-left: 20px">
<summary>2</summary>
<p style="margin-left: 20px"><strong>coefficient: </strong>NA
<p style="margin-left: 20px"><strong>fraction: </strong>NA
<p style="margin-left: 20px"><strong>rank: </strong>NA
<p style="margin-left: 20px"><strong>scope: </strong>isotope
</details>
<details style="margin-left: 20px">
<summary>3</summary>
<p style="margin-left: 20px"><strong>coefficient: </strong>NA
<p style="margin-left: 20px"><strong>fraction: </strong>NA
<p style="margin-left: 20px"><strong>rank: </strong>NA
<p style="margin-left: 20px"><strong>scope: </strong>isotope
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>year (AD) [2-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>MATff75ed4ec7
<p style="margin-left: 10px"><strong>variableName: </strong>year
<p style="margin-left: 10px"><strong>units: </strong>AD
<p style="margin-left: 10px"><strong>description: </strong>Year AD
</details>
<details style="margin-left: 10px">
<summary>temperature (degC) [2-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>O2kLR_118
<p style="margin-left: 10px"><strong>variableName: </strong>temperature
<p style="margin-left: 10px"><strong>units: </strong>degC
<p style="margin-left: 10px"><strong>description: </strong>inferred sea-surface temperature
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>TRUE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>basis: </strong>Mg/Ca calibration to SST
<p style="margin-left: 20px"><strong>direction: </strong>negative
<p style="margin-left: 20px"><strong>interpDirection: </strong>increase
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>seasonality: </strong>1 2 3 4 5 6 7 8 9 10 11 12
<p style="margin-left: 20px"><strong>variable: </strong>T
<p style="margin-left: 20px"><strong>variableDetail: </strong>sea@surface
</details>
<details style="margin-left: 20px">
<summary>2</summary>
<p style="margin-left: 20px"><strong>coefficient: </strong>NA
<p style="margin-left: 20px"><strong>fraction: </strong>NA
<p style="margin-left: 20px"><strong>rank: </strong>NA
<p style="margin-left: 20px"><strong>scope: </strong>isotope
</details>
<details style="margin-left: 20px">
<summary>3</summary>
<p style="margin-left: 20px"><strong>coefficient: </strong>NA
<p style="margin-left: 20px"><strong>fraction: </strong>NA
<p style="margin-left: 20px"><strong>rank: </strong>NA
<p style="margin-left: 20px"><strong>scope: </strong>isotope
</details>
<details style="margin-left: 20px">
<summary>4</summary>
<p style="margin-left: 20px"><strong>coefficient: </strong>NA
<p style="margin-left: 20px"><strong>fraction: </strong>NA
<p style="margin-left: 20px"><strong>rank: </strong>NA
<p style="margin-left: 20px"><strong>scope: </strong>isotope
</details>
</details>
</details>
<details style="margin-left: 10px">
<summary>year (AD) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>MATc670f8ea71
<p style="margin-left: 10px"><strong>variableName: </strong>year
<p style="margin-left: 10px"><strong>units: </strong>AD
<p style="margin-left: 10px"><strong>description: </strong>Year AD
</details>
<details style="margin-left: 10px">
<summary>d18O (degC) [3-1]</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>O2kLR_120
<p style="margin-left: 10px"><strong>variableName: </strong>d18O
<p style="margin-left: 10px"><strong>units: </strong>degC
<p style="margin-left: 10px"><strong>description: </strong>inferred sea-surface temperature
<p style="margin-left: 10px"><strong>useInGlobalTemperatureAnalysis: </strong>FALSE
<details>
<summary>interpretation</summary>
<details style="margin-left: 20px">
<summary>1</summary>
<p style="margin-left: 20px"><strong>basis: </strong>Mg/Ca calibration to SST
<p style="margin-left: 20px"><strong>direction: </strong>negative
<p style="margin-left: 20px"><strong>interpDirection: </strong>increase
<p style="margin-left: 20px"><strong>scope: </strong>climate
<p style="margin-left: 20px"><strong>seasonality: </strong>1 2 3 4 5 6 7 8 9 10 11 12
<p style="margin-left: 20px"><strong>variable: </strong>T
<p style="margin-left: 20px"><strong>variableDetail: </strong>sea@surface
</details>
<details style="margin-left: 20px">
<summary>2</summary>
<p style="margin-left: 20px"><strong>coefficient: </strong>NA
<p style="margin-left: 20px"><strong>fraction: </strong>NA
<p style="margin-left: 20px"><strong>rank: </strong>NA
<p style="margin-left: 20px"><strong>scope: </strong>isotope
</details>
<details style="margin-left: 20px">
<summary>3</summary>
<p style="margin-left: 20px"><strong>coefficient: </strong>NA
<p style="margin-left: 20px"><strong>fraction: </strong>NA
<p style="margin-left: 20px"><strong>rank: </strong>NA
<p style="margin-left: 20px"><strong>scope: </strong>isotope
</details>
<details style="margin-left: 20px">
<summary>4</summary>
<p style="margin-left: 20px"><strong>coefficient: </strong>NA
<p style="margin-left: 20px"><strong>fraction: </strong>NA
<p style="margin-left: 20px"><strong>rank: </strong>NA
<p style="margin-left: 20px"><strong>scope: </strong>isotope
</details>
</details>
</details>
<details>
<summary>ChronData columns</summary>
<details style="margin-left: 10px">
<summary>depth (cm)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>chron1
<p style="margin-left: 10px"><strong>variableName: </strong>depth
<p style="margin-left: 10px"><strong>units: </strong>cm
<p style="margin-left: 10px"><strong>description: </strong>mid-point depth
</details>
<details style="margin-left: 10px">
<summary>age (yr BP)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>chron15
<p style="margin-left: 10px"><strong>variableName: </strong>age
<p style="margin-left: 10px"><strong>units: </strong>yr BP
<p style="margin-left: 10px"><strong>description: </strong>years before 1950 (calibrated age, or ages that dont need calibration)
</details>
<details style="margin-left: 10px">
<summary>age14C (yr14C BP)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>chron2
<p style="margin-left: 10px"><strong>variableName: </strong>age14C
<p style="margin-left: 10px"><strong>units: </strong>yr14C BP
<p style="margin-left: 10px"><strong>description: </strong>14C years before 1950
</details>
<details style="margin-left: 10px">
<summary>age14Cuncertainty (yr14C BP)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>chron3
<p style="margin-left: 10px"><strong>variableName: </strong>age14Cuncertainty
<p style="margin-left: 10px"><strong>units: </strong>yr14C BP
<p style="margin-left: 10px"><strong>description: </strong>14C years uncertainty
</details>
<details style="margin-left: 10px">
<summary>fractionModern (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>chron4
<p style="margin-left: 10px"><strong>variableName: </strong>fractionModern
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>description: </strong>fraction of modern 14C activity
</details>
<details style="margin-left: 10px">
<summary>fractionModernUncertainty (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>chron5
<p style="margin-left: 10px"><strong>variableName: </strong>fractionModernUncertainty
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>description: </strong>fraction of modern 14C activity uncertainty
</details>
<details style="margin-left: 10px">
<summary>delta13C (permil)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>chron6
<p style="margin-left: 10px"><strong>variableName: </strong>delta13C
<p style="margin-left: 10px"><strong>units: </strong>permil
<p style="margin-left: 10px"><strong>description: </strong>delta13C of material analyzed for 14C
</details>
<details style="margin-left: 10px">
<summary>delta13Cuncertainty (permil)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>chron7
<p style="margin-left: 10px"><strong>variableName: </strong>delta13Cuncertainty
<p style="margin-left: 10px"><strong>units: </strong>permil
<p style="margin-left: 10px"><strong>description: </strong>delta13C uncertainty
</details>
<details style="margin-left: 10px">
<summary>thickness (cm)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>chron8
<p style="margin-left: 10px"><strong>variableName: </strong>thickness
<p style="margin-left: 10px"><strong>units: </strong>cm
<p style="margin-left: 10px"><strong>description: </strong>thickness of sample (along depth axis)
</details>
<details style="margin-left: 10px">
<summary>labID (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>chron9
<p style="margin-left: 10px"><strong>variableName: </strong>labID
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>description: </strong>laboratory ID from radiocarbon facility
</details>
<details style="margin-left: 10px">
<summary>materialDated (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>chron10
<p style="margin-left: 10px"><strong>variableName: </strong>materialDated
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>description: </strong>material analyzed
</details>
<details style="margin-left: 10px">
<summary>activity (Bq g-1)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>chron11
<p style="margin-left: 10px"><strong>variableName: </strong>activity
<p style="margin-left: 10px"><strong>units: </strong>Bq g-1
<p style="margin-left: 10px"><strong>description: </strong>210Pb, 239+240Pu or 137Cs activity
</details>
<details style="margin-left: 10px">
<summary>activityUncertainty (Bq g-1)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>chron12
<p style="margin-left: 10px"><strong>variableName: </strong>activityUncertainty
<p style="margin-left: 10px"><strong>units: </strong>Bq g-1
<p style="margin-left: 10px"><strong>description: </strong>210Pb, 239+240Pu or 137Cs activity uncertainty
</details>
<details style="margin-left: 10px">
<summary>supportedActivity (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>chron13
<p style="margin-left: 10px"><strong>variableName: </strong>supportedActivity
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>description: </strong>Y if supported 210Pb activity, N if unsupported 210Pb activity
</details>
<details style="margin-left: 10px">
<summary>x210PbModel (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>chron14
<p style="margin-left: 10px"><strong>variableName: </strong>x210PbModel
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>description: </strong>model used to convert 210Pb activity to age (e.g., constant rate of supply)
</details>
<details style="margin-left: 10px">
<summary>ageUncertainty (yr BP)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>chron16
<p style="margin-left: 10px"><strong>variableName: </strong>ageUncertainty
<p style="margin-left: 10px"><strong>units: </strong>yr BP
<p style="margin-left: 10px"><strong>description: </strong>uncertainty in age
</details>
<details style="margin-left: 10px">
<summary>reservoirAge14C (yr14C BP)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>chron17
<p style="margin-left: 10px"><strong>variableName: </strong>reservoirAge14C
<p style="margin-left: 10px"><strong>units: </strong>yr14C BP
<p style="margin-left: 10px"><strong>description: </strong>14C reservoir age
</details>
<details style="margin-left: 10px">
<summary>reservoirAge14CUncertainty (yr14C BP)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>chron18
<p style="margin-left: 10px"><strong>variableName: </strong>reservoirAge14CUncertainty
<p style="margin-left: 10px"><strong>units: </strong>yr14C BP
<p style="margin-left: 10px"><strong>description: </strong>14C reservoir age uncertainty
</details>
<details style="margin-left: 10px">
<summary>useInAgeModel (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>chron19
<p style="margin-left: 10px"><strong>variableName: </strong>useInAgeModel
<p style="margin-left: 10px"><strong>units: </strong>unitless
<p style="margin-left: 10px"><strong>description: </strong>was this date used in the age model?
</details>
<details style="margin-left: 10px">
<summary>notes (unitless)</summary>
<p style="margin-left: 10px"><strong>TSid: </strong>chron20
<p style="margin-left: 10px"><strong>variableName: </strong>notes
<p style="margin-left: 10px"><strong>units: </strong>unitless
</details>

Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### Sitemap

```{r}
  map.meta.split <- split(map.meta, map.meta$archiveType)


factpal <- colorFactor("Paired",map.meta$archiveType)
buff <- 15
l <- leaflet() %>% 
  addTiles() %>% 
  fitBounds(map.meta$lon[i]-buff,map.meta$lat[i]-buff,map.meta$lon[i]+buff,map.meta$lat[i]+buff)
  

  
  
names(map.meta.split) %>%
  purrr::walk( function(df) {
    l <<- l %>%
      addMarkers(data=map.meta.split[[df]],
                 lng=~lon, lat=~lat,
                 label=~as.character(archiveType),
                 popup=~paste(str_c('Dataset: <a href="',link,'">',dataSetName,'</a>'),
                                 # str_c("Elevation: ",elev),
                                  str_c("Archive Type: ",archiveType),
                                  sep = "<br>"),
                 group = df,
                 clusterOptions = markerClusterOptions(removeOutsideVisibleBounds = F),
                 labelOptions = labelOptions(noHide = F,
                                             direction = 'auto'))
  })

l %>%
  addLayersControl(position = "bottomleft",
    overlayGroups = names(map.meta.split),
    options = layersControlOptions(collapsed = FALSE,
                                   opacity = 0.8)
  )
```

### Search the LiPDverse (Beta! doesn't work well yet)
```{r}
#Add google search bar
htmltools::includeHTML("../../googleSearchChunk.html")
```


Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### temperature (permil) [1-1]
```{r}
plotCol(thisTS,ind = 1)
```

### Mg/Ca (degC) [1-1]
```{r}
plotCol(thisTS,ind = 4)
```

### temperature (permil) [1-1]
```{r}
plotCol(thisTS,ind = 6)
```

### d18O (mmol/mol) [1-1]
```{r}
plotCol(thisTS,ind = 5)
```

### temperature (degC) [2-1]
```{r}
plotCol(thisTS,ind = 7)
```

### d18O (degC) [3-1]
```{r}
plotCol(thisTS,ind = 9)
```

Row {.tabset .tabset-fade}
-----------------------------------------------------------------------

### depth (cm)
```{r}
plotCol(chronTS,ind = 1)
```

### age (yr BP)
```{r}
plotCol(chronTS,ind = 15)
```

### age14C (yr14C BP)
```{r}
plotCol(chronTS,ind = 2)
```

### age14Cuncertainty (yr14C BP)
```{r}
plotCol(chronTS,ind = 3)
```

### fractionModern (unitless)
```{r}
plotCol(chronTS,ind = 4)
```

### fractionModernUncertainty (unitless)
```{r}
plotCol(chronTS,ind = 5)
```

### delta13C (permil)
```{r}
plotCol(chronTS,ind = 6)
```

### delta13Cuncertainty (permil)
```{r}
plotCol(chronTS,ind = 7)
```

### thickness (cm)
```{r}
plotCol(chronTS,ind = 8)
```

### labID (unitless)
```{r}
plotCol(chronTS,ind = 9)
```

### materialDated (unitless)
```{r}
plotCol(chronTS,ind = 10)
```

### activity (Bq g-1)
```{r}
plotCol(chronTS,ind = 11)
```

### activityUncertainty (Bq g-1)
```{r}
plotCol(chronTS,ind = 12)
```

### supportedActivity (unitless)
```{r}
plotCol(chronTS,ind = 13)
```

### x210PbModel (unitless)
```{r}
plotCol(chronTS,ind = 14)
```

### ageUncertainty (yr BP)
```{r}
plotCol(chronTS,ind = 16)
```

### reservoirAge14C (yr14C BP)
```{r}
plotCol(chronTS,ind = 17)
```

### reservoirAge14CUncertainty (yr14C BP)
```{r}
plotCol(chronTS,ind = 18)
```

### useInAgeModel (unitless)
```{r}
plotCol(chronTS,ind = 19)
```

### notes (unitless)
```{r}
plotCol(chronTS,ind = 20)
```
